\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cAriel{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\updatemacro{\cSlave}{
  \nickname{Morgan}
  \mapnickinformal
}

\updatemacro{\cPriest}{
  \nickname{Flounder}
  \mapnickinformal
}

You are \cAriel{}, former \cAriel{\Prince} of \pAtlantis{}, and current \cAriel{\King} of \pAmerica{}. You traded your old life away for a chance at love, and now seek to save your family and earn the respect of \pAmerica{}.

Born as the \cAriel{\mer} \cAriel{\prince} of \pAtlantis{} to your \cKing{\parent}, \cKing{\King} \cKing{} and your \cQueen{\parent}, \cQueen{\King} \cQueen{}, your early childhood was a happy one. Your family doted on you, and you were \cAriel{\aprince} - loved by all, and without a care in the world. You loved your little \cPrincess{\sibling} \cPrincess{} from the moment \cPrincess{\they} \cPrincess{\were} born - and for a short time, you were one big, happy family.

That changed abruptly, however, when your \cQueen{\parent} disappeared when you were only 9 years old. The realization that one of your parents was well and truly gone left an unmistakeable hole in your life. Had \cQueen{\they} really loved you? Had \cQueen{\they} left \emph{because} of you? At some level, you knew that these thoughts were ridiculous. At another level, you couldn't get them out of your head.

You started to pull away from your family, from your duties, and distance yourself from them. You couldn't be fully invested here anymore - something had changed. It didn't take long for you to express your restlessness by joining the Explorer's Guild, led by your \cPlant{\Uncle} \cPlant{}. Here, at least, there was a bit of escape. Here, they didn't treat you like \cAriel{\aprince}. Here, you could explore, carefree, and find yourself even as you found treasures in the ruins. It was the perfect escape. You even met your first commoner friend, a \cPriest{\priest} of the Church of the Tides and great buddy for adventure, who you nicknamed \cPriest{}. Together, you had many adventures under the sea, and the hole in your heart filled, just a little.

Years passed in relative stability. The memories of your \cQueen{\parent}'s abandonment had all but faded from your mind. It was just a routine exploration - one like any other - when your life changed once again. Alone on an adventure for once, you noticed a ship passing by far above, and against your better judgment, you rose to the surface to see. Upon that ship, high above the waves, you saw a human so blindingly \cEric{\hot} that you nearly choked staring at \cEric{\them} in the open air. It was at that moment that you knew what was missing in your life up until then. You had been born a \cAriel{\mer} when your destiny all along had been to be a human.

The next few days were a blur. You were in a haze of memory so deep and impenetrable that you weren't quite sure \emph{how} you came to be standing in front of \cWitch{}, one of the most dangerous and powerful magicians beneath the sea. But the sight of \cWitch{\them} in all of \cWitch{\their} splendor soon broke you from your reverie.

At first it looked like what you were asking was too illegal even for \cWitch{}, but just when you despaired, \cWitch{\they} agreed to help you. \cWitch{} offered you a ten page contact, which you glanced through. The terms were acceptable, albeit stiff. If you succeeded in finding love within a month, you would retain your legs. If you failed to find true love though, your soul would be forfeit to \cWitch{}. You signed the contract without hesitation. You had no doubt that you and \cEric{} were soul mates and \cEric{\they} would fall in love with you in a heartbeat once \cEric{} met you.

Unfortunately for you, there was some fine print in the contract that you missed on your initial reading. Once you had succeeded in wooing \cEric{}. \cWitch{} slipped into \cEric{}'s castle and revealed your folly. Your success in finding true love saved your own soul, but at the price of you second born child's soul. You were devastated, but before you could even start to try to negotiate, \cEric{} panicked and called the guards to haul \cWitch{} off to the dungeons. You watched helplessly as \cWitch{} decimated \cEric{}'s personal guard and killed \cEric{}'s \cSlave{\sibling} \cSlave{} by knocking \cSlave{\them} into the ocean from which \cSlave{\they} never surfaced. \cWitch{} then dove off the balcony into the ocean. While around you the humans cheered their victory, you were sick at heart. A magician as powerful as \cWitch{}, despite being heavily wounded, was back in \cWitch{\their} element -- it was unlikely that the sharks could finish \cWitch{\them}.

Life on land went on though, and you and \cEric{} were married. You struggled somewhat to be accepted by \pAmerica{}. You had hoped that the birth of your \cWillow{\offspring}, \cWillow{}, would melt human hearts. Although they eagerly embraced \cWillow{}, you still felt as though you were on the fringe of acceptance. What could you do to earn the love of your adopted country? 

Your \cKing{\parent}, of course, wouldn't speak to you any more. \cKing{\They} forced you to cut ties with your entire family when you left the sea by disowning you. You miss them, but the happy family you remember from your childhood years was gone long before you left, lost along with your \cAthena{\parent} when you were 9. At least with \cEric{} you have a family with a \cEric{\parent} that didn't sink into endless depression. \cEric{} is there for \cWillow{} in a way that \cKing{} was {\bf never} there for you.

Despite being human, you retained your ability to communicate with ocean creatures. A few years ago, a seagull turned up outside your window with a fish in it's mouth. The fish relayed an urgent message from your contacts in \pAtlantis{}. (Despite your \cKing{\parent}'s best attempts to isolate you for the ``sake of \pAtlantis{}'', you had non-merfolk friends who still kept in touch) Word in the underground was that \cWitch{} had surfaced again, in disguise of course.  Suddenly the old unease over \cWitch{}'s survival bloomed anew. Was she coming for your next child? 

You immediately went to \cEric{} and discussed what to do. The two of you agreed that you would have to revive your contacts in \pAtlantis{}, to try to confirm these rumors. You'd figure some way out of your contract if it turned out to be true that \cWitch{} was still alive. You reached out to your \cKing{\parent}, apologized a thousand times to \cKing{\them}, and begged \cKing{\their} forgiveness. After only some cajoling, your \cKing{\parent} relented. \cKing{\They} \cKing{\simpleverb{seem}} to regret the way \cKing{\they} reacted when you left. The two of you talk occasionally at the seashore at the base of your castle.  In the meantime, you banned \cWillow{} from going near the ocean. If \cWitch{} was still alive, there was no telling what \cWitch{\they} might try to do to get revenge. You had to keep your \cWillow{\offspring} away from \cWitch{}.

You immediately redoubled your search for clues as to how to get out of the contract. Unfortunately, with magic being so rare on land, the going was slow. Eventually you found an obscure, hand written journal about a peculiar brand of magicians that often dealt in souls. These magicians were unusual in that they had no natural magical talent of their own, but instead borrowed from spirits for their powers. These magicians, while incredibly powerful, incur huge debts as they cast spells. They are forever trying to repay them. Perhaps this information could help you deal with \cWitch{}? If \cWitch{} is borrowing power from spirits, you could be in major trouble. You'll have to be careful to not get ensnared in a worse situation than the one you are already in.

It was a few years before \cKing{\King} \cKing{} agreed to let you return to the ocean temporarily. This year is the year. You have two tickets to the \cExExKing{} Ball. This annual celebration of the new year will be made extra special by the presence of a delegation from \pPacifica{}, as \pAtlantis{} and \pPacifica{} try to negotiate a peace treaty. Originally, you and \cEric{} were going to attend, but a convergence of things changed that. \cEric{} suddenly came down with an unknown disease. Within 12 hours, \cEric{} was having seizures and trouble breathing. You would have called off the excursion, but the situation was now dire. You were pregnant again - your second-born. If you cannot find \cWitch{} and get \cWitch{\them} to renegotiate the terms of the contract, you will lose your second child.

When you sent word to your \cKing{\parent} that \cEric{} was sick and would be unable to attend, \cKing{} came to console you. You had been too harsh on \cKing{\them} all those years ago. Now grown up, you realize that \cKing{} really did care about you. Unfortunately, \cWillow{} had followed you down to the beach, despite the fact that it was forbidden. \cWillow{\They} saw you talking to \cKing{} and confronted you. Like the troublesome teenager \cWillow{\they} \cWillow{\were} turning into, \cWillow{} demanded an explanation, and then threw a tantrum that you had hidden something so big as the existence of mermaids from \cWillow{\them}. As an attempt to calm \cWillow{}, your \cKing{\parent} offered \cWillow{\them} \cEric{}'s ticket to the ball if \cWillow{\they} would act with decorum. If only you could tell your \cKing{\parent} that bringing \cWillow{} was incredibly dangerous! Instead, you could only stand helplessly by as \cWillow{} ran back to the castle, ticket in hand.

Compounding your worries about \cWillow{} is the fact that \cWillow{\they} recently ran away from home. In what had to be the most stressful 3 days of your life, you searched tirelessly for your \cWillow{\offspring}, until finally finding \cWillow{\them} by the shore. \cWillow{} clams up every time you try to find out why \cWillow{\they} ran away, and where \cWillow{\they} went, so for now, you've simply grounded \cWillow{\them} for life to teach \cWillow{\them} a lesson.

The last thing \cEric{} asked of you from his sickbed as you left was to find a way to stop the \pPacifica{}n attacks on your ships. After a brief moment of thought, you grabbed a sample of the \cPolio{} vaccine from the infirmary to bring down with you. If \cPolio{} was as big a problem in \pPacifica{} as in \pAtlantis{}, the \cPolio{} vaccine could be a powerful bargaining chip in getting them to stop killing your people. 

You and \cWillow{} were escorted to \pAtlantis{} a few hours ago by \cManta{}, your \cKing{\parent}'s oldest advisor, and the magician who strictly regulates magic in \pAtlantis{} now. \cManta{} cast a spell over the palace, allowing you and \cWillow{} to breathe safely while anywhere on the grounds. As the evening began, you ran into your old friend, \cPriest{}. To your mild surprise, \cPriest{\they} introduced \cPriest{\themself} as \cPriest{\MYname}, which you vaguely recognized as \cPriest{\their} real name. You know it's been a long time, but \cPriest{} sure was cold to you.

As you wandered the halls of the palace this afternoon, enjoying the feeling of weightlessness that swimming gives you, you noticed two things about your old home. One was the continued presence of the palace story teller. You used to love to listen to his stories when you were little. You stopped a moment to listen again This was a new story! He spoke of a powerful magical artifact called \iWishingStone{\MYname}. If it truly exists, it could be a panacea for your troubles\ldots (If you want to pursue this plot, find ``\sOldMan{}'' in the palace entryway.) The other thing you noticed was more disturbing. In the palace archives, the pedestal where your \cAthena{\parent}'s beautiful, heirloom \iMusicBox{} used to sit, is now empty. As you stared at the empty clamshell where it used to rest, a sense of dread washed over you like a cold current. You always knew the \iMusicBox{} was more than mere decoration, but now you were convinced that its disappearance left \pAtlantis{} open to danger. You have to find it.


\begin{itemz}[Goals]
  \item Talk to \cWitch{} and figure out how to get out of your contract. (Note \cWitch{}'s death wouldn't solve your problem, as to do so will not void the contract.)
  \item As long as you are here, see if you can dig up any new clues about what happened to your \cAthena{\parent}. Your \cPrincess{\sibling} should be helpful in this matter.
  \item Repair your relationship with \cKing{\King} \cKing{}, and with your \cPrincess{\sibling} \cPrincess{}.
	\item Find a way to end the \pPacifica{}n attacks on your people, using the vaccine (\iVaccine{}) as a bargaining chip if necessary.
  \item Figure out what has changed with \cPriest{} and help \cPriest{\them} if possible.
  \item Keep your \cWillow{\offspring} safe!
  \item Find the \iWishingStone{}.
  \item Find the \iMusicBox{}.
\end{itemz}

\begin{itemz}[Notes]
  \item You are no longer a member of the Explorer's Guild. Despite knowing its inner workings, you no longer have access to their supplies.
\end{itemz}

\begin{itemz}[Trivia]
  \item The \ppolio{} vaccine was developed in \pCity{}.
  \item The national dance of \pAtlantis{} is merengue.
\end{itemz}

\begin{contacts}
  \contact{\cKing{}} Your \cKing{\parent}. You are still trying to repair your relationship.
  \contact{\cWillow{}} Your \cWillow{\offspring}, who is still grounded. \cWillow{\They} \cWillow{\are} quite a handful.
  \contact{\cPrincess{}} Your little \cPrincess{\sibling}, \cPrincess{\prince} of \pAtlantis{}.
  \contact{\cPriest{}} An old friend of yours, now among the highest ranking Explorer's Guild members. Maybe \cPriest{\they} can help you?
  \contact{\cPlant{}} Your \cPlant{\uncle} and leader of the Explorer's Guild.
	\contact{\cWitch{}} \cWitch{} in disguise. A thoroughly unpleasant individual.
\end{contacts}

\end{document}