\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cQueen{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

Your name is \cQueen{\MYname}. Well, actually it is \cQueen{\King} \cQueen{}, but everyone who knew you by that name thinks you are dead.

You are from \pAtlantis{}. You think. You are not sure, but you look much more like an \pAtlantis{}n than a \pPacifica{}n \cQueen{\mer{}}. Unfortunately your earliest memories are of the barren rooms and harsh teachers of \pAssassin{}, hidden deep in the icy waters of the Bering Strait. You have no idea where you were born, or how you ended up in that dreadful place. 

Wait, no. Your earliest memories are of growing up with a loving family on a coral plantation in the Caribbean. -- Aren't they?

You shake your head, as if to dislodge the false memories. It's been like this for years, getting worse all the time. False memories, implanted in your mind to make you a sleeper agent, bleeding into memories of your real life. It doesn't help that you often wish that the false memories were true. You had a much gentler pretend life. If only you could have lived that one instead of the one you did.

For ten years you trained at \pAssassin{}, until you were ready. Ready to kill \cKing{\King} \cKing{}. You learned a hundred ways to kill a merman with weapons, and a hundred more ways to do it bare handed. But you were more than just an assassin. You were trained in the arts as well. Raised to impersonate a \cAthena{\mer} of the highest station. It was your job to infiltrate \pAtlantis{}, and the heart of the \cKing{\King}, and to strike \cKing{\them} down when \pAtlantis{} least suspected. You were to be the final nail in the coffin of this treacherous nation.

Your memories get really fuzzy right around graduation time.  You remember a ``\cDiplomat{}'' fondly, but weren't sure who \cDiplomat{\they} \cDiplomat{\are}. Well, \cDiplomat{\they} \cDiplomat{\were} important to you. You tried to run away together, but apparently that didn't work. Try as you might, you can't remember what happened next. Its a totally disconnected time line from your life in \pAtlantis{}.

To ensure a seamless integration into \pAtlantis{}n society, your memories were locked away, and a false childhood implanted in your mind. You were left on a destroyed coral plantation, within the ransacked realm of a minor noble, for an \pAtlantis{}n patrol to find.  They discovered a necklace bearing a Baron's seal on your body, which convinced everyone -- yourself included! -- that you must be the only living heir to the barony, and therefore nobility.  Your training, even below the conscious level, served you well, and you quickly rose to prominence at court, and became a favorite of young \cKing{\King} \cKing{}. You would often accompany \cKing{\them} on the long swim to the royal cemetery, where \cKing{\they} went almost daily. You listened with sympathy to the ails of \cKing{\their} heart, and it was with much joy and hope that you accepted \cKing{\King} \cKing{}'s marriage proposal at the end of \cKing{\their} year of mourning.

\cKing{\King} \cKing{} was almost always distant and melancholy. Even the birth of your second child could not stir \cKing{\them} to joy, almost 10 years after the tragedy that put \cKing{\them} on the throne. Only music ever brought a smile to \cKing{\their} face. The lively music and dance of the merengue reached a part of \cKing{\them} that not even the pain \cKing{\they} had endured could destroy. \cKing{\They} smiled, and laughed - \cKing{\They} lived - when \cKing{\they} \cKing{\were} on the dance floor.

About a year later, a nixie came to you in a dream, begging you to journey to \cNixie{\their} home. \cNixie{\They} warned you of impending threats to \pAtlantis{} and offered you a \iMusicBox{\MYname} to protect your country. Some people wouldn't have understood why this was such a big deal, but you did. Music is magic, or the preservation of it anyway. Music has the power to remember spells, and to extend their duration far beyond what would ordinarily be possible. A spell of protection might only last a few days, unless laced into a melody, in which case a well cast spell could endure for years. Too bad you have never demonstrated a proclivity for magic yourself.

What else could you do? \cKing{} had given so much for \pAtlantis{}, surely you could sacrifice a few weeks away from home to protect your beloved homeland. You journeyed far to the north, to the fjords of Norway, where you met a nixie of great power, \cNixie{\MYname}, in the brackish water where \cNixie{\their} stream joined the sea. \cNixie{} gave you the magical music box. Wound once every decade, it played a song that would protect \pAtlantis{} from a number of dangers that \cNixie{} had seen portents for. \cNixie{\They} showed you how to wind it with a special key on a gold chain that \cNixie{\they} also bestowed upon you. You vowed never to take the key from around your neck, except to give it to whichever daughter you would pass the secret on to. You returned to \pAtlantis{}, flush with triumph.

But a week later, your hopes and dreams were shattered when you woke up in the middle of the night, the truth about your past pouring through your head. You knew suddenly that you were not a gentle \cQueen{\mer} of \pAtlantis{}, but a spy and an assassin sent to kill \cKing{\King} \cKing{}.

You balked at the horror of your task - to kill your beloved. Rather than complete your mission, you staged your own kidnapping that very night and fled \pAtlantis{}. You weren't able to tell anyone what had happened, you didn't even get to kiss your younger daughter, \cPrincess{}, goodbye. But it was for their own safety that you did it. You had to leave as soon as possible. If \pAssassin{} could lock your memories away, maybe they could also mind control you. You couldn't risk that. So you swam.

Your heart was heavy with sadness and loneliness, and your mind was clouded with conflicting pasts. In your distracted state, you blundered into a fishing net set in the shallows and nearly drowned. It was only by happenstance that you survived. \cGeneral{}, a human General, was meditating on the beach nearby. Intrigued by the strange movements of the fishing net floats, \cGeneral{\they} dove into the water and came to your rescue.

You were terribly frightened of \cGeneral{\them}, despite the rescue. There is precious little that your real memories and your fake ones agree on, but one of the things they do agree on is that humans are at best dangerous. The only known interactions with merpeople are short, brutal, and never end well for merfolk. You wiggled free of \cGeneral{\their} arms and dove into the water. It wasn't until you were almost 20 meters down that you realized that \cGeneral{} was keeping pace with you. \cGeneral{\They} \cGeneral{\were}n't human! \cGeneral{\They} \cGeneral{\were} a \cGeneral{\mer}! But you could have sworn you had seen legs when \cGeneral{\they} freed you from the net and lifted you out of the water. What was going on? 

It turned out that \cGeneral{} was a shape-shifter. \cGeneral{\They} could change freely between being a human and a \cGeneral{\mer}. \cGeneral{} didn't ask many questions about your past, but treated you with civility regardless. \cGeneral{\they} didn't even blink when you scrambled to come up with a name. It hadn't occurred to you until \cGeneral{\they} asked that you would have to leave the name \cQueen{} behind. You settled on \cQueen{\MYname}. Over the next few months, you returned regularly to \cGeneral{\their} beach, and when \cGeneral{\they} agreed to abandon the shore and live with you under the waves, your heart sang.  \cGeneral{} has a family estate in the North Sea. Safely away from \pAtlantis{}, you began to relax, eventually fell in love, and had a son with \cGeneral{\them}. You and \cGeneral{} celebrated your son's fifth birthday last month. 

Just when you thought you had put your past behind you, both the good and the bad, a letter arrived on the Fair Isle Current. It was anonymous, but casually dropped detailed, personal information about your past life in \pAtlantis{}. The letter went on to reveal a new assassination plot against \cKing{}, entreat you to return to \pAtlantis{}, and imply that no one else would be able to save \cKing{}. An assassination attempt on the night of the \cExExKing{} Ball, at the height of negotiations with \pPacifica{}? Sounds like \pAssassin{} to you. You simply \emph{must} return. It is not like you stopped loving \cKing{}, really, just that circumstances had forced you apart and you had made the best of things with \cGeneral{}. \cGeneral{} insisted that the letter was little more than bait, but you had to go and see for yourself.  In the end, \cGeneral{} consented to let you go, as long as \cGeneral{\they} came with you. It was a simple matter to acquire a couple of tickets to tonight's gala; \cGeneral{} is after all a representative of the Guardian's Guild and it is not surprising that \cGeneral{\they} might want to be present for the treaty talks.

It will be incredibly dangerous to return to \pAtlantis{}. \cKing{}, and in fact all of \pAtlantis{}, thinks you are dead. Should you be found out, you might be lucky, and be welcomed back in all your glory -- or more likely, imprisoned and executed as an impostor, or a deserter! There is also the matter of the \iMusicBox{\MYname}. You had hoped to use your \iMusicBoxKey{} to wind the box, but a quick visit to the palace archive sent you into a panic. It was gone! You have no idea where to go about looking for it. To top it all off, rumors are circulating that your younger \cPrincess{\offspring} with \cKing{}, \cPrincess{}, may be married off to a \pPacifica{}n \cPrince{\prince}. You intend to find out everything you can about \cPrince{\them} and make sure \cPrince{\they}, and anyone else angling to marry your \cPrincess{\offspring} is worthy. You haven't been able to be there for \cPrincess{} growing up, but you can at least give \cPrincess{\them} this much.

Luckily, it appears that fate is not entirely against you tonight. Before the ball this afternoon, while you swam through the bazaar, you caught sight of \cDiplomat{}. \cDiplomat{\Their} face seemed to unlock a rush of memories. You were the best of friends during your time at the Guild.  That was what they didn't like. You weren't supposed to \emph{have} friends as an assassin.  When you were caught after trying to run away, they separated the two of you. You never saw \cDiplomat{\them} again. Until now. You rushed to \cDiplomat{\them}, marveling at how young \cDiplomat{\they} looked. \cDiplomat{} didn't recognize you under your disguise, but was soon convinced that you are in fact \cQueen{}. \cDiplomat{\They} \cDiplomat{\were} as overjoyed as you by the unexpected reunion. Feeling happy and safe, you found yourself talking overmuch, and the story of why you were here - to find an assassin - slipped out. \cDiplomat{} nearly swam into a pole upon hearing this, and quickly agreed to help you find the assassin. \cDiplomat{\They} seemed deeply disturbed that one of the \pPacifica{}ns with \cDiplomat{\them} was untrustworthy.

\pAtlantis{} seems to be beset with dangers. Tonight is going to be a stressful and precarious dance with unknown and dangerous partners (and a few well known ones), with the fate of \pAtlantis{} hanging in the balance.


\begin{itemz}[Goals]
  \item If it is safe to do so, pass the secret of the \iMusicBox{} on to \cAriel{} or \cPrincess{}, whichever child is more likely to be able to wind the \iMusicBox{} in the future. Don't forget to pass on the \iMusicBoxKey{}. -- Although this is somewhat futile if the box cannot be recovered. Surely someone knows something?
  \item Foil the assassination attempt against \cKing{}.
  \item Vet \cPrincess{}'s suitors and prevent \cPrincess{\them} from marrying anyone unworthy of a \cPrincess{\prince}.
  \item Avoid revealing yourself as \cQueen{\King} \cQueen{}.
	\item Support \cGeneral{}'s agenda as representative to the Guardians Guild.
	\item Safeguard your family, both old and new.
\end{itemz}


\begin{itemz}[Notes]
  \item You have a tattoo on your left bicep that marks you as an assassin from \pAssassin{}. All students of the school have the same tattoo, in the same place. See a GM to acquire a temporary tattoo before game.
\end{itemz}

\begin{itemz}[Trivia]
  \item The Assassin's Guild is located in the Bering Strait.
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cKing{}} Your former \cKing{\spouse}.
  \contact{\cGeneral{}} Your current lover. This could get awkward if you are discovered.
  \contact{\cAriel{}} Your elder \cAriel{\offspring}.
  \contact{\cPrincess{}} Your younger \cPrincess{{\offspring}}.
  \contact{\cManta{}} \cKing{}'s advisor. You never had much contact with \cManta{\them}.
  \contact{\cPlant{}} \cPlant{} is \cKing{}'s \cPlant{\sibling}. \cPlant{\they} \cPlant{\were} always kind to you -- in between bouts of paranoia.
  \contact{\cDiplomat{}} Your old friend.
\end{contacts}

\end{document}

