\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cBodyguard{}}

Your name is \cBodyguard{}. You have been \cPrince{}'s bodyguard for three years. You take pleasure in a job well done, and have foiled half a dozen assassination attempts since you signed on - which makes last month's tragic incident hurt all the more.

You were born in the mid-pacific mountains to a loving, and very lucky family. You were the younger of two chidren - a very rare thing in \pPacifica{}. Children are rare in \pPacifica{}, two in a family is almost unheard of. Your older \cSpy{\sibling} \cSpy{} and you got along quite well - at least until \cSpy{\they} disappeared when you were 5.

You grew up fairly normal, attending school, playing with the few other neighborhood children - nothing dramatic. You did start taking lessons from the local magician at the age of 13 though, once your powers really started to come into their own. On your 16th birthday, you got the best birthday surprise ever - your \cSpy{\sibling} turned up on your family's doorstep! \cSpy{\They} had been kidnapped by the black market trade, ran away from \cSpy{\their} new family and journeyed along across much of the Pacific ocean to return home. You had never expected to see \cSpy{\them} again, so you wasted no time in becoming best friends again.

Once you graduated from high school, you had no desire for higher education. School was stuffy, boring, and all together too hard. You turned instead to the \pPacifica{}n military, where hard work paid off quickly with promotions and bonuses. For some reason, your \cSpy{\sibling} never liked your decision. You enjoyed the military, and were crushed when your superiors transferred you to bodyguard training after a minor scuffle with a fellow soldier.

Not one to give up though, you made the best of it, and soon found that bodyguard training was not as bad as you had thought. You weren't assigned to any stupid nobles or anything, and in fact were soon in charge of training the new recruits yourself. Some 10 years into your career though, the \cPacificanRuler{\King} \cPacificanRuler{\them}self summoned you and assigned you to guard \cPacificanRuler{\them} \cPrince{\offspring} \cPrince{}.

\cPrince{} turned out to be a reasonable \cPrince{\guy}, who gave you a lot of freedom to do your job your way. This worked out well, because it gave you plenty of free time to pursue your magical talents and develop your own potion that would allow you to better protect and defend \cPrince{\them}.

When \cPrince{} was selected to go to \pAtlantis{} in order to try to secure a treaty, you of course began packing your bags. Where \cPrince{\they} went, you went - and that was that. It was a good thing, too, or your greatest failure would have turned into a national tragedy instead.

On a routine patrol, you, the \cPrince{\prince}, and your hand-picked honor guard were set upon by a starving pod of sharks, an unprecedented attack. The battle was fierce, and left you with only a handful of guards left. You had just set about seeing to \cPrince{}'s wounds when you got your answer. One of your mers turned into a shark before your very eyes, and went on a rampage, trying to kill off the rest of you. Though you quickly struck him down, the next one turned, and the next. One by one, every mer either revealed themselves as a feral shapeshifter or was cut down by their former comrades, until only you and \cPrince{} were left. And then \cPrince{\they} turned too.

It took you over an hour to subdue your employer without hurting \cPrince{\them}, but subdue you did. You brought \cPrince{\them} back to the palace, smuggled \cPrince{\them} in, and kept watch in \cPrince{\their} room overnight, worrying all the while. When the moon finally stopped shining over the sea, \cPrince{\they} turned back and open \cPrince{\their} eyes - and you breathed again. \cPrince{} may be cursed, but at least \cPrince{\they} isn't dead. You haven't completely failed yet - though if \cPrince{} keeps going on rampages, you may fail soon.

On a more personal note, \pAtlantis{} may offer your last hope for a child of your own.  You've tried everything to get this child. But even with magical assistance, you and your \cVHusband{\spouse} have been unable to conceive. Your \cVHusband{\spouse} wouldn't like that you are considering a black market child. Even you are a little surprised at how much power the idea has over you. After all, your \cSpy{\sibling} was a victim \cSpy{\them}self. But the allure of having children is so strong.  You are sure you can convince your \cVHusband{\spouse} to accept the child once you have it with you. Besides, the \pAtlantis{}n children are {\bf different}. Their families are clamoring to get rid of them. the Church of the Tides is desperate to find them good homes. \cPriest{} will be your chance.

Lastly, and and of national importance, there have been rumors for several months of Indian aggression. There is very little said overtly, and whenever it is, \cPrince{} quickly stomps it out as idle speculation. You are not convinced it is unimportant however. Your training has given you almost a 6th sense about when not to dismiss seemingly trivial details.  You have to find out more about this. The sooner you have proof, the sooner you will be able to convince \cPrince{} to begin preparations. \pPacifica{} can't afford to be caught unaware if \pIndia{} attacks.  If you complete this tonight, which you hope an infusion of \pAtlantis{}n intelligence can help you do, you may even be able to persuade \cPrince{} to enlist \pAtlantis{} as a military ally.

In preparation for your trip, you sequestered yourself for 48 hours and performed the incredibly draining foresight spell. At first you saw nothing alarming. There appeared to be little for \cPrince{}, which suits you just fine. Nothing more interesting than you getting a tarot reading (readers are rare in \pPacifica{}) But then, deep in the bowl of water, you watched someone you didn't recognize die. Tangled in this tragic scene were the threads of a emerging magician's power. You aren't sure if they are connected, but you can't take that risk. You need to find the budding magician and take them under your wing as soon as possible. Without proper tutelage, magical powers can soon spiral out of control and become a huge danger to everyone nearby.

As you walked into the ball this evening, there was an old merman floating by the door, telling a fairy tale about a \iWishingStone{\MYname}. You dismissed him at first, but the more you think about it, the more you wish it were true. Could it really hurt anything to go looking for it? What would you wish for if you had such a powerful item? You could undo \cPrince{}'s curse. You could have as many children of your own as you wanted. Who knows what else?

\begin{itemz}[Goals]
  \item Re-establish contact with the Magician's Guild of \pAtlantis{} as the \pPacifica{}n branch's representative.
  \item Find and induct the budding magician into the Magician's Guild, for their protection, and yours.
	\item Find the \iWishingStone{} for your sick mother. It may be her only hope.
  \item Arrange to receive a black market child from an \pAtlantis{}n priest.
  \item Research the rumors of \pIndia{}n aggression.
  \item Protect \cPrince{} and keep \cPrince{\their} shapeshifting secret.
	\item Keep your magic a secret. \pAtlantis{} is not as accepting of magic as \pPacifica{}.
	\item Get a tarot reading. You saw yourself getting your tarot read, but didn't see the result. It could be extremely useful.
\end{itemz}

\begin{itemz}[Notes]
	\item You are \emph{Level 3}, a magician of moderate power.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cPrince{}} The \pPacifica{}n \cPrince{\Prince}, and your friend. If you come back without \cPrince{\them}, consider your life forfeit.
  \contact{\cSpy{}} Your \cSpy{\sibling}, who you trust implicitly.
  \contact{\cDiplomat{}} The diplomat in charge of the \pPacifica{}n delegation.
\end{contacts}

\end{document}
