\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cDiplomat{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

\cQueen{\They} left you. \cQueen{\They} left you to rot. You turn the thought over in your mind, worrying it like a sore tooth. You shouldn't poke and prod at it, but it feels so good. The fire inside you burns hot.

You are \cDiplomat{}, a graduate of \pAssassin{} currently masquerading as a gifted diplomat. You and \cQueen{} were close friends who tried to run away together in your last year. Unfortunately, clever as the two of you were, the Guild was cleverer. The two of you were caught, and put on ``trial.'' Being older than \cQueen{}, you were held almost entirely responsible for corrupting \cQueen{\them}. Ha! As if there was anything left to corrupt after 10 years in that miserable place. As punishment, you were put in suspended animation and held as collateral against \cQueen{}, while \cQueen{\they} went on \cQueen{\their} first mission. When \cQueen{} abandoned \cQueen{\their} mission however, the Guild did not kill you as threatened. Instead they chose to bide their time, and left you suspended for many more years. Although suspended animation stops the aging process, it does not suspend the mind. Most people never recover after even a few weeks of such paralysis. You were made of stronger stuff however, and you came through unscathed...mostly.

\pAssassin{} finally brought you out of suspension, just 3 years ago. They fed your desperate hunger for news, revealing that \cQueen{} had abandoned \cQueen{\their} mission, and \cQueen{\their} dear friend, in order to go marry some fool of a General in the North Sea. You knew many years had passed, but surely you had not meant so little to \cQueen{} that \cQueen{\they} had forgotten about you. And yet, here was the proof.

In the midst of your seething, the Guild offered you a chance for revenge.  \pAtlantis{} and \pPacifica{} had recently begun peace talks. While peace is not an environment that \pAssassin{} normally approves of, \cPacificanRuler{\King} \cPacificanRuler{} is very much interested, and \pAssassin{} knows better than to upset \cPacificanRuler{\them}. \cPacificanRuler{\They} therefore offered you a chance to become a diplomat, to slip into \pAtlantis{} and kill \cQueen{}. To make the the deal irresistible, the Guild offered to nullify your obligation to them if you succeed at killing \cQueen{\them} undetected. You could be free to go start your own life, your own way, without \pAssassin{} or treacherous friends to ruin it. It seems that the guild really did want \cQueen{} dead. They even arranged for a powerful ally, embedded in \pAtlantis{}n politics, to assist you.

So you became a diplomat, after a few months of rehabilitation and updating your worldly knowledge.  \pAssassin{} placed you on the fast track, and you were soon the head diplomat on the project. 

Then fate stepped in. Cruel, sweet fate. You were in \pAtlantis{}, dancing the tiring dance of politics, pretending to care, pretending to be outraged on behalf of your country, etc, etc. You were so tired. So bored. So restless. You just wanted to get your hands on \cQueen{} and be done with this horrid, extended chapter in your life. But then, one late night, you were wandering the halls of the palace when you collided with an angel. \cPrincess{\They} \cPrincess{\were} gorgeous. No, \cPrincess{\they} \cPrincess{\were} perfect. You stared into \cPrincess{\their} eyes for a heartbeat, then two. You ran your fingers self consciously through your uncombed hair. You must have looked a mess, with bags under your eyes from too many late nights up pouring over documents.  You finally found your voice, and tried to stammer out an apology for the collision. Ever the graceful \cPrincess{\prince}, \cPrincess{\they} asked if you would join \cPrincess{\them} in a stroll about the gardens. Somehow you managed to push the word ``yes'' out past your uncooperative lips. And the rest was, as they say, history.

Your angel was none other than \cPrincess{}, \cPrincess{\prince} of \pAtlantis{}. In that instant the pain and boredom of politics evaporated. You threw yourself into the proceedings with vigor. After all, without good faith between the countries, how could you ever hope to see \cPrincess{} on a regular basis? To your great frustration, politics move slowly. You couldn't see enough of \cPrincess{} to satisfy either of you. Then \cPrincess{\they} came up with a reckless, dangerous idea that you couldn't resist. \cPrincess{\They} managed to sneak across the border into \pPacifica{} to see you! It was the most glorious afternoon. No formal proceedings, no pretending to be nothing more than acquaintances. No trying to sneak off and snatch a few moments alone. \cPrincess{\They} started to sneak across the border regularly to see you. It was wonderful. But it was also terribly dangerous. If \cPrincess{\they} \cPrincess{\were} caught\ldots{} and then \cPrincess{\they} \cPrincess{\were}.

You were working in the palace when you heard the news. \cPrince{\Prince} \cPrince{} had apprehended a pair of merfolk crossing the border. One of them was \cPrincess{\Prince} \cPrincess{}. Nearly everyone was salivating at the thought of holding \cPrincess{\them} hostage to gain the upper hand against \pAtlantis{}. You scrambled to find \cPrince{}. \cPrince{\They} \cPrince{\were} the only level head that might listen to reason. To your dismay, \cPrince{\they} \cPrince{\were} already questioning \cPrincess{}. You contemplated the problem for a moment, then swam confidently into the interrogation chamber. You whispered a few things in \cPrince{}'s ear, regarded \cPrincess{} with an icy, disapproving look, and left. You hoped it was enough to get \cPrincess{\them} released, without giving away anything. Luckily, \cPrince{} saw the wisdom in releasing the \cPrincess{\prince} of \pAtlantis{} unharmed. \cPrincess{} was escorted back to the border, and that was that.

Over the next few months, you worked tirelessly to bring the treaty to fruition. If diplomacy had started as merely a cover, it was certainly closer to an obsession by now. The Assassin's Guild had made it clear to you that they did {\bf not} want the treaty to go through, but you are beyond their power now. Love rules your life. If the treaty fell through, you would never see your \cPrincess{} again. Ah \cPrincess{}, \cPrincess{\they} brought light to your life that you hadn't known since before you were put in suspended animation. Unless\ldots could you convince \cPrincess{} to elope with you? But no\ldots \cPrincess{\they} \cPrincess{\are} a \cPrincess{\prince} and could never marry a commoner like yourself. If only you could become royalty somehow\ldots

In your search for a way to prove how precious \cPrincess{} is to you, you started on a quest for the fabled \iGlowShell{\MYname}. The \iGlowShell{\MYname} would make a fitting wedding gift. This shell is the stuff of legend, and it was to your immense surprise, that the cryptic chain of clues pointed to the \pAtlantis{} palace. Well, perhaps it was not so unusual. Perhaps some Explorer's Guild member had encountered one and brought it back to the palace without any idea as to the shell's true value. It would doubtlessly be locked up in the palace vault, thrown carelessly in some corner, instead of adorning the neck of the most beautiful \cPrincess{\mer} in the seven seas. You will of course have to keep this quest a secret. Should the other \pPacifica{}ns learn about the \iGlowShell{}, they will most likely want to bring it back for the \cPacificanRuler{\King} of \pPacifica{}.

Just this morning, one more wonderful piece fell into place. As you were walking through the market, you were accosted by a \cQueen{\mer} you didn't recognize at first. After only a few minutes' discussion however, you realized who it was -- \cQueen{} in disguise. \cQueen{\They} yammered at you as if nothing were wrong, as if \cQueen{\they} had never betrayed you. \cQueen{} wanted your help finding a \pPacifica{}n assassin. For a moment you though \cQueen{\they} knew everything, and was about to attack you, but the moment of tension passed and \cQueen{\they} went on to outline \cQueen{\their} plan to trap the assassin. Just as well that \cQueen{\they} \cQueen{\have} no idea what you have planned for \cQueen{\them} tonight. But \cQueen{\they} \cQueen{\simpleverb{seem}} to be well prepared. Finding a more subtle way of dealing with \cQueen{\them} might be a better idea than just taking the direct approach, but you are prepared to do what is necessary if it comes to that\ldots

\begin{itemz}[Goals]
  \item Kill \cQueen{} subtly, both for revenge and to clear your obligation to the Assassin's Guild.
	\item Deliver the official document (\iBirthCertificate{\MYnumber}) to \cManta{} and secure \cManta{\their} help in return.
  \item See that the treaty is signed. Make sure it is as favorable to \pPacifica{} as possible.
	\item Avoid attracting the wrong kind of attention from your fellow Assassin, \cSpy{}, for trying to get the treaty signed.
  \item Find a way to convince \cKing{} to let you marry \cPrincess{} officially -- or elope with \cPrincess{} if you have to.
  \item Acquire the \iGlowShell{} as a wedding gift for \cPrincess{}.
\end{itemz}

\begin{itemz}[Notes]
  \item You have a tattoo on your left bicep that marks you as an assassin from \pAssassin{}. All students of the school have the same tattoo, in the same place. See a GM to acquire a temporary tattoo before game.
\end{itemz}

\begin{itemz}[Trivia]
  \item The Assassin's Guild is located in the Bering Strait.
\end{itemz}

\begin{itemz}[Trivia]
  \item The \iGlowShell{\MYname} is rumored to bring marital bliss to the lucky couple who possesses it.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cPrincess{}} The love of your life.
  \contact{\cQueen{}} Actually \cQueen{}. \cQueen{\They} \cQueen{\are} here in disguise with some story about an assassin plot against \cKing{\King} \cKing{}.
  \contact{\cPrince{}} The \cPrince{\prince} of \pPacifica{} and your political rival for \cPrincess{}'s hand in marriage.
  \contact{\cSpy{}} The other diplomat assigned to see the treaty through, a fellow assassin who will likely expect you to help torpedo the treaty. \cSpy{} is \cBodyguard{}'s \cSpy{\sibling}.
  \contact{\cBodyguard{}} \cPrince{}'s bodyguard and a capable magician in \cBodyguard{\their} own right. \cBodyguard{\They} \cBodyguard{\simpleverb{seem}} suspicious of you. But then \cBodyguard{\they} \cBodyguard{\are} suspicious of everyone except \cBodyguard{\their} \cSpy{\sibling}, \cSpy{}.
  \contact{\cManta{}} The \pAtlantis{}n contact that the Assassin's Guild has arranged to have assist you. \cManta{\Their} reasons are \cManta{\their} own, but \cManta{\they} will help you. You should approach \cManta{\them} discreetly as soon as possible this evening.
\end{contacts}

\end{document}
