\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cPlant{}}

You are \cPlant{}, \cPlant{\prince} of \pAtlantis{} and conspiracy theorist extraordinaire. Due to unfortunate circumstances beyond your control {\bf you are actually an NPC, scheduled to die of poisoning about 2 hours into game, in the middle of the banquet. }  See a GM before game for details about this.

You are the only surviving \cPlant{\sibling} of \cKing{}. Your family was slaughtered when you were just a \cPlant{\kid}, and there was nothing you could do to stop it. This trauma has left you paranoid, scattered, and prone to fits of conspiracy - a situation that modern \pAtlantis{}n medicine has so far failed to provide any succor for. Your place as leader of the Explorer's Guild is sufficiently prestigious for a \cPlant{\prince}, so you are satisfied (though secretly, you are sure that it was a post given to you to get you out of the palace). Should tragedy befall your family again, you are perfectly ready and willing to support \cPrincess{\prince} \cPrincess{} as the heir apparent, or even take on your \cKing{\sibling}'s throne should the need arise.

As leader of the Explorer's Guild, you have spent a lot of time with many of \pAtlantis{}'s youth. Your favorite is, of course, your \cPrincess{\nephew}, \cPrincess{\prince} \cPrincess{}. \cPrincess{\They} is a free spirit, and completely in love. While \cPrincess{\they} thinks that \cPrincess{\they} can hide it from everyone, it is as plain as day to you that \cPrincess{} is in love with \cDiplomat{}. You would like very much to see these two love birds married, and hang the political fall out if \cPrincess{} doesn't marry the \cPrince{\prince} of \pPacifica{}. You have been a driving force in getting those two to see each other ever since you found out, and you don't plan to stop now. The only stumbling block is that \cDiplomat{} is not royalty\ldots

On the other hand, you cannot in good conscience support your \cKing{\sibling}'s endeavor to make peace with \pPacifica{}. You don't trust the people of \pPacifica{} any farther than you can throw them. Any people who would harbor the monsters in the Assassin's Guild don't deserve any kind of consideration. While you are not involved in the treaty in any official capacity, you continue to do what you can to correct your \cKing{\sibling}'s doomed course as an unofficial ``mediator.'' Everyone keeps overlooking the possibility of a cease-fire. You can establish a temporary reprieve for your country, and give \pPacifica{} time to grow up and dismantle the Assassin's Guild without signing up for peace and alliance with them. Unfortunately, your bouts of mania make it somewhat difficult to maintain good rapport with everyone involved.

Despite everyone's belief that you are inattentive, you are incredibly perceptive, and can see that many ails trouble \pAtlantis{} (\emph{Not everything your character ``knows'' is actually true, but your character believes they are.}). You try to warn people about them, but they seldom listen. The one thing you are most sure about is the fact that one of the \pPacifica{}ns in the delegation is a spy sent to kill the \cKing{}. The question is, which one?

Here is a short list of the things you have been trying to warn people of:
\begin{itemize}
 \item \pPacifica{} has sent a spy to kill \cKing{}.
 \item The \ppolio{} vaccine from \pAmerica{} is actually toxic to merfolk.
 \item The Magician's Guild has joined with the Assassin's guild in secret, and is operating outside of the law.
 \item The mafia is growing incredibly powerful and needs to be dealt with.
 \item \pIndia{} is gathering it's resources to attack \pAtlantis{}.
 \item The black market trade of children that goes on in \pPacifica{} is starting to corrupt the Church of the Tides in \pAtlantis{}.
 \item The Merchant's Guild is looking to overthrow the monarchy and establish a democracy.
 \item The \iWishingStone{\MYname} has reappeared, in the palace, tonight!
 \item Shape shifters are actually really common. The Church of the Tides is actively trying to keep this a secret.
 \item {\bf Feel free to make additional things up. It doesn't matter if it is consistent or not; sometimes it's even more fun if you tell different players contradictory things.}
\end{itemize}

\begin{itemz}[Trivia]
  \item You are \cOsiris{\MYnumber} years old. Who wants to know?
\end{itemz}

\begin{itemz}[Goals]
  \item Convince as many people of as many conspiracy theories as possible.
  \item Support \cPrincess{}, your favorite \cPrincess{\nephew}.
  \item Help \cKing{} get the cease fire signed - and make sure that it doesn't include peace!
	\item Prevent illegal magic use through your full authority as \pAtlantis{}n Royalty. Magic is the root of all evil.
	\item Get your Tarot read. Somehow, you have a bad feeling about today... Even moreso than yesterday, the day before that, and the day before that...
	\item Give \cPrincess{} or \cDiplomat{} the old book of \pPacifica{}n law you found. You have a hunch it'll be useful to them. {\bf This book is crucial to the player's plots. Give it to them within the first 10 minutes of game.}
	\item Prevent the \pPacifica{}n assassin from killing the \cKing{\King}.
	\item Make liberal use of your will packets to warn your allies and confuse your enemies in the case of your death. {\bf Make sure not to use OOC information for these.} There are more in your room if you run out.
	\item (Out of game) Have an awesome and dramatic death in the middle of the banquet!
\end{itemz}

\begin{itemz}[Notes]
  \item Your catchprase should be something along the lines of ``I'll tell you after the banquet.'' Feel free to invent increasingly ridiculous reasons for why.
  \item You are only somewhat crazy. You should spend 3/4 of your time or more perfectly lucid, if paranoid.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cPrincess{}} Your favorite \cPrincess{\nephew}
  \contact{\cKing{}} Your older \cKing{\sibling} and \cKing{\King} of \pAtlantis{}.
  \contact{\cPriest{}} The representative you appointed from the Explorer's Guild whose job it is to see to the Explorer's Guild's interest in the treaty.
	\contact{\cAriel{}} Your least favorite \cAriel{\nephew}. A \cAriel{\mer} who turned traitor by becoming human, and has returned for unclear reasons. Is clearly up to something.
	\contact{\cManta{}} Advisor to the \cKing{\King}. Is clearly up to something.
	\contact{\cQueen{}} A reclusive \cQueen{\mer} who usually keeps to \cQueen{\their}self. Is clearly up to something.
	\contact{\cWitch{}} A very nice \cWitch{\mer} who you often see at various functions. Is clearly up to something.
\end{contacts}

\end{document}
