
\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cKing{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

Ah, \pAtlantis{}. Your beautiful kingdom. What tragedy it has seen. First the massacre of your family, then the assassination of \cQueen{\King{}} \cQueen{}, and finally the loss of \cAriel{\Prince{}} \cAriel{}. Sometimes you wonder how it is still a functioning kingdom. Sometimes you wonder how you are still a functioning \cKing{\King{}}.

Your \cExKing{\parent{}}, \cExKing{\King} \cExKing{} was a good \cExKing{\King{}}. \cExKing{\They{}} brought \pAtlantis{} out of chaos with the help of the \iTrident{\MYname{}} which \cExKing{\they{}} acquired on a dangerous quest many years ago. It was bestowed upon \cExKing{\them{}} by a freshwater spirit named \cNixie{}. The journey nearly killed \cExKing{\them{}} -- but it was worth it. \iTrident{\MYname{}} brought \cExKing{} the power to bring peace to \pAtlantis{}, and secure the borders against the militaristic \pPacifica{}.

You grew up the middle child of five, and so never envisioned yourself as \cKing{\King{}}. Instead of studying the ins and outs of politics, you spent much of your youth in the company of the court cartographer. The thrill of the unknown tugged at your heart, and you were never so happy as when you were exploring some uncharted canyon, or previously unknown reef.

Thirty years ago, your carefree life all changed dramatically when \pPacifica{} struck unexpectedly, and slaughtered your family. The only reason you survived was that you had lost track of time while exploring a supposedly bottomless crack in the ocean floor, and so arrived home well after dark. As you swam toward the castle, a sense of uneasiness grew inside you, and a metal taste started to build in your mouth. Sharks circled the palace, making approach nigh impossible for you. When the body of a merperson was thrown unceremoniously out of one of the upper story windows, only to be torn to shreds in an instant, you knew what was happening. No matter how fast the sharks converged, you had seen the flaming red hair of your own mother.

Anger welled up in you and you darted from your hiding place, without a thought in your mind but revenge. It was not until a bolt of electricity shattered the roof of the throne room and \iTrident{\MYname{}} came sailing out of it toward you that the magnitude of what was happening hit you. As your hand closed around the \iTrident{\MYname{}}, you knew you were your \cExKing{\parent{}}'s eldest living heir. The palace was awash in blood, both \pPacifica{}n and \pAtlantis{}n that night. 

A growing dread, your own adrenaline, and the lurking nightmares that threatened to swallow you, kept you from your rest that night. In the deepest hour of the night, a \pPacifica{}n army attacked, expecting to find \pAtlantis{} in disarray. Instead, they met the tip of \iTrident{\MYname{}}, and the points of your soldiers' weapons. You drove the army out, showing no mercy, and pursued them deep into \pPacifica{}. In your rage and shortsightedness, you ordered fields and homes destroyed, families killed and livelihoods decimated. You wanted \pPacifica{} to truly feel the pain that tore at your own heart.

Upon returning to \pAtlantis{}, you felt empty. There was no sense of satisfaction--no closure. You tried to rebuild what \pPacifica{} had so callously destroyed. After a year of mourning, you took a \cQueen{\spouse{}}, \cQueen{\King{}} \cQueen{}, in an attempt to raise the spirit of your people. \cQueen{\They{}} \cQueen{\were} beautiful, kind, and tried to help you to put the past aside gently and live again. Despite the life you built with \cQueen{}, and your two beautiful children, your past haunts you. You deeply regret the revenge you extracted against \pPacifica{}. 

If the fact that you are now \cKing{\King} wasn't enough of a reminder of the loss of your family, cruel fate left you with one surviving \cPlant{\sibling}. \cPlant{} had been hidden by the servants at your mother's behest.  While they managed to keep \cPlant{\them} from seeing anything, they couldn't stop \cPlant{\them} hearing everything. \cPlant{} never recovered from the trauma.  While some days are better than others, \cPlant{} is always going on about conspiracies. He sees assassins everywhere.  You aren't in a much better state, though; you've been taking anti-depressants for 20 years or so, ever since you lost \cQueen{}. 

Ten years after the raid on \pPacifica{}, \cQueen{} was killed. You missed \cQueen{\them} at breakfast one morning and you went to \cQueen{\their} chambers to awaken \cQueen{\them}, for surely \cQueen{\they} had just overslept after the long sea-horse ride the two of you had taken the day before. When you opened the door to \cQueen{\their} chambers however, you were met with a horrific sight. The entire room was in shambles, with many of \cQueen{\their} greatest treasures shattered. Since there was no body, you maintained hope that \cQueen{\they} might still be alive, only kidnapped for ransom. Yet no ransom note ever came. After almost a year of searching in vain, you had to concede defeat. Your beloved \cQueen{} was dead. You looked around you at \pAtlantis{}, and felt like you had failed \cQueen{\them}. Your beautiful country, which you were never meant to run, was in ruins. The gloom of worthlessness washed over you.

It was almost the last straw when \cAriel{\Prince} \cAriel{} abandoned \pAtlantis{} for the human world 18 years ago.  It wrenched your heart to lose \cAriel{\them{}}. Worse still, if word got out that contact was possible with the human world, who knew what changes might come to \pAtlantis{}? The destruction that humans were capable of wreaking on your world was incalculable.  Your \cExKing{\parent} had never trusted them, and neither do you. You bent all your power on hushing up what you could, but there was no way to cover the gaping hole in your heart, and that of \pAtlantis{}. 

You knew who had probably helped \cAriel{} leave you: \cWitch{}, a powerful magician who flirted with dangerous spells, and flaunting \cWitch{\their} magical prowess. \cWitch{\They} disappeared mere hours after \cAriel{} left. When the Magician's Guild refused to give \cWitch{\them} up from wherever they were concealing \cWitch{\them}, you dissolved the Guild. Only \cManta{}, your trusted advisor, was allowed to continue practicing magic. In the years since, \cManta{} has persuaded you to relax your ban somewhat. \cManta{} carefully regulates magic in \pAtlantis{} now, and the Magician's Guild has begun to rise in power again - though not yet enough to regain their spot on the council. \cWitch{} never resurfaced, but rumors suggest that \cWitch{\they} continued to practice magic through the ban and outside of \cManta{}'s control. \cWitch{} is a fugitive as far as you are concerned.

In your darkest hour, the spark of hope wormed its way into your mind: peace. That is what you could offer \pAtlantis{}. That is how you would have your reign remembered. Not in tragedy, and blood, but in peace and hope and renewal.  As the idea came to you, it felt as if you were a new person, looking out on the world. Peace with \pPacifica{} - that was your guiding light. You sent emissaries, and opened communication channels. 

It seemed your fate had changed. After ten years apart, you even reconciled with your estranged \cAriel{\offspring} \cAriel{}.  You learned that \cAriel{} had given you a grand\cWillow{\offspring}. Hope swelled in your chest, and life was worth living again.  

Then talks stalled. \pPacifica{} claimed that it had apprehended spies from \pAtlantis{} at its borders. To your shock, your youngest daughter \cPrincess{} was caught among them. \cPrincess{\They} showed \cPrincess{\themself} to be an unexpectedly brilliant diplomat, however -- smoothing the whole issue over with a dramatic tale of love and longing for the unknown world of \pPacifica{}. Talks proceeded with new vigor, and optimism. It was even discussed that young \cPrince{\prince} \cPrince{} might make a fine match for \cPrincess{}.

The treaty with \pPacifica{} was drafted, and will be signed at a special ceremony during the Ball tonight. The treaty has been five years in the making and will be your crowning achievement. Nothing must be allowed to sabotage this treaty, as the people of \pAtlantis{} cry for peace.

On a more personal and uplifting note, you recently met your \cAriel{\offspring} by the seaside and had the chance to invite \cAriel{\them} and \cAriel{\their} \cWillow{\offspring} to the ball. Both will be in attendance tonight, and you look forward to catching up with your \cAriel{\offspring} while showing \cWillow{} the wonders of \pAtlantis{}.

\begin{itemz}[Goals]
  \item Get the peace treaty signed.
  \item Arrange to have \cPrincess{} marry \cPrince{} as part of the treaty. \pPacifica{} insists on this to have a full peace.
  \item Keep an eye out for illegal doings in the palace, especially restricted potions. \cReporter{} can help with this.
  \item Make sure no blood is spilled at the Ball. Definitely don't let anyone die!
  \item Renew ties with your wayward \cAriel{\offspring}.
  \item Manage your depression without anyone finding out -- especially your family.
  \item Protect \pAtlantis{}n heritage by preserving the artifacts in the treasury.
\end{itemz}

\begin{itemz}[Trivia]
	\item A nixie named \cNixie{} gave your \cExKing{\parent} the \iTrident{}.
  \item The \pPolio{} vaccine, which virtually eradicated what was once a deadly disease in \pAtlantis{}, was provided to \pAtlantis{} by humans.
\end{itemz}

% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cAriel{}} Your now-human \cAriel{\offspring}.
  \contact{\cPrincess{}} Your younger \cPrincess{\offspring}. \cPrincess{\They} \cPrincess{\are} a budding diplomat.
  \contact{\cManta{}} Your trusted advisor. \cManta{\They{}} \cManta{\have} been with you since the raid on \pPacifica{}.
  \contact{\cPlant{}} Your conspiracy obsessed \cPlant{\sibling}.
  \contact{\cPrince{}} The \pPacifica{}n \cPrince{\prince}, and an ideal match for \cPrincess{}.
  \contact{\cDiplomat{}} The diplomat in charge of the \pPacifica{}n delegation. \cDiplomat{\They} \cDiplomat{\are} a pleasant \cDiplomat{\mer}, committed to seeing the treaty go through.
  \contact{\cGeneral{}} The representative from the Guardian's Guild.
  \contact{\cSlave{}} The representative from the Merchant's Guild.
  \contact{\cPriest{}} The representative from the Explorer's Guild.
	\contact{\cReporter{}} A reporter from The Daily Current, and both a boon and a thorn. \cReporter{\They} bring you news they scope out of plots and underhanded dealings to keep you ahead of the curve, but \cReporter{\they} \cReporter{\are} also merciless in \cReporter{\their} determination to publish everything they find, and everything that happens at the palace.
\end{contacts}

\end{document}
