\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cManta{}}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

Where to begin? The beginning is so far in the past, it's hard to trace the convoluted path that has led you to this day. You guess it all began with \cExExKing{\King} \cExExKing{}, who was both \cKing{\King} \cKing{}'s grand\cExExKing{\parent}, and your \cExExKing{\parent}. Although can you really call \cExExKing{\them} your \cExExKing{\parent}? \cExExKing{\They} never accepted you, never acknowledged you, never did anything for you.

\cExExKing{\They} was jealous of \pPacifica{} in every way. From the bounty of the harvests on the Central Pacific Basin, to the beauty of the kingdom's only \cMother{\prince}, your \cMother{\parent} \cMother{\MYname}. \cExExKing{} started a war over it. A war that devastated both \pPacifica{} and \pAtlantis{}. In the end, he got what he wanted though. His aggressive military tactics led to a breech in the castle wall, and the successful capture of your \cMother{\parent}. \cExExKing{} carried \cMother{\them} off, back to \pAtlantis{}, and by the time a successful counterattack was mounted to retrieve her, you had already been conceived.

Upon discovering the pregnancy, the Royal Family burned for revenge. Your \cMother{\parent}'s brothers wished to just kill you and storm \pAtlantis{} - but your \cMother{\parent} was a seer, and even as \cMother{\their} rage burned hot, she saw more clearly than \cMother{\their} siblings. You were \cMother{\their} best chance at revenge. You were the legitimate heir to the \pAtlantis{}n throne. You were born two months before \cExKing{}. That made you the rightful heir. \cMother{} persuaded \cMother{\their} brothers to spare your life, and to put out the word that \cMother{\they} had died, so that \cMother{\they} might raise you in secret.

And so it was done. You lived with your \cMother{\parent} at the \pAssassin{}, a place of utmost secrecy. The only thing that grew faster and stronger than you was your hatred of \cExExKing{} and what had done to your \cMother{\parent}. \cExExKing{} had to pay. When \cExExKing{\they} died in battle when you were 5, you were dismayed, but not deterred. \cExExKing{\Their} descendants carried the same sin in their veins. How dare they sit on your throne? Their blood would quench your thirst for revenge. 

Although you didn't inherit you \cMother{\parent}'s gift of foresight, you were not without your own talents. From a young age, magic flowed in your veins, and you studied hard from the moment you could read. When you were 14, \cMother{} had a vision that the fate of both \pPacifica{} and \pAtlantis{} were intimately tied to \iTrident{\MYname}. Despite your youth, you relished the chance to strike back at your \cExExKing{\parent}, and so set out on a decades long quest to find it. The search kept you away from home for months at a time. Your mother died, alone in the Guild, while you risked life and fin in the icy waters of the Ross sea, chasing what turned out to be another dead end. 

Years of painstaking research eventually led you to \pAtlantis{}. With a few words whispered in the right ears, you persuaded \pPacifica{} to attack the Angola plain of \pAtlantis{} by sneaking through the neutral kingdom of \pIndia{}. The operation gave you the perfect cover to infiltrate \pAtlantis{} as you blended in with a group of \pAtlantis{}n refugees. Soon, you established yourself in court, and made your extensive magical powers available to the then current \cExKing{\King}, \cExKing{}. You rose through the political ranks quickly, as well as the ranks of the Magician's Guild. You were soon among those elected to the Court of Advisors, with easy access to the \cExKing{\King}'s ear. This put you in position to continue your search for \iTrident{\MYname}, which you wasted no time in exploiting.

It took you more than a decade, but you eventually traced the trail of \iTrident{\MYname} to the fjords of Norway, and a nixie by the name of \cNixie{}. Unfortunately, in your excitement, you weren't subtle enough in your search, and ended up exposing the wrong people to the wrong ideas. As a result, \cExKing{} got there first, and persuaded \cNixie{} to give him the \iTrident{\MYname} as you looked on from a secret cave. You fantasized about blasting him out of the water with a particularly vicious spell, but with the power of \iTrident{\MYname}, he would certainly have bested you in the fight. You beat down your frustration, and hastened to return to the palace before the \cExKing{\King}. It was not yet time to show your hand.

You studied the problem from every angle, but there didn't seem to be a simple way to claim the \iTrident{\MYname}. Your best hope was to somehow be named the legitimate heir to the throne, a feat made harder by the \cExKing{\King}'s numerous children. What you wanted was control of \pAtlantis{} Unfortunately, proof of your lineage was frustratingly hard to come by, with your mother and father both dead. You had to make a move to keep the situation under control - but at the same time, you couldn't risk the kingship passing too far from the \cExExKing{} lineage, for fear of losing your claim to the throne. What you needed was a young, foolish \cKing{\King} on the throne - and a way to eliminate him cleanly when the need arose. So you arranged to have a baby \pAtlantis{}n \cQueen{\kid} kidnapped and taken to the Assassins Guild to be raised as the perfect, deadly match for \cKing{} - \cExKing{}'s third child. Then you waited, and watched - and when \cKing{} was just old enough to take the throne, you smuggled a dozen \pPacifica{}n assassins into \pAtlantis{} to kill the royal family. \cKing{} was \emph{conveniently} off on an Explorer's Guild expedition at the time, allowing \cKing{\them} to escape the carnage.

Meanwhile, the \cQueen{\kid} had been successfully converted to a sleeper agent. When \cQueen{} was delivered to you, you quickly and seamlessly integrated \cQueen{\them} into the \pAtlantis{}n court. Within a year, \cKing{} was married to \cQueen{}, and the pieces were in place. The perfection of your plans faltered when they managed to have a healthy \cAriel{\offspring} named \cAriel{}, undoing much of your work. Maybe you should have killed \cKing{} when you had the chance.

While you secretly manipulated \cKing{\King} \cKing{}'s life, you continued to tend your other plans. Among them was the Magician's Guild. You maintained your position as elected representative to the Court of Advisors, and cultivated your standing with other magicians. One particularly powerful contact was \cWitch{}. \cWitch{\They} gave you an anti-aging spell that if properly maintained meant you could essentially live forever. At the age of 52, you stopped aging, though you did your best to keep up appearances.

For a couple of years, things in \pAtlantis{} were stable. Then that stupid nixie decided to get involved again. You felt the brush of her power, late one night about 20 years ago. You traced the ``scent'' of it through the palace, like a shark on a blood trail. You found yourself in front of \cQueen{}'s room. You envisioned of your carefully laid plans unravellings as \cNixie{} whispered the truth to \cQueen{} in dreams. You burst into the room, fear throwing caution to the currents. But there was no catastrophe waiting for you on the other side of the door. \cQueen{} slept soundly and the residue of \cNixie{} was already diluting. Still, when \cQueen{} slipped off in what \cQueen{\they} thought was a sneaky manner the next morning, you resolved to put this part of your plan into action.

A few weeks after \cQueen{}'s return, you unraveled the spell that locked away her memories. You cloaked yourself in darkness, rendering yourself nearly invisible -- at the cost of several brutally finicky potions -- so you could watch and savor the moment of betrayal that would course through \cKing{} before \cQueen{} killed him. But you waited in the \cKing{\King}'s chambers in vain. \cQueen{} never came to fulfill her mission. The next morning you learned that \cQueen{\they} was gone, and her room destroyed. The minx had staged \cQueen{\them} own kidnapping and gotten away with it - infuritating. Your best efforts weren't enough to track the former assassin. \cQueen{\They} had disappeared.

In the mean time, there were other matters to deal with. That fool \cAriel{} managed to persuade some magician to turn \cAriel{\them} into a human, and ran away from home. This set \cKing{} off into a rage that involved  \cKing{\them} disbanding the Magician's Guild. The guild was scattered, magic was harshly restricted, and your position in court was suddenly very tenuous indeed. Around this time, \cWitch{} disappeared as well. You figured that \cWitch{\they} was involved in some way when \cWitch{\they} came to you a few weeks later, gravely wounded and in need of secret aid. \cWitch{\They} had with \cWitch{\them} a human \cSlave{\prince}. \cWitch{} was so weakened that \cWitch{\they} needed your help concocting a powerful enough love potion to suppress \cSlave{\their} will and make \cSlave{\them} \cWitch{\them} slave. If only you'd managed to steal the recipe! Alas, a missed opportunity.

You went to work on \cKing{}. It took years, but you slowly managed to ease the restrictions on magic. Today, registered magicians may practice openly, and the only ``dark'' magic, including poisons and transformation potions, remains banned. 

You quickly got \cWitch{} permission to practice, hoping that \cWitch{\they} would prove a fruitful ally in return for your previous assistance. Unfortunately, it seems that \cWitch{\they} is almost as power hungry as you. \cWitch{\They} quickly began to amass followers and challenge your position in the Magician's Guild. \cWitch{} also rose to prominence in court, partly due to \cWitch{\their} \cSlave{\sibling}'s growing role in the Merchant's Guild. You worry that if \cWitch{} is not kept in check, \cWitch{\they} may surpass you in influence.

As a pleasant twist in your story, you recently stumbled upon \cQueen{}'s trail again. Your Guardian's Guild contact didn't know who \cQueen{\they} was, of course, but the timing of \cQueen{\their} appearance was enough to convince you. As the pieces for tonight began to fall into place, you wrote an anonymous letter to \cQueen{}, enticing \cQueen{\them} back to the court with lies about an assassination plot against \cKing{}. You also wrote to the Assassin's Guild to inform them of \cQueen{\their} location, prompting them to send an assassin to do away with \cQueen{}. Though bringing \cQueen{\them} here was a big risk, eliminating \cQueen{} will simplify your ascension to the throne, tie off a potentially dangerous loose end, and fulfill your desire for revenge against \cQueen{\them}. Suffice to say, you intend to help the assassination along in any way you can.

The Ball tonight is also host to peace talks between the nations. As advisor to the \cKing{\King}, you can easily tell that peace is in \pAtlantis{}'s best interest. As such, it needs to be stopped - at least until you can ascend the throne. \cKing{} is not to be allowed to do good by \pAtlantis{}. It is your right to be the hero of the country and end the war your \cExExKing{\parent} started. In their letter, the Assassin's Guild told you that they are not terribly enamored of the idea of peace between the countries either. They have therefore sent \cSpy{}, another one of their agents, to stop the treaty from being signed. Given your own interest in stopping the peace talks, you arranged a meeting with \cSpy{\them} last night to fill \cSpy{\them} in on the most recent happenings in the negotiations. After verifying your identity and intentions, \cSpy{} promised to bring you \iHemlock{\MYname}, a rare ingredient that is key to your shape-shifter potion, and the other reason \cSpy{\they} came. The \iHemlock{\MYname} is only fresh for a short while longer, so you will have to make the exchange tonight, and brew the potion in the palace. \iHemlock{\MYname} is highly illegal and known to be dangerous, so you had better be on your toes around other magicians or those in the know. The shape-shifter potion is to be used to facilitate the most ambitious of your plots - ascending to the throne. 

A golden opportunity arose earlier this morning when \cKing{} forced \cPlant{} to come ask you for a potion to help suppress paranoia. You brewed a potion, but not the one \cPlant{\they} asked for - instead, you brewed a deadly, slow acting poison. You don't know when it will trigger, but death will be swift - and one obstacle to the throne will be removed. That only leaves two, possibly three, people standing in your way to the throne - \cKing{}, \cPrincess{}, and \cQueen{}. If you can prevent \cQueen{} from revealing \cQueen{\their} identity, or help to get \cQueen{\them} killed, \cQueen{\they} won't be a threat. That leaves the two current royals. One of them, you can use the shapeshifter potion to discredit - shapeshifters are reviled in \pAtlantis{}, and would never be accepted as ruler once you summon the Chief Justice to verify your claim. The other, you may have to get more creative for. Poison is always one option - overwhelming force is another. There may be more. Really, it would be hard to choose just one - you've been thinking about this for a long, long time.

And there there is the matter of the \iMusicBox{\MYname}. This innocuous looking trinket that \cQueen{} had produced before \cQueen{\their} disappearance. You eventually realized that though it looked harmless, it played a song of protection for \cExExKing{}'s line, and for \pAtlantis{}. As long as this box exists, it is a threat to all of your carefully laid plans - and protection for the bloodline you hate so much. It was clearly a powerful magical item, almost equal to \iTrident{\MYname} - for when you tried to destroy it, your every attempt was thwarted. It took 11 years before you were even able to chip away at its barrier enough to steal it from its pedestal in the royal treasury. You hid it away in the castle and schemed about how to destroy it. It was clearly losing power, though you didn't know why. Regardless, the rate of decay was clear. The spell will finally be weak enough for you to truly secure the box at the end of the night - though actually destroying it will require some kind of magical artifact of great power.

Tonight will be a careful dance. You need to prevent the treaty from being signed, keep the \iMusicBox{} safe, and use the shapeshifter potion tonight. You may not have another chance at any of these. The rest of your plans are not so immediate. It would be convenient to complete as many parts as possible, but you \emph{cannot} afford to have your ultimate plans revealed. Better to spend the night under the radar. Just act the loyal advisor, and pretend to help \cKing{} ensure all his guests have a good time.

Remember, \pAtlantis{} is your country. It is your birthright. While the country could burn for all you care if \cKing{} remains in power, more than anything you want to \emph{rule} \pAtlantis{}, and lifting \pAtlantis{} to it's greatest glory under your reign would be the sweetest revenge.

\begin{itemz}[Goals]
  \item If the opportunity arises, find proof of your lineage and attempt to seize the throne by killing or discrediting those ahead of you in line. A good way to do this is to acquire the \iHemlock{} and make the shapeshifter potion.
  \item Sabotage the Treaty. It is \cKing{}'s dream and you can't let \cKing{\them} take credit for peace.
  \item Keep the \iMusicBox{} hidden. You've stashed it in the residential wing for now (\sPacketA{\MYloc}) and need to keep it hidden from prying eyes.
  \item Investigate rumors of a \iGlowShell{} in the palace. If you can acquire it, it will greatly boost your magical powers post-game.
\end{itemz}

\begin{itemz}[Notes]
  \item Having been raised at the Assassin's Guild complex, you know that all agents from the guild are suppose to bear a tattoo on their left bicep. You were never officially part of the Guild however, and therefore bear no such brand.
	\item The \sRunicCircle{} useful for magical rituals is in the \pCaves{\MYname}.
	\item You are \emph{Level 4} as an accomplished magician whose power has waned in recent years.
  \item You cast the breathing spell that allows the humans to breathe here, but have no special control over it now that it is cast.
\end{itemz}

\begin{itemz}[Trivia]
  \item The \cExExKing{\King} when the war started was \cExExKing{}.
	\item A Nixie named \cNixie{} gave \cExKing{} \iTrident{\MYname}.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cKing{}} Your nephew and the \cKing{\mer} who is sitting on your throne.
  \contact{\cWitch{}} This is \cWitch{} in disguise. \cWitch{\They} is a powerful magician and may prove a crucial contact. More likely \cWitch{\they} will prove an unwelcome adversary in your quest for power.
  \contact{\cPrincess{}} \cKing{}'s younger \cPrincess{\offspring} and heir to his throne.
  \contact{\cPlant{}} \cKing{}'s younger \cPlant{\sibling}. \cPlant{\they} is more than a little crazy and is always yammering about conspiracy theories. Don't let \cPlant{\them} catch onto yours.
  \contact{\cQueen{}} This is \cQueen{} in disguise. You have no intention of revealing that you know \cQueen{\them} unless strictly necessary.
  \contact{\cSpy{}} Your \pPacifica{}n contact who is bringing you \iHemlock{} and is supposed to help you sabotage the treaty.
	\contact{\cDiplomat{}} The assassin sent by the guild for \cQueen{}. Arrange for \cDiplomat{\their} mission to succeed.
\end{contacts}

\end{document}
