\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cPrince{}}

You are \cPrince{}, crown \cPrince{\prince} of \pPacifica{}, heir to the throne, and recently bitten were-shark. You rule your subjects with pride and want to protect them from the disease ravaging your land at all costs - which has become much more complicated with your new lycanthropy.

Born into opulence, you have enjoyed easy prosperity from an early age. Your \cPacificanRuler{\parent} \cPacificanRuler{\King} \cPacificanRuler{} doted on you, but to you, that attention seemed smothering. Lessons in the art of diplomacy were difficult and taxing, but you relished the challenge. You didn't take kindly to your \cPacificanRuler{\parent}'s worried attentions after every single lesson. Without a strict guiding hand, you became rebellious, and spent the majority of your free time sneaking out into the surrounding town to mingle with your common friends, and to take part in the commoners' practice of dancing. Your \cPacificanRuler{\parent} didn't approve, worrying that you would pick up a disease or worse, be kidnapped, but you paid \cPacificanRuler{\them} no mind. What was the worst that could happen to a royal \cPrince{\prince}, beloved by the people?

In retrospect, perhaps you should have listened. It wasn't long before the plague hit your circle of friends. While \ppolio{} was rocking the lower quarters of the capital, you were rocked along with it, contracting a severe case. Your \cPacificanRuler{\parent} immediately sequestered you and began treatment, but not before the disease took a heavy toll. Upon emerging from the palace after being given a clean bill of health, you returned to the lower quarters and fully took in the devastation. What you saw killed a small part of you. Friends you had known and danced with all of your life had died in the streets as you had been being fanned and pampered in your royal bedroom, oblivious that anyone other than yourself had been suffering. You resolved that day to do everything in your power to bring the vaccine to \pPacifica{}, and to champion the cause of the marginalized from then on.

It didn't take you long to find a way to make good on your vow. Your chance came six months ago in the form of a wayward \cPrincess{\waif}. You happened upon \cPrincess{}, \cPrincess{\prince} of \pAtlantis{}, crossing the border illegally while you on a routine patrol. You brought \cPrincess{\them} back to the palace and interrogated \cPrincess{\them} -- gently, though. After all, \cPrincess{\they} \cPrincess{\were} a \cPrincess{\prince} -- fragile and beautiful. You couldn't get much out of \cPrincess{\them} -- \cPrincess{\they} didn't seem to know much -- until talk turned to \ppolio{}. You learned that \pAtlantis{} had a vaccine for \ppolio{}, thanks to their friendly association with humans. Here was your answer! You had to secure the vaccine for your people.  You sent \cPrincess{} back unharmed as a gesture of good faith, and immediately began drafting the treaty that you would propose. Things moved quickly after that, and sooner than even you expected, the trip to \pAtlantis{} was scheduled. You would leave within the month as head of the delegation.

It was then that disaster struck. On a routine patrol, you and your honor guard, including \cBodyguard{}, were set upon by a starving pod of sharks, an unprecedented attack. The battle was fierce, and left you with only a handful of guards left. You had just set about bandaging your wounds and trying to figure out why the sharks had attacked when you got your answer. One of your men turned into a shark before your very eyes, and went on a rampage, trying to kill off the rest of you. When \cBodyguard{} put him down, the next one turned, and the next. One by one, every mer either revealed themselves as a feral shapeshifter or was cut down by their former comrades, until only you and \cBodyguard{} were left. And then -- you turned too.

You don't remember anything else of that night, but you woke up in the morning to the tired, but sharp stare of your faithful bodyguard. \cBodyguard{\They} had wrestled you back to the palace and kept you safe during your transformation. You had been permanently cursed by the feral pod of shapeshifters - and you had no one to turn to for help.

Though the trauma and fear of your new condition was intense, you couldn't let this opportunity go to waste - saving your country at the Neptune Ball is more important than saving yourself. As such, your objectives were clear. First and foremost, you must secure the \ppolio{} vaccine. The easiest way to do this would be to sign the treaty, but apparently humans will be attending the ball as well. Perhaps you could bridge the gap between your nations and they could help you directly? You haven't really thought about what they might want, but you're sure with all of the resources of \pPacifica{} behind you, you can make a good offer. 

Second, you must find a shapeshifter, as discreetly as possible, and find out from them anything they know about controlling the transformation. Something about your new feral nature tells you that there is at least one other shapeshifter here - a shapeshifter that \cBodyguard{} and her magical abilities can find. According to \cBodyguard{}, any magician can reveal a shapeshifter with one of the easiest spells they know - which, while convenient for you, could also spell your doom if cast on you.  \pAtlantis{} is uniformly hostile to shapeshifters.  Be discreet, and pay any price you need to find the answer - your life, and that of your subjects, easily hang in the balance.

An additional benefit you could get by signing the treaty, if you are lucky, would be to secure the \cPrincess{\prince}'s hand in marriage - after all, a political marriage could strengthen the treaty, as you made sure to point out in drafting. But beyond that and the possibility of the vaccine, you aren't terribly convinced that the treaty is worth being signed. \pAtlantis{} is far from trustworthy, and \pPacifica{} has the upper hand. You are less interested in seeing this treaty signed than you let on.

On a more personal note, your studies of \pAtlantis{} have engendered a certain curiosity in you about their native dance forms. You had grown up dancing the waltz, but have read that \pAtlantis{} practices a different form of dance altogether. See if you can learn a new form of dance or two to bring back to your people -- you may learn something else while you're at it.

\begin{itemz}[Goals]
  \item Arrange an agreement to receive the \ppolio{} vaccine for your nation by any means necessary.
	\item Ensure that any treaty that is signed is favorable to \pPacifica{}.
	\item Keep anyone from finding out about your shapeshifting.
	\item Work with \cBodyguard{} to find a shapeshifter and get them to tell you how to keep your shifting under control.
	\item If you don't find a way to keep your shifting under control, you must slake your thirst for fresh blood. Refer to \aBloodthirsty{} for details. 
	\item Keep the members of your delegation safe from harm.
	\item Marry \cPrincess{} if at all possible - and, ideally try to get \cPrincess{\them} to fall for you.
	\item Learn as many forms of dance as you can, and show your stuff at the dance.
\end{itemz}

\begin{itemz}[Notes]
  \item Pick up a \colorShark{} shark headband before game in case you shape shift.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cBodyguard{}} your loyal bodyguard of 3 years, who harbors paranoid delusions about an impending invasion from \pIndia{}. \cBodyguard{\They} \cBodyguard{\are} your only hope of finding a way to keep your shifting under control.
	\contact{\cDiplomat{}} The head diplomat sent to help you get the treaty signed.
	\contact{\cSpy{}} A second diplomat sent to aid in the signing of the treaty.
	\contact{\cAriel{}} Former \cAriel{\Prince} of \pAtlantis{} who may be able to help you secure the vaccine you're looking for to help your people.
	\contact{\cKing{}} \cKing{\King} of \pAtlantis{} and a worthy political adversary.
	\contact{\cPrincess{}} a beautiful \cPrincess{\Prince} who you hope to marry for \cPrincess{\their} beauty and political power.
\end{contacts}

\end{document}
