\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cSpy{}}

Your name is \cSpy{}. You are a spy sent by the Assassin's Guild on a mission to collect intelligence, protect \pPacifica{}'s interests, and prevent the signing of the treaty by any means necessary.

Your early childhood was a fairly normal and happy one. Your family was atypical only in the fact that your parents managed to have two healthy children when so many families had none, and the two of you got along well. That normalcy was quickly shattered, however, when you were kidnapped on your eighth birthday, and whisked far away to the icy waters of the Bering Strait to begin your new life as an assassin.

Like all displaced children, you fought your new life at first. The Assassin's Guild was austere and unforgiving - mistakes were punished swiftly and harshly. But slowly, over time, you began to appreciate the sense of power that your new life brought to you. You were stronger, faster, and sharper, improving your body and mind in ways you had never imagined. By your fourth year, you had fully embraced your new lifestyle, and were well on your way to becoming a deadly, invisible force. You graduated with full marks as an infiltrator with an unflinching dedication to your guild.

Reintegrating into society and your family was easier than you had expected. Your cover story was that you had been kidnapped by the \pPacifica{}n child black market and had trekked across the country after your foster family revealed your lineage to you. You were never quite sure if your parents fully believed your story, but your \cBodyguard{\sibling} \cBodyguard{} certainly did. You hadn't made any friends in the Assassin's Guild, so the companionship of your younger \cBodyguard{\sibling} was a welcome change. Sadly, your duties called, and too soon, you had to move away to take up a diplomatic post at the \pPacifica{}n Royal Palace, where you could only visit \cBodyguard{\them} occasionally. You did manage to secretly pull some strings with the Assassin's Guild to get \cBodyguard{\them} transferred out of military training into a safer bodyguarding role, however, so at least you won't have to worry about \cBodyguard{\them} dying in a border skirmish.

Two weeks ago, you were contacted by your Assassin's Guild superiors with a job. The Assassin's Guild has a different view of the future of \pPacifica{} from the royal family, and it doesn't involve a treaty with \pAtlantis{}. Therefore, you are to attend the treaty negotiations soon to occur in \pAtlantis{} and in your role as diplomat, prevent and obstruct the treaty from being signed. You can count on support from your superior, \cDiplomat{}, another assassin presumably sent on a similar mission. Meanwhile, you are to meet in secret with an \pAtlantis{}n general turned traitor, \cGeneral{}. The turncoat claims to have a prototype for a new weapon \cGeneral{\they}'d like to offer to \pPacifica{}. Your job is to inspect and, if all was in order, retrieve this weapon that would give \pPacifica{} the edge in the coming war. After you deem \cGeneral{\them} to be trustworthy, you were told to hand over the \iBattlePlan{}, so that \cGeneral{\they} could match what \cGeneral{\they} knew to \pPacifica{}'s plans, and help you come up with a way to crush the \pAtlantis{}n movements. Your third contact is \pAtlantis{}n Court Advisor \cManta{}.  You met with \cManta{\them} last night, where \cManta{\they} requested some rare and dangerous herbs, which the Assassin's Guild went to some trouble to obtain in exchange for the information and support \cManta{} will provide you.

Receiving this assignment immediately gave you an idea. As a dabbler in military history, you are intimately familiar with the \pPacifica{}n view of the origins of this war, and though much of it has been lost to time, you have the distinct feeling that \pPacifica{} wasn't the aggressor as \pAtlantis{} has always claimed. Additional research in \pAtlantis{} is definitely in order - and maybe what you uncover can help you more easily sabotage the treaty. 

Last week, amidst your preparations for your departure, you collapsed on the sidewalk as you were returning to your home. A trip to the doctor quickly revealed the worst - \pPolio{}. You had recently contracted it from somewhere, possibly on one of your missions to the lower quarters - and a case this bad could kill you within months. This left you with a problem - sabotaging the treaty would prevent \pPacifica{} from receiving a cure in the short term. Conquering \pAtlantis{} would serve the same purpose, but at this advanced stage of your disease, you might not live to see that come to pass. You know that humans are the source of the cure, and this is the only time you're likely to interact with humans on friendly terms in the near future. Maybe the human delegation can be of some use to you - because a dose of the vaccine has been known to cure early cases of the disease\dots

\begin{itemz}[Goals]
	\item Prevent the treaty from being signed.
	\item Find the hidden history of the war, which may help spark tensions between the two parties.
	\item Avoid being outed as a member of the Assassin's Guild, and avoid capture at all costs.
  \item Find any military intelligence you can about \pAtlantis{} to report to your superiors for the eventual war.
	\item Investigate the \iPrototype{} from \cGeneral{} and seal the deal with the \iBattlePlan{} document if it is viable.
	\item Deliver the herbs to \cManta{}; extract information or assistance from him in exchange.
	\item Take the vaccine to cure your \pPolio{}.
\end{itemz}

\begin{itemz}[Notes]
  \item Your \pPolio{} is making you weak and slow. If you manage to consume the vaccine in game, permanently increase you CR by 1.
	\item You have a tattoo on your left bicep that marks you as an assassin from \pAssassin{}. All students of the school have the same tattoo, in the same place. See a GM to acquire a temporary tattoo before game.
\end{itemz}

\begin{itemz}[Trivia]
  \item The Assassin's Guild is located in the Bering Strait.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
	\contact{\cDiplomat{}} The diplomat in charge of the \pPacifica{}n delegation. As an assassin, \cDiplomat{\they} will help you torpedo the treaty.
	\contact{\cPrince{}} The \pPacifica{}n \cPrince{\Prince}.
  \contact{\cBodyguard{}} Your \cSpy{\sibling}, who you love and can rely on. \cBodyguard{\They} \cBodyguard{\have} magical powers.
	\contact{\cManta{}} Court adviser to \cKing{\King} \cKing{} and known magician.
	\contact{\cGeneral{}} Your weapons supplier and turncoat general.
\end{contacts}

\end{document}
