\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cReporter{}}

The Daily Currents Reporter

You originally emigrated from the Indian Ocean over 20 years ago. You came for college, and a degree in journalism, intending to leave the cutthroat politics of India behind. Moving away from your loving family was the hardest thing you'd ever done, but it was supposed to be good for your career. Unfortunately, the politics followed you.

In your time in \pAtlantis{}, you have made quite a name for yourself. You have a knack for explaining politics in a way that the merfolk of \pAtlantis{} can understand. For the past few years, you have been the Castle correspondent (OOC: think the White House correspondent) for the Current. It gives you an unprecedented position from which to report on the goings on at the Castle. In that time you have become surprisingly close to \cKing{\King} \cKing{}. \cKing{\They} \cKing{\mfn{relies}{relies}{rely}} on you to ferret out what's going on and let \cKing{\them} know about it before it becomes a problem.  When it was announced that there would be peace talks at the ball today, the Current didn't even have to go to the trouble of securing you a ticket, \cKing{\King} \cKing{} delivered your invitation personally.

At first It was kind of fun to be the \cKing{\King}'s little birdie. This however made you deeply attractive to the Indian equivalent of the CIA. With threats to the family you left behind, they are compelling you to use your position in the castle to funnel state secrets to the Indian government. You fear they are planning some sort of an invasion, but without a way to secure safety for your family, you dare not defy them.

Your public objectives at the event will be to ensure that nothing gets swept under the rug - the people of \pAtlantis{} must know! -- and to keep \cKing{\King} \cKing{} from being surprised by any underhanded dealings by finding them out and telling \cKing{\them}. It might be a stretch to call you a gossip, but only a small stretch. You, have no intention of missing a moment of the action. You expect that with all the politics and obligatory back room deals, at least one person’s reputation will end up in ruins. It's not that you take pleasure in their fall, but that you take pleasure in bringing the truth to light.

Secretly, you are also collecting information of military value on \pAtlantis{} and \pPacifica{}. Luckily, tonight you don't need to do the active collecting yourself. You've been informed that the Indian intelligence agency has arranged for none other than \cWillow{}, \cAriel{}'s \cWillow{\offspring} to do it for you. How you might ask? Apparently \cWillow{} has been manipulated into becoming addicted to \iDrug{\MYname}, and is expected to need a source tonight. So you've been provided a store of \iDrug{}, and are expected to exchange doses for answers to various questions. \cWillow{} will present you a written answer (warning: these will be in game items you might not want to be caught with), and you will give them a dose of \iDrug{}. You've stashed the doses in your quarters in the palace. You were so proud when you were granted that room\ldots{}

The thing is, you don't actually \textbf{want} \pAtlantis{}, your new home, to be destroyed or conquered by India. While the treat to your family prevents you from doing anything too direct or obvious, you can support the treaty. A treaty between \pAtlantis{} and \pPacifica{} would go a long way towards protecting \pAtlantis{} from any such threat. So, you've got a plan. You don't usually do character features, but with \cPrince{\aprince} from \pPacifica{} present, you are very interested in getting an interview with \cPrince{\them}. You know that such a piece could be a tough sell to \pAtlantis{}ns who have been at war with \pPacifica{} their whole lives -- the war has been going on for 100 years and no one is alive who remembers a time of peace -- but such an article presenting the \pPacifica{}ns in a good light would go a long way toward making peace last. It is hard to be at war with merfolk just like you. It is much easier when they are some scary unknown.

Still, \pAtlantis{} is your home, and you want to make sure any treaty passed tonight does right by your adopted country. It wouldn't do for \pAtlantis{} to survive an attack by India, only to be substantially taken advantage of by their new ``allies,'' or worse still, tear itself apart form the inside. Don't let the council members from the various guilds exploit the treaty to their advantage at some cost for the country at large, and definitely don't let the council or the \cKing{\King} be hoodwinked by the \pPacifica{}ns. If a proposed treaty is not favorable to \pAtlantis{}, make sure they know that signing it would be a betrayal of the country and will not go unnoticed by the public. 

One small part of this is the royal marriage of \cPrincess{} to \cPrince{}. Such marriages are traditional to seal alliances. You also know the folly of royalty marrying non-nobles. Your native country of the Indian Ocean was wracked by years of civil war after the merchants demanded that the Prince marry someone of their choosing. You don't want to see that happen here too. (OOC: feel free to play the nationalism and classism up as much as is entertaining; don't be afraid to publish ``clickbait.'')

You converted to the Church of the Tides not long after arriving in \pAtlantis{}. Most \pAtlantis{}ns are at least nominally believers. You find many of the teachings resonate with you, especially the practical messages like the dangers of predators, and weresharks. Yes, they are a real thing, and yes, they do attack merfolk on an infrequent basis -- perhaps one or two attacks a year. Those attacks are nearly always lethal though, so caution is well warranted.

Unlike the Church of the Tides, your mind is not at all made up on the question of mages and magic. You think the ban on magic and dissolving of the Magician's Guild was really a power grab by the throne, since they already de facto control the Explorer’s Guild with how many royals are in their ranks. You should do your best to make a decision at the event, based on events you witness and talk you hear. You hope to eventually write an informed opinion piece on the matter, assuming you don't uncover some dastardly plot. As such a well respected writer, your piece would carry a lot of weight to weigh public opinion one way of the other on the issue.

Over the course of the event, you are encouraged to write up small articles, or even “eddies” (tweets), and post them in the grand ballroom, so everyone attending knows what you are telling the rest of the country.

\begin{itemz}[Goals]
  \item For the sake of your family, collect the state secrets being gathered by \cWillow{}, and leave game with them, without being discovered.
	\item For the sake of your adopted country: get a private interview with \cPrince{} and write a character piece on \cPrince{\them}, help the council make sure \pAtlantis{} isn't getting screwed over by the treaty, and make sure that the treaty includes a \textbf{royal} marriage.
	\item Report on the proceedings of the ball to the public, especially the peace talks.
	\item Ruin reputations by reporting on secret doings as necessary.
\end{itemz}

\begin{itemz}[Notes]
  \item You are the only merperson with Indian heritage here tonight. Feel free to invent canon on them, though having left the country over 20 years ago your knowledge may be out of date. If you have any questions or don't know how to answer something, feel free to grab a GM.
\end{itemz}


\begin{contacts}
  \contact{\cKing{}} The \cKing{\King} of \pAtlantis{}.
	\contact{\cWillow{}} The kid doing the actual information collecting tonight. You just have to be the intermediate who trades \iDrug{} doses for that information.
  \contact{\cGeneral{}} Leader of the Guardian's Guild.
  \contact{\cSlave{}} Leader of the Merchant's Guild.
  \contact{\cPriest{}} Leader of the Explorer's Guild
  \contact{\cManta{}} The Court Magician.
\end{contacts}

\end{document}