\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cGeneral{}}

\updatemacro{\cSlave}{
  \nickname{Morgan}
  \mapnickinformal
}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

You are a shape-shifting general out to protect your family and your adopted homeland.

You were born on land to a single mother. You never knew your father growing up. You took one of the few paths open to you - the military. You joined up with the \pAmerica{}n army at the age of 15 to support your mother. Your strength and wit served you well, and you rose through the ranks. By the age of 25, you made drill sergeant. It was your job to train all of the new recruits. You did so well at that job that you were also named captain of the royal guard. This brought you in fairly close contact with the royal family. You struck up somewhat of a friendship with the King, and even beat him at chess occasionally.

When the royal twins were old enough, the unenviable job of training them in swordsmanship fell to you. The children were a pair of royal brats -- at least at first. \cEric{} outgrew this quickly enough, but \cSlave{} never did take kindly to being ordered around. You are sure that you would have eventually turned both of them into stellar soldiers and leaders if the shipwreck hadn't cut your plans short.

It was a on an expedition to the Labrador Sea with the King that an icy storm sprung up. Despite the best efforts of the seasoned crew, the ship was smashed to pieces on the coast of Greenland. You were thrown into the numbingly cold water, and lost consciousness when a wave smashed you against a rock.  You expected you'd never wake up again.

But you did -- at the bottom of an underwater canyon. You were bewildered for few minutes as you tried to remember what happened. Were you dead? You didn't feel dead -- everything hurt. But you were under water. You could breathe under water and for some reason you had a tail. A tail instead of legs. You were a \cGeneral{\mer}! Eventually you got over the shock and went looking for your friends and the King.

It took you two days to find the shipwreck, and when you did, you were heartbroken. The ship had been battered to pieces, and there were clearly no survivors. You  weighed your options and realized that you couldn't go back to \pAmerica{} with gills and a tail. You were half fish now, and didn't know if you could change back. If you did return, you would probably be treated as a traitor. Merfolk occasionally attacked ships, and it was too convenient that you, a \cGeneral{\mer}, were the only survivor.

You reluctantly looted the ship for a few valuable items and set off in search of civilization. You found a military outpost of \pAtlantis{} in the Norwegian Sea, and traded the trinkets from the ship for a chance to earn the merfolk's trust.  The constant border skirmishes with \pPacifica{} gave you plenty of opportunity to master the use of a trident. Your military training from \pAmerica{} served you well, and you were soon a trusted member of the outpost. After about a year, they allowed you to officially join the Guardian's Guild, \pAtlantis{}'s military.

You enjoyed the company of your new brethren, and often went out to bars with them, despite the fact that you were almost twice the age of some of the new recruits. Every time you would go though, in just about every bar you went to, some drunk (or the bartender themselves) would tell you that you looked \emph{exactly} like some old drunk who used to frequent the place. Eventually, you stopped dismissing the stories, and began to wonder if there might not be something to it. In particular, you wondered if this mysterious drunk might be your father.

You took a sabbatical from the Guardian's Guild to follow the trail of drunken stories. It was a convoluted trail, and nothing was ever concrete until you reached the gates of a palatial estate. You marched onto the grounds and demanded to see the Lord. The servants put up a token resistance, saying that the lord was unavailable -- clearly covering up for his drunkenness, which clearly happened often. Once you gained an audience with the Lord, it was clear that he was your father. There was no mistaking the resemblance. It was like looking into the future, and seeing yourself aged 20 years. Once you sobered your father up, he revealed to you the family secret: shape-shifting. Your transformation into a \cGeneral{\mer} was totally normal. Better still, you could change back! You could be human again! -- Your elation faded a moment later, as you realized you had been gone for almost 3 years. There was no way you'd be accepted back at the palace.

Instead, you decided to build a real life here, in the North Sea. You took over the reins of the estate, and soon restored credibility and respect to the family name. You worked prominently as a member of the Guardian's Guild, and rose through the political ranks as well. You even visited the \pAtlantis{}n capital a few times. With all of the social pressures of your new life you sometimes needed a break. Once a week or so, you would swim to some abandoned beach somewhere, shape-shift into a human and sit on the beach and meditate. It felt good to cross your legs occasionally.

It was on one of these trips that you met \cQueen{}. You noticed the buoys holding up your fishing net just off shore to be moving in a very peculiar pattern. You thought a dolphin or something must have been caught in the net. When you went out to investigate, you found a \cQueen{\mer} caught in the net. You cut \cQueen{\them} free, and then dove after \cQueen{\them} when \cQueen{\they} took off. After you got \cQueen{\them} to calm down, \cQueen{\they} introduced \cQueen{\themself} as \cQueen{} -- and did indeed look like the \cQueen{\King} of \pAtlantis{} who you'd heard was recently killed. Eventually you got the whole story out of \cQueen{\them} -- or at least enough of it. \cQueen{} was in need of a place to hide -- and being the upstanding citizen you were, you offered to let \cQueen{\them} stay on your estate for a while, under the identity of \cQueen{\MYname}.  Three years later, you realized that neither one of you wanted \cQueen{\them} to leave. You had fallen in love. Despite the complications should anyone discover who \cQueen{} really was, you decided to take the chance and marry \cQueen{\them}.

While your home life has vastly improved in the last couple of years, the fighting with \pPacifica{} has gotten much worse. Border skirmishes are common, and orders often come from the capital to make strikes into \pPacifica{}n territory. By now, you had been promoted to general, and so found yourself in charge of the very outpost you had encountered all those years ago when you first became a \cGeneral{\mer}. Due to the increased tension with \pPacifica{}, the outpost was expanded into a full fort. You find yourself leading nearly a hundred soldiers and trying to protect the town that has sprung up around the outpost. To complicate matters, a year after you were named general, \cQueen{} had a son (not appearing in person at this game). To your dismay, he seems to have inherited your family's ability to shape shift. The Church of the Tides doesn't look kindly on shape shifters, and your son is in imminent danger in \pAtlantis{}.

You believe that this vendetta by the Church of the Tides to be driven by something darker than fear -- greed. As a member of the Guardian's Guild, even part of the military branch, you are privy to many police reports, and have noticed an alarming increase in the strength of the mafia in \pAtlantis{}. The world of doubt and distrust that you see threatening to destroy \pAtlantis{} would be just a little too convenient for the mafia for this to be entirely coincidence. You threw a considerable amount of resources at tracking down the mafia, and trying to find a way to bring them down. You now head the investigation, in addition to being a military general.

Three years ago, while fulfilling orders to strike into \pPacifica{}n territory, you found yourself out manned and out matched. You were taken prisoner, and dragged off to the gulag-like prisons in the Bering Sea. After a few hard weeks, you were dragged out of your bed in the middle of the night, and hauled off to what you assumed to be another round of interrogations. Instead, you were brought before a man who claimed to be from the Assassin's Guild, whatever that was. Regardless, he claimed to have the power to have you released, if you agreed to become a spy, and pass information to \pPacifica{}. You thought fast. This might be your only chance to get out of here -- back to your \cQueen{\spouse} and son. You agreed.

Once you were back in \pAtlantis{} however, you immediately informed your superiors of the situation, and together you soon cooked up a plan. You began feeding carefully measured bits of information to the \pPacifica{}ns to maintain your cover, while extracting every bit of information you could from the tidbits your contacts dropped. Once \pPacifica{} came to believe that you had actually turned to their side, the Guardian's Guild put its master plan into action. You offered \pPacifica{} a prototype weapon, claiming it came from humans. Supposedly, this weapon would give \pPacifica{} a huge advantage over \pAtlantis{}. They of course jumped at it.  All you had to do was provide the schematics. The weapon is actually designed to explode upon use in a real battle, but stand up to any amount of testing and training. It \emph{should} be subtle enough that the \pPacifica{}ns will outfit most of their army with the weapon before they start to malfunction. Even if they do eventually discover the flaw in testing, though, you intend to extract a heavy price in information beforehand - their \iBattlePlan{}, which you are supposed to use to betray \pAtlantis{} even more thoroughly. Either way, \pAtlantis{} should come out ahead on this deal.

Despite your commitment to \pAtlantis{}, things are getting awfully dangerous around here. You really wish you could move your family onto land, at least until the war dies down. \cKing{\King} \cKing{} claims that a peace treaty will be signed tonight, but the Guardian's Guild knows better than to allow that. And you know better than to hope for the impossible. Your son is a shape shifter, and just learned how to turn human, but your beloved \cQueen{\spouse} \cQueen{} can't leave the ocean without help. While magic is strictly regulated in \pAtlantis{}, you suspect that there are still practitioners who could provide you with a potion that would turn \cQueen{} into a human, and not rat you out for it. You have {\bf not yet} revealed this idea to \cQueen{}, which might be a challenging discussion.

Tonight is the \cExExKing{} Ball. You are going, along with \cQueen{}. Originally you did not plan to attend, hoping instead to trade  the prototype weapon quietly, away from the prying eyes of court. Unfortunately, \cQueen{} received an anonymous letter that spooked \cQueen{\them} -- \cQueen{\they} \cQueen{\are} determined to return to the \pAtlantis{}n capital to find out if the information in the letter is true. You could not understand why \cQueen{} was so upset and concerned, until \cQueen{\they} revealed to you a huge secret: \cQueen{} had been trained as an assassin at the Assassin's Guild in \pPacifica{}. You were floored. Then you were wary. Then you realized that \cQueen{} had no reason to lie to you. Since \cQueen{\they} would not be dissuaded, you insisted on going with \cQueen{\them} to try to help. You will have to be careful to call \cQueen{\them} \cQueen{\MYname}, lest anyone recognize \cQueen{\them} as the \cQueen{\King}. You should probably also help keep it quiet that \cQueen{\they} \cQueen{\are} a former \pPacifica{}n assassin. That is unlikely to go over well at the palace.

As far as your national concerns go, you wrote to your \pPacifica{}n contact and arranged to deliver the schematics at the ball instead. You'll have to be careful though: if anyone should trace the schematics back to you, things could get dicey. And \cQueen{} certainly wouldn't approve.

Just this morning, you intercepted a very interesting letter. To anyone else, it seemed an innocent little letter to someone in the palace. To your trained, tactical mind though, it was obviously a cipher. You spent all afternoon deciphering it. The message was a warning -- about you! The letter warned the intended recipient that the Guardian's Guild member in attendance tonight (that would be you) is hot on their trail. Unfortunately for you, you aren't \emph{actually} hot on anyone's trail. You don't know \emph{who} this letter was intended for. You'll have to dig carefully though people's histories to figure out who is the mafia contact here. Finding proof of their involvement will be crucial to your investigation, their subsequent arrest, and hopefully the eventual capture of the entire group.

\begin{itemz}[Goals]
  \item Pass the schematics to your \pPacifica{}n contact, \cSpy{}. Get the \iBattlePlan{} in exchange, and watch your back in case \cSpy{\they} \cSpy{\simpleverb{discover}} that the weapon is booby trapped.
  \item Find a transformation spell or potion, and convince \cQueen{} to use it so your family can move to the surface.
  \item Represent the Guardian's Guild's interest in the treaty.
  \item Find the mafia contact and collect proof of their involvement.
  \item Assist \cQueen{} in \cQueen{\their} search for the assassin.
  \item Prevent anyone from finding out who \cQueen{} is.
  \item Keep your shape shifting and human past a secret.
\end{itemz}

\begin{itemz}[Notes]
  \item Pick up a \colorHuman{} headband before game in case you shape shift.
  \item Any transformation potion you acquire will lose potency at the end of the game, so you will have to administer the potion before then.
\end{itemz}

\begin{itemz}[Trivia]
	\item While you have never had to use it, your father controls his feral shapeshifter transformation with the the rare and secret sea green herb found in \pAntiLycanthropyHerbs{}. 
	% If Prince Jared knew this, he could suppress his lycanthropy permanently.
  \item \cKratos{} is the head of the Guardian's Guild and he is \cKratos{\MYnumber} years old.
	\item Some alarmist junior members of your guild think that \pIndia{} is amassing troops on a plateau somewhere. You don't have time to deal with such foolishness.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cQueen{}} Your \cQueen{\spouse} and the love of your life. You would be devastated if anything were to happen to \cQueen{\them}.
  \contact{\cSpy{}} Your \pPacifica{}n contact.
  \contact{\cKing{}} The \cKing{\King} of \pAtlantis{}.
  \contact{\cManta{}} The \cKing{\King}'s closest advisor, and the only magician you know.
\end{contacts}

\end{document}
