\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cSlave{}}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\updatemacro{\cSlave}{
  \nickname{Morgan}
  \mapnickinformal
}

You are a human \cSlave{\Prince} enslaved by an evil \cWitch{\magician} and disguised as a \cSlave{\mer} against your will.

Your early life was a happy one, being pampered as a \cSlave{\prince} should in your castle in \pAmerica{}. Your relations with your older \cEric{\sibling} were good, and your father doted on you twice as much, since your mother was lost at sea during a family outing when you were just a kid. The loss of your father when you were 11 affected you deeply for a time. But after a while, you went back to your carefree lifestyle, moving past your loss. You took full advantage of your position, wiling away your time, going through your lessons and flirting with the courtiers. All in all, it was a good life.

...a fact that changed abruptly on your 18th birthday when a monster attacked the palace.

It had been just a normal day for you. Your lessons in diplomacy were winding down and one of your favorite courtiers wanted to share dinner with you. The stage had just been set for a pleasant evening when shouts rang through the castle, followed swiftly thereafter by the sounds of battle. Quickly you ran to your room and donned your sword and chainmail vest before dashing out into the hallways to take command of the first band of palace guard that you saw. The battle had progressed to the balcony, and so you led your troops there, ready to fight to defend your home. When you got there, you saw a strange octopus-like creature. Unfortunately, it also saw you.

With inhuman speed, it grabbed you and threw you head over heels over the side of the balcony. You flipped end over end, rushing faster and faster towards the waves - and then, you knew no more.

You don't remember much of the next few days, only fading in and out of consciousness, and some dark THING forcing you to drink something. But when you came to, you were in a strange place. The floor was sand, the walls were stone, but strangest of all, the air was saltwater. You were beneath the sea - and yet somehow, still alive?

Your new surroundings surprised you, but no more than the sight of the beautiful creature that approached you soon after - a \cWitch{\mer} so perfectly formed that it drove all other thoughts out of your mind, including why you looked like \cWitch{\them}. \cWitch{\They} introduced \cWitch{\themself} as \cWitch{}, brought you food and asked you a few questions. And when you were done, \cWitch{\they} kissed your forehead, which left you surprisingly lightheaded for hours after.

Living with \cWitch{\them} became your new routine, which in retrospect, you questioned surprisingly little. The questions about your life soon faded to \cWitch{\them} teaching you about strange new abilities that you didn't know you had - the reading of the Tarot - and truly bizarre questions that you nevertheless did your best to answer.  Always at the end, \cWitch{\they} would kiss your forehead, and the lightheadedness would last a little longer each time.

It took you half a year to work up the courage to say no to the kiss, but when you did, you wished you hadn't. At first, \cWitch{\they} just seemed surprised. Then a terrible expression came over \cWitch{\their} face. \cWitch{} \emph{ordered} you to submit, and to your shock, you did. And with a cruel smile, \cWitch{\they} left you, drained and alone.

From that day forward, \cWitch{} dropped all pretenses. You were \cWitch{\their} slave, and \cWitch{\they} \cWitch{\were}n't going to let you forget it. Your training continued, and \cWitch{\they} turned to ripping energy straight from your chest.  Though you tried to resist \cWitch{\them} at every turn, you continued to obediently follow orders. Unable to escape, and unable to disobey, you lived your days in misery, continuing to struggle against your magical bonds. You were forced to join the Merchant's Guild, and through your hard work and unwilling sacrifice, moved quickly through the ranks. You were \cWitch{}'s cover to rejoining the undersea country of \pAtlantis{}, and another tool in \cWitch{\their} corruption.

Though \cWitch{\they} assured you that the spell was perfectly inescapable, you found that continued resistance actually did weaken the hold that \cWitch{\they} had on you, though the daily draining of your life force slowed your progress. Though you had been forbidden long ago to touch anything in \cWitch{}'s room, you found that by exerting yourself mentally and taking advantage of a loophole in an offhand command you had carefully elicited from \cWitch{\them}, you could look at the books on the shelves of the room around you. After much careful research while you were sure \cWitch{} was asleep, you found the spell \cWitch{\they} had placed on you - and found how to most effectively go about removing it. You needed a place with a high concentration of magic, and preferably a magician, to deal with the spell. Unfortunately, that didn't describe any place where you could encourage \cWitch{} to go normally. But of course, the Neptune Ball, hosted at the \pAtlantis{}n Palace, is your chance. The Palace is a place teaming with magic. You subtly made sure \cWitch{} knew about it, and began to lay plans, ever so painstakingly, to make your escape while there. And so, you bided your time until the day arrived.

Upon reaching the ball, you noticed a number of interesting things. Though \cAriel{} had known you for a year before your disappearance, \cAriel{\they} didn't recognize you at all! You looked in a mirror, and suddenly understood why - your soul-draining at the hands of \cWitch{} had aged you at least 30 years. You looked nothing like your old self anymore. That meant you couldn't count on \cAriel{\their} help, until you can convince \cAriel{\them} of your identity.

The other thing was also unexpected. General \cGeneral{}, your former arms instructor, was in attendance! But not only \cGeneral{\were} \cGeneral{\they} a human at the time, \cGeneral{\they} had been lost at sea in the same storm that killed your father all those years ago! You need to confirm that your old memories are true, and find out more. Then you must confront \cGeneral{\them} about it, and see what really happened that day at sea.

The last was the most unexpected of all. An old man shouting about the \iWishingStone{\MYname}. From your studies in \cWitch{}'s books, you found that the \iWishingStone{\MYname} is all too real, and has magical power that can break your curse. This may be an alternate, much quicker means to freeing yourself from servitude - \emph{if} you can get your hands on it in the space of the ball. (If you wish to pursue this plot, find the ``\sOldMan{}'' in the palace entryway.)

As the possibility of escape became more real, your thoughts turned to what you would do after you had broken your bonds. Leaving the undersea world forever was not actually as appealing as you had thought it would be; you had grown to love your life under the sea. Officially, though to \cWitch{} it was just a cover story, you're here as the representative to the Merchant's Guild, so fulfilling that role as well as possible made sense. You understand the Merchant's Guild's objectives, but given your hatred of \pPacifica{} from the viewpoint of two different countries, you think you can do better. While you ultimately want the treaty signed as much as the next person, you know that \cKing{\King} \cKing{} is going to be far too lenient with the \pPacifica{}ns. You should do your best to squeeze them for all they're worth, extracting as many concessions as possible.  Someone needs to look out for \pAtlantis{}, so it might as well be you!

\begin{itemz}[Goals]
	\item Break the spell binding you to \cWitch{}!
	\item Acquire the \iWishingStone{} - that could be an easy shortcut to removing the spell, or a powerful bargaining chip otherwise.
  \item Safeguard the agenda of the Merchant's Guild and squeeze \pPacifica{} for all it's worth - but get the treaty signed.
	\item Find out how \cGeneral{} survived the shipwreck and confront \cGeneral{\them} about it.
	\item Make sure \cWitch{} dies -- painfully.
	\item Read the Tarot for as many people as possible.
\end{itemz}

\begin{itemz}[Note]
  \item When you lived on land, your name was \cSlave{}, but everyone under the sea knows you as \cSlave{\full}.
	\item You have long been working away at the spell that \cWitch{} uses to control you. There are standing orders that you cannot break until the spells are gone, such as not being able to directly harm \cWitch{\them}, or do anything to reveal \cWitch{\them} (check your magical effects for a full summary). However, new orders are now less potent. {\bf No single order issued during the ball can compel you beyond 1 minute.} It may be useful to pretend otherwise, however - \cWitch{} hopefully doesn't even know \cWitch{\their} spell has weakened.
  \item Seers are not considered magicians.
  \item You have no reason to want the \iTransformed{} effect broken, given your plans to remain undersea.
\end{itemz}

\begin{contacts}
  \contact{\cWitch{}} Your enslaver. \cWitch{\They} \cWitch{\are} posing as your \cWitch{\sibling}, and as a legal magician.
  \contact{\cAriel{}} Your \cEric{\sibling}'s \cAriel{\spouse} and \cAriel{\King} of \pAmerica{}.
  \contact{\cGeneral{}} Your old arms teacher and the \cGeneral{\mer} who must know what actually happened to your father.
  \contact{\cKing{}} Your \cKing{\King}, and a reasonable \cKing{\mer}.
\end{contacts}

\end{document}
