\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cPriest{}}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

You are a dirty priest, \cPriest{\offspring} of a mafia don, scorned by a \cAriel{\Prince}, and out for revenge.

From birth, you were raised to be a cold, calculating criminal, out for power and coin wherever it could be found. As your family's heir, expectations of you were high, and you excelled at what you did. You always tried to make your parents happy, working hard at your studies and trying to internalize their ethics - but your conscience constantly cast a shadow on your heart. Deep within yourself, you knew that this was wrong - did it really have to be like this? And yet, you saw no other way to make your parents happy. Torn between your parents and your conscience, your only outlet was the Explorer's Guild, a guild of adventurers who sought out and documented new places under the sea. Your far-ranging explorations were the only thing keeping you from succumbing to the dissonance, and running away from this life forever.

That all changed when a young \cAriel{\prince} named \cAriel{} joined the Explorer's Guild. \cAriel{\They} \cAriel{\were} just as restless and adventurous as you, and, more importantly, stunningly beautiful. The two of you became fast friends, exploring new places and learning new things, and getting into a lot of trouble along the way. You sought \cAriel{\them} out every chance you got, and soon, you were inseparable. As you grew closer, Ariel began asking increasingly uncomfortable questions about your home life. Because you knew \cAriel{\they}'d never approve of what you family really did, you quietly packed your bags, left your home, and joined the priesthood of the Church of the Tides. Your piety was questionable, but your heart was in the right place - with \cAriel{}, always and forever.

Or so you thought. Because soon enough, \cAriel{} asked you the question that would ruin your life. 

One day, \cAriel{} came back from a solo adventure with the strangest look on \cAriel{\their} face. A little too casually, \cAriel{\they} asked you if you knew any way to become human. In fact, you did know a magician with more than enough power to do it, a fact that your face couldn't fully hide - but when \cAriel{\they} pressed, you insisted that the magician was bad news. When you could not dissuade \cAriel{\them}, you at least made \cAriel{\them} swear that you two would go together. \cAriel{\They} agreed - you told \cAriel{\them} the name \cWitch{} - but the next day, \cAriel{\they} \cAriel{\were} gone and you were still here.

It didn't take long before the news of \cAriel{}'s disappearance spread. The news was on everyone's lips. But you paid no heed. You were in the deepest spirals of betrayed depression, and nothing could snap you out of it.

Years passed. If time healed all wounds, it had skipped over you - all that had filled the void left in your life was rage and pain, and you had no one to share it with because \emph{\cAriel{\they}} had betrayed you and left.

But finally, your family reached out to you for help. Your 10 year old little \cSister{\sibling}, \cSister{} had been taken by an incurable madness, and they hoped that you could cure \cSister{\them} with your religious rites. Seeing your family again after all of those years wasn't nearly the shock that you received on seeing your little \cSister{\sibling} - madness was only half of it. \cSister{\They} had received the bite of a shape shifter, one of your religion's most hated foes. Though \cSister{\they} \cSister{\were} once beautiful, \cSister{\their} body was now a half transformed mess of flesh, agony, and teeth, tragically too far gone to have any hope of saving. Wordlessly, you struck out into the night, lethal needle at the ready, and over the next week, tracked down and killed your \cSister{\sibling}'s murderer. When you returned, \cSister{} was gone, leaving in \cSister{\their} place only grief, and a lifelong hatred of shape shifters.

Now that you had returned to them, your family wasted no time in leveraging your connections to the priesthood. You found that you were in a unique position to expand the supply of black market children, a lucrative market, and soon, you acquired the legal right to confiscate children ``at risk'' of contracting the shapeshifting disease from the cursed full moon. Your steady supply of children and revived connections to the Explorer's Guild also made you uniquely able to make clandestine, semi-legal trips across the border to \pPacifica{}. The going was slow, however, slow enough that when the head of the Explorer's Guild, \cPlant{\Prince} \cPlant{} \cPlant{\themself} approached you about taking one of your Explorer's Guild colleagues, \cPlant{\their} \cPrincess{\nephew}, \cPrincess{\Prince} \cPrincess{} regularly across the border, you couldn't refuse. It was great cover for your business of ``helping \pAtlantis{}n orphans find a home'', and it renewed your royal connections, a resource your family had not taken kindly to losing. You never did get around to asking why \cPrincess{\they} wanted to cross the border, but that hardly mattered in the long run.

Business was good, for a time - before THIS \cPrincess{\prince} messed up just like \cPrincess{\their} \cAriel{\sibling}. Through \cPrincess{\their} stupidity, the two of you were caught by a border patrol led by the crown \cPrince{\Prince} of \pPacifica{} \cPrince{\themself}. You were swiftly taken back to the palace and interrogated. Fortunately, you managed to dispose of the evidence of your crime along the way - but in the long run, it might not have mattered, since the \cPrince{\prince} seemed much more interested in the \cPrincess{\prince} anyway. You're not sure how you escaped, but the both of you were returned none the worse for wear to \pAtlantis{}, with only your pride and profits damaged - though you may never be able to make that run again because of \emph{\cPrincess{\them}}.
 
Unexpectedly a few weeks later, you were given a great opportunity. In your capacity as a high ranking member of the Explorer's Guild, you were to attend the Neptune Ball to represent the Explorer's Guild, and to make sure that the treaty being drafted between \pPacifica{} and \pAtlantis{} favors \pAtlantis{}. You had heard rumors of peace talks, but never paid much mind to them. You had grown up with the war. Your parents had grown up with the war. The concept of ending the war was foreign to you. 

The \cExExKing{} Ball, where the treaty would be signed, would be attended by a great number of nobles - \emph{including a now human \cAriel{}} - as well as a delegation of \pPacifica{}ns. This immediately brought many avenues of profit to mind - as well as revenge.

First, and most importantly, you need to approach \cAriel{} with the guise of friendship. \cAriel{\They} ruined your life thoroughly and completely, and now, you mean to ruin \cAriel{\theirs}, no matter the cost. But first, you have to figure out how best to ruin it, and that will require persuading \cAriel{} to trust you with \cAriel{\their} secrets.

Second, part of the treaty is to decide who controls the \pGazaStrip{}. Your family has just discovered a vast bed of pearl bearing clams in the \ptrench{}, and if you can wrest this piece of land from \pPacifica{}n control, you'll be able to harvest them safely and quietly. The \pPacifica{}ns have a shaky claim to the land anyway, so your father has given you some ideas about some research you might conduct in the palace library. Perhaps you can convince everyone present that \pAtlantis{} deserves that land after all.

And finally, you want to find the fabled \iGlowShell{\MYname}. You know that you can sell it for an immense price if you can get your hands on it. You also know that its in this palace, but as to exactly where, well... who can say?

\begin{itemz}[Goals]
  \item Find a way to thoroughly ruin Ariel's life.
	\item Research the history of the \pGazaStrip{} and use that knowledge to get it into \pAtlantis{}n hands.
	\item See to the Explorer's Guild interests in the treaty.
	\item Obtain the \iGlowShell{}
	\item Get your hands on as many items marked valuable as possible without getting caught.
\end{itemz}

\begin{itemz}[Notes]
	\item \cAriel{}'s nickname for you used to be ``Flounder.'' You have come to detest this name because of what it represents.
  \item Your black market contacts can provide you with a child on short notice if you deem the risk worth the reward. Simply send a handwritten note through a page requesting one from your contact. The delivery will be made 20 minutes later - ask a page for the child then. 
\end{itemz}

\begin{itemz}[Trivia]
  \item The Church of the Tides patron animal is the Sperm Whale.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cWitch{\MYname}} A powerful magician and family contact, long thought dead. Her real name is \cWitch{}. \cWitch{\They} could make you useful potions - for a price.
  \contact{\cAriel{}} Your former best friend and the target of your revenge.
  \contact{\cPrincess{}} A royal brat who thinks only of \cPrincess{\themself} and \cPrincess{\their} childish wants. You have no interest in doing \cPrincess{\them} any favors after \cPrincess{\they} got you caught at the border.
  %%\contact{\cPlant{}} Head of the Explorer's Guild and brother to \cKing{\King} \cKing{}.
  \contact{\cKing{}} \cKing{\King} of \pAtlantis{}. 
\end{contacts}

\end{document}
