\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cWillow{}}
%

You are \cWillow{}, crown \cWillow{\prince} of \pAmerica{}. You're 16, and practically a grown up - and you're tired of your parents bossing you around. They micromanage every second of your day. How are you supposed to learn to be a competent ruler when you never get to make any decisions yourself?

Six months ago, you decided that you'd had enough. You ran away. To be fair, you didn't get far - your parents sent half the kingdom after you. But you had three glorious days of freedom first. In that time, you rode north along the coast, avoiding towns and people as much as possible. The lack of authority figures trying to ruin your life was wonderful. You steered clear of \pAmerica{}n citizens as much as possible, but on the second night out, your curiosity got the better of you.

You were sleeping on the beach. \cAriel{\Parent} would be so upset if \cAriel{\they} knew, but that just added to the thrill of sleeping in the sand, still warm from the sun. You had been banned from going near the ocean for your whole life, and that big, mysterious expanse of water always intrigued you. Sounds woke you in the middle of the night. You looked around, and noticed a fire farther down the beach, with the sounds of music coming from that direction. You approached the fire to find three people, one of whom was waist deep in the water, singing and laughing and smoking something sweet.

The jovial group invited you to join them in merrymaking. Soon you were taking drags on the joints as they were passed around. You quickly got high on the \iDrug{\MYname} and weren't even surprised when the person in the water lifted himself onto a rock and revealed that instead of legs, he had a tail like a fish. ``You're, you're a merperson!'' you giggled.

The next morning, through your pounding headache, you realized the absurdity of it all. Merpeople didn't exist! Except... there by your bedroll was a pouch of \iDrug{\MYname}. You slipped it into your bags and continued to ride north on your horse. Late that day, the royal guard caught up to you. To your dismay, your \cAriel{\parent} was with them. \cAriel{} grounded you for the rest of your life and hauled you back to the palace.

A week later, you started to develop a craving for something you couldn't quite place. After trying and discarding all of your favorite sweets in the kitchen, you went to your room, grabbed the \iDrug{\MYname}, and slipped out of the castle.  You rolled a joint, just like your friends had taught you, and lit it up. Almost immediately the craving was sated, and everything was blissful and relaxing. Even the thought of being trapped in the palace for months until your parents relented on your punishment seemed more tolerable.

Everything was wonderful until you ran out of \iDrug{\MYname}, a month later. You started to panic. You had no idea how to get more. To your great relief, after almost a week of withdrawal, you got a message -- though it was delivered in a most peculiar way. A seagull alighted on your balcony and rapped at the window until you opened it and untied the note from its leg. The note was from the merman, and explained that he wanted to give you more \iDrug{\MYname}, but he would need something in return.  The question was innocuous. ``How many brothers and sisters do you have?'' You wrote the answer on the note (none, you are an only child) and sent the gull off. It returned that night with a two week supply of \iDrug{\MYname}.

Over time, the questions became less innocuous and more pointed, but your need for \iDrug{\MYname} became sharper. You kept answering them. Then things got interesting. Really interesting. Three weeks ago, the gull brought a note revealing just how much your parents don't trust you. Your \cAriel{\parent} \cAriel{} is a \cAriel{\mer}! Or, was - apparently \cAriel{\they} used a spell to turn \cAriel{\themself} human. And \cAriel{\they} had concealed it from you! Worse still, \cAriel{} was planning to return to the ocean for some conference or other with your grand\cKing{\parent}, three weeks hence, and had no intention of telling you. Your dealer promised you a month's supply of \iDrug{\MYname} if you could manage to go with \cAriel{\them}.

You puzzled about how to confront your \cAriel{\parent}. Luckily you noticed \cAriel{\them} slipping off one afternoon and heading for the shore. You snuck after your \cAriel{\parent}, only to get the biggest surprise of your life. There, waiting at the shore, was a \cKing{\mer}, wearing a crown and carrying a trident! You let them converse for about five minutes, until talk turned to the conference. Then you stepped out from behind the rocks you were hiding in, and confronted \cAriel{}. After the biggest fight of your life, \cKing{} interjected with just the proposal you were hoping for: \cKing{\they} proposed that you be allowed to come and see \pAtlantis{} for yourself. Your \cAriel{\parent} couldn't talk \cAriel{\their} way out of it.

Some things are awesome about being underwater. The novelty of breathing water doesn't seem to fade. And down here, your \cAriel{\parent} is too busy with political stuff to boss you around. If only you could find some way to come and go as you pleased\ldots{} Your dealer mentioned something about shape shifters at one point - humans who can turn into merfolk at will. Wouldn't that be cool if you could become one?

Some things, on the other hand, are not so awesome. Your cravings for \iDrug{\MYname} are getting worse -- much worse. Your grand\cKing{\parent} doesn't have any time to spend with you -- not that you \emph{need} the attention of an old \cKing{\mer} like \cKing{\them}, and something is making you tingle all over -- weird things keep happening around you. 

Your addiction to \iDrug{} is turning into a real problem. It started as a small craving every now and again, but as time wore on, you found yourself craving it more and more. Every couple of hours you had to slip off for a smoke. So far you've managed to conceal this addiction from your parents, and you intend to keep it that way. To that end, you brought a small stash with you from the surface - what should have been enough to stave off the craving. However, you can't exactly smoke underwater.  Chewing \iDrug{} works for you, but you've discovered the hard way that it does much less for you than smoking -- so your stash is no longer enough to get you through your trip.

This afternoon, you started to feel the effects of your last dose fade. Driven to distraction, you were forced to break the promised radio silence with your dealer to arrange for more. To your surprise, he didn't seem angry - rather, it seemed almost like he expected you. He quickly prepared a list of questions he'd like you to find the answers to, and promised you doses in repayment. Tonight you'll be working through an intermediary, \cReporter{}. You collect the answers to the questions, and trade them for doses of \iDrug{}. \emph{See the ``\mSpyBook{}'' membook for mechanics of this interaction}.

As you wandered the palace after arranging things with your dealer, you encountered an old merman, yammering on about something called ``\iWishingStone{\MYname}''. Despite yourself, you were intrigued. The stone apparently has all kinds of amazing powers. If you find it, you could use it to easily solve one of your current problems, or keep it around for later. (Find the ``\sOldMan{}'' in the entryway to begin this plot.)

\begin{itemz}[Goals]
  \item Get the \iDrug{} you need to satisfy your cravings. Refer to ``\gAddicted{}'' for details.
  \item Get turned into a shape shifter so you can visit underwater whenever you want.
	\item Figure out why weird things are happening to you, and make them stop.
	\item Find the Wishing Stone. Use it to do something awesome.
\end{itemz}

%
%Of course, your \cAriel{\pa} isn't \emph{that} cool. \cAriel{\They} tried to keep you from finding out about merfolk, and even banned you from playing in the ocean. Your parents can be so weird some times. They wouldn't even tell you why. But it didn't really matter because it is not like you listened to them anyway. You regularly snuck out of the palace and went down to the ocean to play, imagining you could breath under water, or turn into a fish.
%
%It turned out to be a good idea too, because one day, you came across your \cAriel{\pa} at the shore, talking with a \cKing{\human} half submerged in the water. You thought it was weird, so you you hid behind a rock, and watched. You were so surprised when the \cKing{\human} turned out not to be a \cKing{\human} at all. \cKing{\They} lifted \cKing{\them}selves out of the water, and you saw that \cKing{\they} had the tail of a fish instead of legs! You ran out to look, and found it was true -- \cKing{\they} was a \cKing{\mer}!! Your wildest dreams were true! 
%
%When your \cAriel{\pa} told you to go back to the palace and forget about the enchanted undersea world of merfolk, you understandably started to throw a tantrum. How could \cAriel{\they} tell you to just forget the biggest thing that had ever happen to you? You were really just getting started when the \cKing{\mer} admonished you to act like a \cWillow{\prince}. Apparently this \cKing{\mer} was actually your grand\cKing{\parent}! (That meant that \cAriel{\pa} had once been a \cAriel{\mer} too! Awesome!) \cKing{\They} promised that if you behaved, you could attend a ball in \pAtlantis{}!
%
%Obviously there are a \emph{bazillion} things you need to know about ``\pAtlantis{}'' and everywhere else under the sea, but even you know there are limits to what you can find out in one go. So, like the logical \cWillow{\prince} and future ruler that you are, you made sure to decide on a few priorities for yourself before the start of the ball.
%
%First, make friends! Any budding \cWillow{\prince} knows that making friends means power, so you want to make as many friends as possible. They're all going to be in one place and not going anywhere, so now would be a great time! You also wanna get to know your grand\cKing{\pa}, who your \cAriel{\pa} talks about a lot now that you know. \cKing{\They} sounds really nice, and maybe \cKing{\they}'ll give you presents!
%
%Second, your \cAriel{\pa} wouldn't tell you many stories about the world under the water, but \cAriel{\they} did tell you about the dancing. You were immediately enchanted by the idea of dancing \emph{in 3D}, so while you're here, you want to learn as much about that as possible!
%
%Third, as you were walking in here, you heard a crazy old man yelling something about a \iWishingStone{\MYname}. You don't know what that is, but it sounds super neat, so you really want to find it!
%
%This all sounds like quite a lot of stuff to do in just four hours at the ball! Of course, if you could find some way to become a \cWillow{\mer}, then you'd have all of the time in the world. Plus you'd get to move in 3D \emph{all the time}. Maybe you should work on that first, because that sounds kind of awesome...
%
%\begin{itemz}[Goals]
  %\item Find some way to become a \cWillow{\mer} without letting your \cAriel{\parent} find out!
  %\item Learn as many dance styles as possible.
  %\item Make as many friends as possible, especially with your grand\cKing{\pa}.
	%\item Find the \iWishingStone{}!
  %\item Find out everything else too. If you learn anything cool, go tell your \cAriel{\parent}.
	%\item Figure out why you feel funny. It might be because you're breathing water right now, but that doesn't sound \emph{quite} right...
%\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cAriel{}} Your \cAriel{\parent}. \cAriel{\They} \cAriel{\are} here to protect you and hang out with \cAriel{\their} family.
	\contact{\cKing{}} Your grand\cKing{\parent}. Is trying to get a treaty signed. It sounds kinda important, or something.
\end{contacts}

\end{document}
