\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bAssassin{}}

Only the highest ranking officials actually know the full plans of the Assassin's Guild. They have fingers in many plots, and pull many strings. The guild is heavily involved in \pPacifica{}n politics, but only as a shadow player.  They do not overtly oppose the \cPacificanRuler{\King}, but there is certainly no guarantee that their ultimate goal is not at odds with the \cPacificanRuler{\King}'s. The guild has also tried to infiltrate \pAtlantis{}. It is not known, even to most members of the guild, whether they were successful or not.\\

As a member of The Assassin's Guild, there are a few things you know. In no particular order, these are:

\begin{itemize}
  \item Children are often kidnapped and brought to the school to be trained from very early ages.
  \item All members of the Guild bear a tattoo on their left bicep, marking them.
  \item All members of the guild are highly trained in combat and subterfuge. Expect them to be excellent fighters and capable spies.
  \item The Assassin's Guild is located in the icy waters of the Bering Strait.
	\item A magical contract entered unwillingly can be broken with a Pactbreaker Ritual.
  \item The Assassin's Guild does not train magicians.\\
\end{itemize}

{\bf Missions and Guild Obligations:}\\
The Assassin's Guild is not a club you can come and go from at will. Once you have been inducted, you owe your life to the guild and are obligated to carry out every mission assigned to you, without drawing suspicion to the Guild. In very rare circumstances, the Guild may release someone from their obligation, but even once released from active duty, a member is never allowed to reveal Guild secrets on pain of death.

Should you discover that a Guild member has betrayed the Guild or abandoned their mission, it becomes your mission to remove this security risk. You should consider this on par with whichever mission you are currently serving for the Guild.

\begin{itemz}[Trivia]
	\item The guild has several branches, each with a small standing army, along with numerous spies and sleeper agents stationed all over the undersea world that could be pulled in to fight with enough notice.
\end{itemz}


\end{document}