\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bAtlantican{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

{\bf History of the War:}\\
The war with \pPacifica{} began several generations ago. No one remembers why \pPacifica{} attacked on that fateful day, but the aftermath is well remembered. Many thousands of \pAtlantis{}ns have died in the war. While the balance of power has tipped back and forth over the decades, the two kingdoms seem fairly evenly matched. Although \pAtlantis{} has appealed to the other major power, \pIndia{}, for aid, \pIndia{} has remained resolutely neutral in the conflict. Relatively recently, \pAtlantis{} has won a string of strategic victories. From this position of power, \cKing{\King} \cKing{} has generously chosen to extend the olive branch to \pPacifica{}.\\

\cKing{\King} \cKing{} opened negotiation talks with the \pPacifica{}ns nine years ago. Negotiations have been rocky. In the first eight years, several cease fires were issued and broken, and despite every effort, no meaningful progress was made in that time. However, in the past two years or so, \cPrincess{\Prince} \cPrincess{} has joined \cPrincess{\their} \cKing{\parent} in negotiations and it seems that progress is finally being made. \cKing{\King} \cKing{} has invited a delegation of \pPacifica{}ns to attend this year's \cExExKing{} Ball to sign the treaty that has been half a year in the making.\\


{\bf History of the Royal Family:}\\
\cKing{\King} \cKing{} \cKing{\are} the current ruler of \pAtlantis{}. \cKing{\They} \cKing{\have} ruled for almost 35 years and it is generally accepted that \cKing{\they} \cKing{\are} a good and benevolent ruler despite the terrible misfortunes that have defined \cKing{\their} rule.

\cKing{\Their} reign began in blood, when almost the entire royal family were killed by \pPacifica{}n assassins; only \cKing{} and \cKing{\their} younger \cPlant{\sibling} \cPlant{} survived. It is still a mystery how the strike force got into the palace. \cKing{} took up \iTrident{\MYname{}}, and rallied the kingdom to repel the ensuing invasion.

\cKing{\King} \cKing{} took a \cQueen{\spouse} soon after assuming the throne. \cQueen{\King} \cQueen{} was beautiful, gracious, and well loved by the people. They had two beautiful children. \cPrincess{\Prince} \cPrincess{}, the younger \cPrincess{\offspring}, has recently blossomed into a persuasive diplomat. The older \cAriel{\Prince} was named \cAriel{}; \cAriel{} spent almost all of \cAriel{\their} time with the Explorer's Guild and often neglected \cAriel{\their} royal duties. 

However, all is not well in \pAtlantis{}'s royal family. \cPlant{\Prince} \cPlant{} has become paranoid and delusional as the years have gone by. \cPlant{\They} publicly and loudly \cPlant{\simpleverb{claim}} all kinds of conspiracies are afoot. 21 years ago, \cQueen{\King} \cQueen{} was killed by \pPacifica{}n assassins. \cAriel{\Prince} \cAriel{} ran away from \cAriel{\their} royal duties and married a human \cEric{\prince}. The whole affair was hushed up by the royal family, so little is known about how \cAriel{\they{}} managed it. But, since \cKing{} dissolved the \pMagician{} almost immediately after, rumor has it that \cAriel{\they} used magic to become human. In the years since these tragedies, \cKing{} has become reclusive and erratic, and some believe \cKing{\they{}} may no longer be fit to be \cKing{\King}.\\

{\bf Religion:}\\
Most \pAtlantis{}ns subscribe to the Church of the Tides. The church worships the Moon Goddess for her power to control the tides. The church preaches love, forgiveness, and the salvation of the weak. It is believed that your soul will be reincarnated again and again until you live a life pure enough to earn you a place among the stars. The care of your eternal soul is particularly important, because there are spirits that dwell in the center of the earth, who if given the opportunity would imprison your soul for eternity.

The Moon Goddess requires religious rituals to be performed regularly on her behalf, or she can get\ldots tetchy.  At the Ball, the dance event organized by \cPrincess{\Prince} \cPrincess{} is dedicated to the Moon Goddess' worship.

While the Goddess can be benevolent and grant powerful boons, the Church of the Tides also believes that some individuals are cursed by the moon to be shape shifters (merfolk who can change between merfolk, human, and sharks), forever without a true form or identity. Shape shifters are unable to control their transformations, and when they do transform, they are a menace to everyone. The priests of the church have therefore taken it upon themselves to protect the citizens of \pAtlantis{} from shape shifters, hunting them down wherever they appear to terrorize an innocent community.\\

{\bf Guilds:}\\

The economy and government of \pAtlantis{} center around the guilds. As far back as anyone can remember, \pAtlantis{} has had four guilds that provide a division of tasks to help \pAtlantis{} run smoothly. They each elect one official for a two year term that make up a council that advises the \cKing{\King}.  Members of the royal family may belong to guilds but may not be elected to the council (they are not barred from holding high ranks in the Guilds, and the representative to the council is not necessarily the most powerful Guild member). The guilds are:
\begin{itemize}
  \item {\bf Explorer's Guild:} Composed of explorers, cartographers, archaeologists, historians, librarians etc. They handle the acquiring and storing of data (of all kinds) for \pAtlantis{}.
  \item{\bf Merchant's Guild:} Composed of traders, economists etc. They claim that despite the recent lull in the war, \pAtlantis{} is still on the brink of economic collapse.
  \item {\bf Guardian's Guild:} In charge of the military and police force of \pAtlantis{}. Their most prestigious role is to guard the royal family.
  \item {\bf Magician's Guild:}  Formally dissolved 14 years ago, but reinstated recently. Their seat on the council has not been reinstated.
  
  Despite the dissolution of the Guild, \cManta{} retained \cManta{\their} position as the court Magician. Since the reinstatement, \cKing{} has tasked \cManta{} with strictly regulating magic in \pAtlantis{}, and \cManta{} takes \cManta{\their} job very seriously. \cManta{} has an aggressive program that requires all magicians to register in a national registry, and submit all intended projects for review. As one of the most powerful magicians in \pAtlantis{}, even before the dissolution of the Magician's Guild, none wish to incur \cManta{\their} wrath. However, there are unconfirmed rumors that a few, very powerful, magicians refused to register. If they exist, they are considered criminals.\\
  
\end{itemize}
  {\bf A note about tarot readings}: Tarot readings, despite their mystical origins, are not considered magic and are therefore not subject to the same regulations. Tarot readings are common in \pAtlantis{}, and readers are often highly respected members of society.

{\bf The \cExExKing{} Ball:}
The attendee list for the \cKing{\King}'s private party includes:
\begin{itemize}
  \item The \pAmerica{}n representative, \cAriel{\King} \cAriel{}. It has been 14 years since \cAriel{} forsook Atlantis, so there is great speculation as to why \cAriel{\they} \cAriel{\have} chosen to attend this year.
  \item The \pPacifica{}n representative, \cPrince{\Prince} \cPrince{} and a small delegation of diplomats.
  \item The Explorer's Guild representative, \cPriest{}.
  \item The Merchant's Guild representative, \cSlave{}.
  \item The Guardian's Guild representative, General \cGeneral{}.
\end{itemize}


\end{document}