\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bExplorer{}}

As a member of the Explorer's Guild, you have access to certain information and supplies that are not readily available to the general populace of \pAtlantis{}.

{\bf History:}\\
The Explorer's Guild has a rich history of adventure and bringing wealth into \pAtlantis{}. The mission of the Guild is to explore and document uncharted areas of the sea, find and collect valuable flora and fauna, and bring back any sunken treasure or undersea wealth that they can lay their hands on.

Current members of the Explorer's Guild have access to the Explorer's Guild supplies, which are useful for a variety of medicinal and construction purposes. They also have access to the Guild archives, where the records of the Guild's activity are stored. 

{\bf Betrayal:}\\
If any member of the guild suspects another member of betraying the ideals and mission of the guild, they can submit a formal accusation. An independent investigation will be conducted by the guild over the next few weeks, and the judicial review board will make final ruling within a month. During the investigation, the accused is still considered a full member, and retains access to guild supplies and information.

{\bf Current Members in Attendance Tonight:}
\begin{itemize}
\item \cPlant{} (Head of Guild, just celebrated \cPlant{\their} \cOsiris{\MYnumber}th birthday.)
\item \cPriest{} (Representative to the Concil of Advisors)
\item \cPrincess{}
\end{itemize}

{\bf Former Members in Attendance Tonight:}
\begin{itemize}
\item \cAriel{}
\item \cKing{}
\end{itemize}

{\bf The Treaty:}\\
As a member of the Explorer's Guild, you are interested in having the treaty accomplish several things. 

The most important is procuring the \pGazaStrip{}. As a large, uncharted area of the ocean that has been rumored to contain great wealth, the Guild is eager to explore it, find the treasure within, and complete their knowledge of the oceanic region surrounding \pAtlantis{}. The region is clearly within \pAtlantis{}n borders anyway. {\bf In the absence of new information, if the treaty does not include \pAtlantis{} gaining control of the \pGazaStrip{}, then you should highly consider vetoing the treaty.} If control cannot be established, making it a demilitarized zone is at least preferable to having \pPacifica{} gain control of it.

The Guild is also pushing for open borders, as it would give you a much wider range of area to operate in, for further exploration and understanding of the sea. Given a recent budget crisis, the Guild is also interested in the influx in cash that reparations would represent for \pAtlantis{}.

%%Induction ritual


\end{document}