\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bGuardian{}}

As a member of the Guardian's Guild, you are charged with the protection of \pAtlantis{} and all of its citizens.

{\bf History}\\
The Guardian's Guild has a rich and noble history. The guild has been the protector of \pAtlantis{} as far back as the records go. What began with a loose alliance of town militias has grown into one of the best organized and farthest reaching militaries under or above the ocean.

The Guild trains bodyguards for high ranking officials, keeps the peace in daily \pAtlantis{}n life, and deals with the day-to-day of the ongoing war. Generals consult with \cKing{\King} \cKing{} and launch assaults against \pPacifica{}. So far, \pAtlantis{} is winning the war, although at a terrible cost. The \pPacifica{}ns are devious and untrustworthy, but superior tactics and strategy have so far led to several key victories.

{\bf High Ranking Officials}\\
Head of the Guild: \cKratos{} (\cKratos{\MYnumber} years old)\\
Representative to the Council of Advisors: General \cGeneral{}

{\bf The Treaty}\\
As a member of the Guardian's Guild, you are interested in having the treaty accomplish several things. 

The two most important things to the Guardian's Guild are the issues of the prisoners of war and the threat that ``peace'' poses to your nation.  The Guild does not trust \pPacifica{}. Without proof of their trustworthiness, you cannot in good conscience agree to more than a ceasefire. {\bf In the absence of new information to prove their trustworthiness, or especially if the treaty includes a military alliance between \pAtlantis{} and \pPacifica{}, then you should highly consider vetoing the treaty.} However, several important \pAtlantis{}n officials have been captured, including the head of the Guardian's Guild, \cKratos{}, and the continued success of the Guild's military ventures depends in significant part to their safe return. {\bf In the absence of new information, if the treaty doesn't contain an exchange of Prisoners between \pAtlantis{} and \pPacifica{}, then you should strongly consider vetoing the treaty.}

The Guild is also against open borders, for similar reasons. There's no discernible benefit to \pAtlantis{}, and the additional security required would require time and funding that the Guardian's Guild does not currently have.

\begin{itemz}[Trivia]
	\item The guild has discussed the idea of a draft, but rejected it as something that the citizens would never support.
\end{itemz}


\end{document}