\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bHumanShort{}}

{\bf The Royal Family:}\\
The royal family of \pAmerica{} is small. \cEric{\King} \cEric{} rules \pAmerica{}, with \cEric{\their} \cAriel{\spouse}, \cAriel{\King} \cAriel{} at \cEric{\their} side. \cAriel{} is from \pAtlantis{}. Much of the country was shocked to learn that communication between the nations was even possible, never mind the idea that \pAtlantis{} might be friendly, given ongoing altercations with \pPacifica{}. \pAmerica{} has not yet adopted \cAriel{} as their \cAriel{\King}, despite \cAriel{\their} having lived among them for 14 years.

\cEric{}'s father was lost in a storm, 21 years ago. A regent ruled until \cEric{} came of age, and then peaceably transfered power to the new \cEric{\King}. \cEric{}'s \cSlave{\sibling} was killed, 14 years ago, during an attack on the palace.\\

{\bf Religion:}\\
The human kingdom of \pAmerica{} practices a religion that worships the sun. The Sun God brings life to all things on the land. The summer solstice is the most sacred day of the year, and the midsummer festivals are elaborate and expensive. There is no greater omen than to be married under the noon-day sun on a clear day.

Humans fear the ocean, and its dark depths, for they conceal the mighty kraken. The kraken is hated by all and expeditions often set out to kill the beast. Only some of them return. It is believed that the storm that killed \cEric{}'s father was summoned by the kraken itself. Only a devil storm could have bested that crew and left no survivors.\\

{\bf Everyday life in \pAmerica{}:}\\
Life in \pAmerica{} is simple. \pAmerica{} is at peace with its neighbors, and so much of its populace is farmers. A few brave souls are fishermen, or mariners,  but for the most part, the citizens of \pAmerica{} prefer to stay on land and give thanks to the Sun God for his bounty.

Magic is extremely rare in \pAmerica{}. There is very little magic to be found anywhere on land. Magicians are therefore regarded with some suspicion. They are not necessarily outcasts though, and a few, like Merlin, have become prominent advisors to rulers.

14 years ago, \cPolio{} was a big problem in \pAmerica{}. It has devastated much of several previous generations. When you were last in \pAmerica{}, people were desperately scrambling for a cure. You don't know if they succeeded in finding one.

{\bf Relationship with \pAtlantis{}:}\\
\pAmerica{} has slowly been building a tenuous relationship with \pAtlantis{}. Over the past couple of years, informal discussions  have begun to occur between the two nations, led by \cAriel{\King} \cAriel{}. Many people are hopeful that \pAtlantis{} could become a lucrative, new trading partner.\\

{\bf Relationship with \pPacifica{}:}\\
 \pAmerica{} has a much less amicable relationship with \pPacifica{}. The merfolk of \pPacifica{} attack \pAmerica{}n ships on sight, and the concept of trade talks is laughable. No one really knows for sure why \pPacifica{} is so aggressive, but it may have something to do with the kraken.

\end{document}