\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bMagician{}}

As a member of the Magician's Guild, you are part of a powerful cabal of magicians. The guild spans \pAtlantis{} and \pPacifica{}, and has a long and storied history.

{\bf History:}\\
The Magician's Guild began in \pAtlantis{} 300 years ago. At that time, \pAtlantis{} and \pPacifica{} were friendly with each other, and so the guild soon expanded to incorporate magicians in both oceans. Information and spells flowed freely between the branches of the guild, and both countries profited from the exchange. For many years, the Magician's Guild worked closely with the Church of the Tides to hunt down shape shifters since some spells can be used to disrupt a shape shifter's transformation.

When relations between the countries soured, the Magician's Guild kept up friendly contact for some time, although the exchange of information was somewhat more limited. When \cKing{\King} \cKing{} disbanded the Magician's Guild in \pAtlantis{}, the \pAtlantis{}n magicians either went to ground or fled to \pPacifica{}. Only \cManta{}, the \cKing{\King}'s trusted advisor, stood \cManta{\their} ground. In the years since, \cManta{} has persuaded \cKing{} to relax the ban on magic. Licensed magicians may now formally practice magic. There are still a few spells and potions that are illegal, and as the guild representative to \cKing{\King} \cKing{}'s court, \cManta{} is in charge of regulating magicians.

{\bf Factions}\\
While \cManta{} is nominally the head of the Guild in \pAtlantis{}, this is far from the whole story. There are two factions in \pAtlantis{} who are vying for control of the guild. {\bf The White Tower} is led by \cManta{} and {\bf The Society of Free Magicians} is led by \cWitch{\MYname}. The White tower is a guild centered in the \pAtlantis{}an capital whose strict regulations and scientific approach have produced many magical breakthroughs. The Society of Free Magicians are more lax in their book-keeping, and more dispersed, and as a result have developed many novel practical applications for magic. The two factions are well matched, and there is no resolution to this conflict in sight.

The \pPacifica{}n branch of the guild calls itself the {\bf The Royal Spell Guard}, and is strictly loyal to \pPacifica{}.

{\bf Regulation of Magic:}\\
Magic is strictly regulated in \pAtlantis{}. All members of the \pAtlantis{}an Magician's guild are licensed magicians and so may practice freely. However, egregious acts of magic may cause authorities to revoke your license. Performing illegal magic is punishable by death.

{\bf Inducting new Members}\\
\emph{Refer to the greensheet ``\gInduction{}'' for details on the actual mechanics of induction} \\
All magicians take the induction of new members very seriously as each new member is sworn directly into a faction. The number of members of the faction is strongly related to how much power the faction wields within the guild.

{\bf Spells and Potions:}\\
The spells and potions a magician can use are based on their level. Spells are represented as ability cards and are used as instant abilities. All potions follow a standard brewing strategy (see ``\gPotions{}''). Potions have distinctive colors and can be recognized by magicians by their color (Lay people don't know what color the different potions are). Potions are represented as item envelopes that {\bf must be obtained from the GM. TELL A GM WHEN YOU --START-- BREWING A POTION}.

Some ingredients are common across the ocean floor and easily obtainable. Some are rare or difficult to obtain, and acquiring them during the ball may be difficult. The Explorer's Guild collects rare and valuable items, some of which may be useful for potions. A few ingredients are known to be dangerous. \emph {Refer to the ``\gPotions{}'' greensheet for details.}

Potions can be administered in 2 ways. A willing or helpless target can drink the potion, in which case, the person administering the potion should hand over the potion envelope to the target. An ignorant target can also be injected with a potion. The person administering the potion must successfully stick a certain number of stickers on the target without being caught in the act by the target or anyone else. (Stickers can be acquired at the cauldrons.) The person who is attempting to administer a potion should then find a GM, explain who the potion is targeting, and hand over the potion. The GM will handle the rest.

{\bf Current Members:}
\begin{itemize}
\item \cManta{} - Head of The White Tower faction.
\item \cWitch{\MYname} - Head of The Society of Free Magicians.
\item \cBodyguard{} - A member of The Royal Spell Guard.
\end{itemize}

\begin{itemz}[Trivia]
	\item Each of the three factions stands at about 500 practicing members strong, though there are rumors of underground magicians.
\end{itemz}

\end{document}