\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bMerchant{}}

As a member of the Merchant's Guild, you are charged with safeguarding the economy of \pAtlantis{} and representing the common worker.

{\bf History}\\
The Merchant's Guild protects the economic interests of \pAtlantis{}, and represents traders, artisans, economists and many other sectors of the \pAtlantis{}n economy. In the recent negotiations with \pPacifica{}, the Merchant's Guild has played a very prominent role. The guild has many demands and a large stake in the treaty. In fact, all of \pAtlantis{} has a larger stake than they know. Economists predict that \pAtlantis{}'s economy will collapse within a decade if the war expenditures aren't curbed.

{\bf High Ranking Officials}\\
Head of the Guild: \cNautilus{} -- \cNautilus{} is away on unexpected, urgent personal business and could not attend tonight's ball. \cNautilus{} is \cNautilus{\MYnumber} years old.\\
Representative to the Council of Advisors: \cSlave{}

{\bf The Treaty}\\
As a member of the Merchant's Guild, you are interested in having the treaty accomplish several things. 

Primarily, you would like to see peace between your two nations. The war has been a constant drain on the nation's coffers, and the fear in the populace has damaged the economy. Peace would also offer many new trade opportunities, which would be the only way to reverse the damage inflicted by such a prolonged war. {\bf In the absence of new information, if the treaty doesn't include long-term peace with \pPacifica{}, then you should highly consider vetoing the treaty.}

The Guild is also looking to receive reparations for the \pPacifica{}ns aggression and the economic damage \pAtlantis{} has sustained. The war is essentially the fault of the \pPacifica{}ns, and because of this, the Guild feels that receiving compensation to help speed along recovery is a valid demand. The Guild would further like open borders, as this would foster trade and begin to repair the massive damage the war has done to the economy.

\end{document}