\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bPacifican{}}

You are a citizen of \pPacifica{}, and therefore know much about the history of \pPacifica{}, but little about the strange realm of \pAtlantis{} where you now find yourself.

{\bf History of the War:}
The war with \pAtlantis{} began several generations ago. No one remembers why \pAtlantis{} attacked on that fateful day, but the aftermath is well remembered. Many thousands of \pPacifica{}ns have died in the war. While the balance of power has tipped back and forth over the decades, the two kingdoms seem fairly evenly matched. \pPacifica{} reached out to \pIndia{} in hopes of tipping the balance of power, but they have remained stubbornly neutral. Recently however, \pPacifica{} has been consolidated its forces for an inevitable, crushing counterattack while suffering minimal losses. It is from this position of power that \cPacificanRuler{\King} \cPacificanRuler{} has chosen to parlay with the \pAtlantis{}n royal family.

\cKing{\King} \cKing{\MYname{}} has sought negotiations since a decade ago, but negotiations have always been rocky. Several cease fires have been issued and broken, and despite every effort, no treaty has materialized. Though hopes for this treaty are similarly slim, \cKing{\King} \cKing{} has invited a delegation of \pPacifica{}ns to attend this year's \cExExKing{} Ball to sign the treaty that has been half a year in the making.

{\bf The Treaty:}
In order to ratify the treaty, the head of the \pPacifica{}n delegation must sign it. \cPrince{} is currently in charge of the delegation and is considered \pPacifica{}'s primary representative. Should the unthinkable happen, it is important that everyone in the delegation understand the chain of command. \cDiplomat{} can sign in \cPrince{}'s place, should \cPrince{} be dead, but then \cDiplomat{} will have the unenviable task of returning to \pPacifica{} and explaining to \cPacificanRuler{\King} \cPacificanRuler{} why \cPacificanRuler{\their} \cPrince{\offspring} didn't come back. Should both \cPrince{} and \cDiplomat{} be dead, technically \cSpy{} has the authority to sign a treaty, but at the point where the crown \cPrince{\prince} of \pPacifica{} and one of your country's most prominent diplomats are dead, you should be \emph{very} wary of signing so much as a ceasefire with \pAtlantis{}.

In addition, \pPacifica{}n law dictates that ``no peace shall be established with a foreign power without a joining of the blood lines.'' In other words, \pPacifica{} will accept no treaty for peace without a marriage between a member of \pPacifica{}n royalty, and a member of \pAtlantis{}n royalty.

{\bf The Royal Family:}
\cPacificanRuler{\King} \cPacificanRuler{} is a wise and just ruler. The \cPacificanRuler{\King} always listens to the will of the people and advocates for their interests, and so is much beloved in \pPacifica{}. \cPacificanRuler{\They} is not without fault, though, as \cPacificanRuler{\they} can often be covetous of wealth and wrathful in the face of insult. In one of \cPacificanRuler{\their} worse moods, the \cPacificanRuler{\King} demanded a token of respect be retrieved from \pAtlantis{} by the visiting delegation. Anyone who has worked directly with the \cPacificanRuler{\King} knows that painful punishment awaits those that do not fulfill \cPacificanRuler{\their} whims.

The former \cPacificanRulerSpouse{\King} \cPacificanRulerSpouse{} was also beloved by the people, but was unfortunately a bit too hands on with \cPacificanRulerSpouse{\their} forays into the enemy field, and was killed years ago. In \cPacificanRulerSpouse{\their} place, \cPrince{\Prince} \cPrince{} has stepped up to fill \cPrince{\their} \cPacificanRulerSpouse{\parent}'s role. \cPrince{} commands border patrols and leads small skirmishes regularly, as well as acts as a general in more major battles. \cPrince{} is also quickly becoming an accomplished diplomat, and as such has been entrusted with the delicate Neptune Ball political situation. \cPrince{\they} is much beloved by \cPrince{\their} \cPacificanRuler{\parent}, \cPacificanRuler{\King} \cPacificanRuler{}, though \cPacificanRuler{\they} can be just as harsh on \cPrince{} as any of \cPacificanRuler{\their} other subjects.\\

{\bf Current Life in \pPacifica{}:}
While far from peaceful, life in \pPacifica{} is at least free and governed fairly. The war is thought of as a necessary evil, one which the people strive to take their minds off of with many festivals and religious ceremonies. Waltz is a popular pastime, and is partaken of by commoners and nobles alike.

\begin{itemize}
  \item {\bf Religion:} \pPacifica{}ns worship the power of the squid, who are the incarnations of ancient Gods upon this land. Primary among these is the Kraken, whose crushing power represents the most ancient of Gods, and whose very passage consecrates the waters through which it passed. The humans, who hunt the squid, are your mortal foes for this very reason. The Kraken has only been sighted by merfolk half a dozen times, and the \pGazaStrip{} is holy water, because it is the last place that the Kraken was sighted. On \cKraken{\MYname}, \cLiar{\MYname} awoke to behold the Kraken as it swam above him, across the \pGazaStrip{}. Despite near continual monitoring ever since (at great risk given that the \pGazaStrip{} is on the border with \pAtlantis{}), the Kraken has not been seen again.
  \item {\bf \cPolio{}:} \cPolio{} is the disease that threatens the very existence of \pPacifica{}. The symptoms are flu-like at first, but quickly escalate into life-threatening territory. Even worse, if you survive the initial symptoms, you are permanently crippled, forever short of breath and have skin mottled by boils. It also reduces fertility, a condition that can be easily passed to your children -- if you are lucky enough to have them. The disease has reached epidemic proportions, especially among the poor, and shows no sign of stopping. 
  \item {\bf The Black Market:} It is well known in Pacifica that there is a merchild smuggling ring of great influence. The ring smuggles children into and out of \pPacifica{}, selling them to the families that can no longer concieve, either because of \cPolio{} or for other reasons. \cPacificanRuler{\King} \cPacificanRuler{} nominally opposes such criminal activity, but as their main focus is on stealing merchildren from outside of \pPacifica{}, efforts to stamp them out have been half-hearted at best.
  \item {\bf The Assassin's Guild:} The Assassin's Guild is an extremely influential force in \pPacifica{}. In generations past, the Assassin's Guild openly sold the skills of assassins, but in recent years, have cleaned up their act, and pursue legitimate contracts openly. The \cPacificanRuler{\King} has publicly pardoned the organization after an extensive audit, and has welcomed them back into the larger political discourse.
  \item {\bf Magic:} Magic is free and celebrated in \pPacifica{}, and is often employed to improve the lives of its citizens. Magicians are also often employed to supplement the armed forces and protect important figures.
  
  Magic is not so free in \pAtlantis{}, and you have been warned repeatedly that revealing the identity of a magician in your party could compromise the safety of the magician in question, the whole diplomatic contingent, and even the possibility of signing a treaty tonight.
  
  Despite the strict control of magic in \pAtlantis{}, tarot is still widely practiced. While readers are fairly rare in \pPacifica{}, they are common in \pAtlantis{}, and many people take advantage of the foretelling abilities of the tarot.
\end{itemize}

{\bf Goals:} 
\begin{itemize}
	\item Negotiate for and sign a fair treaty with \pAtlantis{}. A peace treaty must be accompanied by a royal marriage.
	\item Find an item marked ``valuable'' to bring back for your \cPacificanRuler{\King}. A ``\iSignetRing{}'' will not suffice. It must be a item that \cPacificanRuler{\King} \cPacificanRuler{} doesn't already have.
\end{itemize}

\end{document}