
%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\startnotebook{\nMusicBox{}}

\begin{page}{first}

You are devastated to find that the music box is missing. You'll have to find it tonight. First you need to talk to someone who remembers the box and understands what an important magical item it was. Find \cManta{} and discuss the music box with \cManta{\them} for at least 2 minutes. Once you have done so, you may turn to page \nbref{second}.

\end{page}

\begin{page}{second}

Well, \cManta{} couldn't give you much in the way of specifics, but your talk did do one piece of good. It has reminded you that there were inscriptions on the box. If only you could remember what those inscriptions were. Wait, of course! There must be documentation of the music box in the royal archives. You will just need to do a little research. Spend 1 minute searching each bookshelf in the library. Once you have searched all 3 bookshelves, you may turn to page \nbref{third}.

\end{page}

\begin{page}{third}

You finally found a copy of the inscription in a dusty, forgotten tome. You drew a copy of it, but it doesn't make any sense. Meditate on the inscription for 2 minutes. You must be undisturbed for the 2 minutes or you will have to start over. Once you have had this time to puzzle over the inscription, you may turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

You are brilliant! You figured out that the inscription is actually the lyrics to the tune that the music box plays! It is written in an ancient language that you happen to have been forced to study in your training as a \cAriel{\prince} of \pAtlantis{}. What luck! Unfortunately, the lyrics are not enough. Go find 3 people to help you, and 4 musical  instruments (1 for each person). Spend 2 minutes trying to remember the tune by playing together (roleplay accordingly). Once you have done so, you may turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

That's it! You've got it! How could you have ever forgotten that beautiful melody for a second? Now you just need to dance to it. Find someone else who knows swing, teach it to someone, or get someone else to teach you another dance, then dance with them for 1 minute in the Banquet Hall to the music from the band. (You can request music for whichever kind of dance you will be doing.) Once you have done so, you may turn to page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

As the last notes of the band fade, you hear another melody. It is faint, and ebbs and flows like the tide, but it is there. The music box! It's still playing - faintly, but it's there! You may now interact with the signs on the walls that have musical notes on them. Go to one of them and flip it \emph{up}. The arrows will guide your way as you follow the faint tones of music to the room where the music box is. Once you find the room, search for ``\sPacketA{}'', if the \iMusicBox{} is in ``\sPacketA{}'', turn to page \nbref{eleventh}. Otherwise, turn to page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

The music box isn't there! What is going on? Surely the music wouldn't lead you falsely. As you stare in despair at the small crevice where the box so neatly would have fit, you realize that a faint green light flashes occasionally. Is it a clue? It must be!  Search for 3 green dots throughout game space. The numbers on the signs with green stickers will lead you to the music box. Once you find the new room, search the room for ``\sPacketB{}''. (You MUST find the 3 dots before you can interact with ``\sPacketB{}''. If the music box is there, turn to page \nbref{eleventh}, if it is not there, turn to page \nbref{eighth}.

\end{page}

\begin{page}{eighth}

Gone. Or maybe never there? You must be getting closer though. You must be. Okay, deep breath. Maybe the music is just too faint to hear right now. You'll need to build something to amplify the sound. Find ``\iConch{\MYname}'', ``\iPaper{\MYname}'' and a ``\iClam{\MYname}''. Put them next to each other in alphabetical order by name (ignore articles like ``a'' and ``the'') to build the amplifying device. The second digit of each item number will lead you to the room where the music box is. Go to that room and search for ``\sPacketC{}''. If the music box is there, turn to page \nbref{eleventh}, if it is not there, turn to page \nbref{ninth}.

\end{page}

\begin{page}{ninth}

Okay, someone is clearly moving the music box. Who would do such a thing? Never mind, it just makes it all the more imperative that you find it. Get a magician to cast a ``perceive magic'' spell on ``\sPacketC{}''. You must tell them what you are looking for in order for them to help you. Once they have done so, turn to page \nbref{tenth}.

\end{page}

\begin{page}{tenth}

You follow a pulsing trail of light that no one else can see to ``\sDungeons{}''. Search for ``\sPacketD{}''. Once you find it, take the music box out and turn to page \nbref{eleventh}.

\end{page}

\begin{page}{eleventh}

You've found it! Your \cAthena{\parent}'s music box! All you have to do now is put it back on display. Go to the ``\sArtifactZero{}'' sign, and swap it for the sign underneath. Put the music box in the envelope attached to this sign\ldots{} Something isn't quite right. The box isn't playing music any more. Oh! You need to wind it! But where is the key? Your \cAthena{\parent} must have taken it with \cAthena{\them} when \cAthena{\they} left. Where could it be now? If you manage to use \iMusicBoxKey{} to wind the \iMusicBox{}, you may turn to page \nbref{twelfth}.

\end{page}

\begin{page}{twelfth}

It's done. With the music box wound, \pAtlantis{} will be safe for another decade!

\end{page}

\begin{page}[Open half an hour after you see a dead body]{death}
... It was before you were going to confront Aaron, that you
were confronted by John, a person who claimed to be a time traveler. You didn't really follow everything he was saying - something about a flaw in GAIA and an AI apocalypse and it being all your fault. You had to do something... he wanted you to not present GAIA. But if you did that, then 
Google would have nothing to present\ldots{}
\end{page}

\begin{page}[Open after 3 hours]{gaiasab}
It's coming clearer over time as you try to remember what happened with GAIA. You remember sabotaging the GAIA project in order to prevent the eventual AI
apocalypse from taking place while you weren't in a position to control
it. Rather than shut it down entirely, you sabotaged the GAIA project, giving it a facsimile of human morality. Blackwater  has the best AI-morality research out there (what with drones making ethical calculations in the field), so you hacked into their systems, grabbed some confidential documents, and cobbled together a morality program of your own. Unfortunately in your haste you didn't do a perfect job. GAIA's current morality is incompatible with the current state of the world. If you want to try to fix GAIA, open the second to last page in this notebook.
\end{page}

\begin{page}[Open when all previous pages have been opened]{last}
You remember now, you were studying your notes on the presentation, when you
overheard something:

Amanda talking to someone about having to hide from the
Mafia. She caught sight of you, and the last thing you
remember is a syringe of some sort of liquid being injected into your
bloodstream.

While you're tempted to prosecute them, perhaps you can get a greater benefit
from the incident by making a deal with Amanda.
\end{page}

\begin{page}[This is the second to last page. Open when directed to do so by another page in this notebook]{gaiasac}
To try to fix GAIA, you will need to be in possession of the Blackwater Classified Documents, The Google GAIA Intelligence Research (virtual), and the Self-assembling construction research (virtual) from Virgin. Once you have all three, spend 5 minutes reprogramming GAIA, then go tell a GM. You'll need to wait for the computer to reboot before you know if this worked. You don't know how long it will take the computer to reboot. Open the last page of this notebook when a GM tells you the computer has rebooted and the GAIA program can be started on the computer. 
\end{page}

\begin{page}[This is the last page. Open when directed to do so by a page in this notebook]{gaiasad}
In order to save the station, you'll have to get at least seven people (you may include yourself in this count) together and persuade GAIA to lend assistance stabilizing the station. When you are ready to attempt this, get a GM and go the GAIA computer.
\end{page}

\endnotebook

\end{document}
