\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gAddicted{}}

You are addicted to \iDrug{}. Normally you would smoke \iDrug{}, but since that doesn't really work under water, you've been chewing it. To your great frustration, chewing is far less effective at calming your cravings. You can already feel your dose this afternoon fading, and you have only one left.

Throughout the evening tonight, you will have to continue to take doses of \iDrug{}. You will need to acquire more doses from your dealer. See the ``\mSpyBook{}'' membook for details of this mechanic.)

\begin{enumerate}
	\item Within 5 minutes of \cTFifteen{\MYname{}}, you must take 1 dose.
	\item Within 5 minutes of \cTOneFifteen{\MYname{}}, you must take 2 doses.
	\item Within 5 minutes of \cTTwoFifteen{\MYname{}}, you must take 2 doses.
	\item Within 5 minutes of \cTThreeFifteen{\MYname{}}, you must take 3 doses.
\end{enumerate}

If you don't get your doses on time, you start to experience withdrawal. Once you hit withdrawal, you go into a confused rage. You must make a knock out attack on the first person you see with your full CR. If you miss multiple doses, you must attack 1 new person for each missed dose. Once you have attacked as many people as doses you have missed, you must fall unconscious for 5 minutes. Withdrawal applies each hour you don't get your doses.

\iDrug{} has some positive effects and some negative effects. Immediately upon consumption, it will boost your CR by 1 for 10 minutes, but then it will reduce your base CR by 1 for the ten minutes following that. The buffs do not stack or cancel each other out.

{\bf N.B. If anyone in your family finds out about your addiction, give them the mem-packet related to this.}

\end{document}