\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gBackground{}}

As a member of the Guardian's Guild, you have the ability to perform a background check on anyone in game. This process will take some time, but may provide you with valuable clues as to the identity of your mafia suspect.

To do a background check on someone:
\begin{enumerate}
\item Spend 3 minutes engaged in conversation with your target. You need this time to deduce what would be most useful records to check. Try to get as much information about their past out of them as possible.
\item Start a 5 minute timer. This represents sending a request out to your contacts to see what they can dig up for you.
\item See a GM for what you learned.
\end{enumerate}

\textbf{Note:} You may only engage this process for one character at a time. You may not start a conversation with a new person for the purpose of this mechanic until you have the results of the previous inquiry. For example, it will take an absolute minimum of 16 minutes to acquire information on two characters, since each takes a total of eight minutes without overlap.

You may wish to keep notes on this sheet regarding what you have learned about various people. This trumps the usual restriction on writing in game information down on out of game documents - this represents your character's superior ability to keep track of these details, without requiring it of the player should you prefer not to attempt to keep it all in your head.

Your background checks may provide useful information other than whether someone is your suspect.  You may continue to perform background checks even after finding your suspect.

\end{document}