\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gBackgroundGM{}}

This document contains the information \cGeneral{\full} gets from \cGeneral{\their} ``\gBackground{}'' greensheet mechanic. \cGeneral{\They} will give you a name, and you can read off to them the information for the given character. \textbf{Please do not just give them this sheet, or show it to them. This is to ensure that \cGeneral{\they} \cGeneral{\are} adhering to the mechanic.} If they come to you again with a new name in less than 8 minutes you should review their greensheet with them and emphasize the time required. You don't have to track this exactly, but you should be aware that the mechanic takes 8 minutes to execute for \textbf{each character it is used on}, but a careless reading may assume you can do it in parallel, thus reducing the time to only 5 minutes.


\begin{itemize}
	\item \textbf{\cPlant{\full}:} This is the \cKing{\King}'s \cPlant{\sibling}. \cPlant{\They} \cPlant{\are} paranoid but harmless. \cPlant{\They} \cPlant{\are} not your suspect.
	
	\item \textbf{\cKing{\full}:} This is the \cKing{\King}. \cKing{} has no secrets to hide. \cKing{\They} \cKing{\are} not your suspect.
	
	\item  \textbf{\cQueen{\full}:} \cQueen{}'s history is incomplete. No records of \cQueen{\them} extend more than 21 years back. This is unsurprising as this is when \cQueen{\they} fled the capital. On the other hand, \cAthena{} has no history beyond 34 years ago, despite being considerably older than that\ldots{} Still, \cQueen{\they} \cQueen{\are} not your suspect.
	
	\item \textbf{\cSlave{\full}:} This old \cSlave{\mer} is part of the Merchant's Guild. Oddly enough, \cSlave{\they} \cSlave{\have} no records more than 10 years back\ldots{}. \cSlave{\They} \cSlave{\are} not your suspect though.
	
	\item \textbf{\cWitch{\full}:} This young \cWitch{\mer} has no records more than 10 years back\ldots{}. \cWitch{\They} \cWitch{\are} not your suspect though.
	
	\item \textbf{\cPriest{\full}:} This \cPriest{\mer} seems to be connected to the the growing black market for children. Something smells fishy here. {\bf \cPriest{\They} \cPriest{\are} your suspect.} You may open page 2 of your research notebook entitled ``\nMafia{\MYname}''.
	
	\item \textbf{\cPrincess{\full}:} This is the crown \cPrincess{\Prince} of \pAtlantis{}. \cPrincess{\They} \cPrincess{\have} nothing to hide and \cPrincess{\are} not your suspect.
	
		\item \textbf{\cReporter{\full}:} This is the top castle correspondent for the \pAtlantis{}n news service. \cReporter{\They} \cReporter{\simpleverb{write}} an awful lot of letters to an address in the Cape of Good Hope that doesn't actually exist. Certainly suspicious, but \cReporter{\they} \cReporter{\are} not your suspect. (OOC Note: The Cape of Good Hope is the southern tip of Africa.)
	
	\item \textbf{\cAriel{\full}:} \cAriel{} is now \cAriel{\King} of \pAmerica{}. \cAriel{\They} can't be involved with the mafia and \cAriel{\are} not your suspect.
	
	\item \textbf{\cWillow{\full}:} \cWillow{} is just a kid. What trouble could \cWillow{\they} possibly be up to? \cWillow{\they} \cWillow{\are} not your suspect.
	
	\item \textbf{\cManta{\full}:} \cManta{} has a very interesting history, with many\ldots{} suspicious\ldots{} gaps. You may want to keep an eye on \cManta{\them}. \cManta{\They} \cManta{\are} not your suspect though.
	
	\item \textbf{\cDiplomat{\full}:} As a \pPacifica{}n, your information on \cDiplomat{} is limited. But from what you can tell, \cDiplomat{\they} \cDiplomat{\simpleverb{seem}} to appear out of nowhere about 3 years ago. \cDiplomat{\They} \cDiplomat{\are} not your suspect though.
	
	\item \textbf{\cBodyguard{\full}:} As a \pPacifica{}n, your information on \cBodyguard{} is limited. What records you do find are clean as a whistle. A good choice for the crown \cPrince{\prince}'s bodyguard. \cBodyguard{\They} \cBodyguard{\are} not your suspect.
	
	\item \textbf{\cPrince{\full}:} As a \pPacifica{}n, your information on \cPrince{} is limited, but \cPrince{} is the \cPrince{\Prince} of \pPacifica{}, and apparently without anything to hide. \cPrince{\They} \cPrince{\are} not your suspect.
	
	\item \textbf{\cSpy{\full}:} As a \pPacifica{}n, your information on \cSpy{} is limited, but \cSpy{\they} \cSpy{\simpleverb{appear}} to have no record beyond 17 years ago. \cSpy{\They} \cSpy{\have} also been asking around quietly about ``adoption.'' \cSpy{\They} \cSpy{\are} not your suspect, but might lead you to your suspect if you're lucky.
\end{itemize}

\end{document}