\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gBuff{}}

You have created a special potion that is unknown to other magicians. This potion causes the target's CR to increase by 2 for {\bf 10 minutes}.  You have previously conducted a ritual on yourself that causes this potion's effect to last longer on you. If you consume this potion yourself, your CR will increase by 2 for {\bf 30 minutes}. These CR buffs DO NOT stack. {\bf You, and only you, may consume this potion in response to an attack. This is a useful property, so try to keep at least one of these on hand.}

In order to administer the potion, the victim must either be a willing or helpless victim, or you may roll a 9 or 10 on a D10 (gm provided) while within 1 ZoC of your target. If you don't roll a 9 or 10, you can keep rolling until you do, or until someone stops you. If anyone asks you what you are doing, you must tell them that you look like you are trying to do something without the target's permission. If you succeed in your roll, give the potion to a GM to give to your target.

The potion is BLUE in color and takes 30 minutes to brew. 

The required ingredients are:
\begin{enumerate}
\item \iManOfWar{}
\item \iTeeth{}
\item \iSwordfish{}
\end{enumerate}

This potion is brewed as any other potion would be.\\

{\bf How to Brew a Potion:}\\ %%MAKE SIGNS!!!
\begin{enumerate}
  \item Acquire the necessary ingredients.
	\item Tell a GM that you are making this potion.
  \item Stand in front of an unused cauldron for one minute. At the end of this time, destroy the ingredients (they have been consumed by the potion), swap the cauldron sign to ``Full of liquid'' and write down the color of the potion you are brewing.
  \item Return after the duration listed above and stir the potion for 1 minute. Put both hands on the sign for this time.
  \item Erase the color, swap the sign back to ``An Empty Cauldron'', and return to the GM to get your potion item card.
\end{enumerate}
\end{document}