\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gDance{}}

You love the \cExExKing{} Ball. It is an annual event of great beauty and culture, and a celebration in honor of the Moon Goddess. This year, your secret relationship with \cDiplomat{} has enamored you to the ball even more -- so much so that you asked your \cKing{\parent} if you could help organize the ball. \cKing{} agreed to let you organize the dance showcase just before the banquet. The showcase is one of the most important parts of the Ball, as dance is the pinnacle of reverence for the Moon Goddess.

On the one hand, you are excited. The organizer and all participants of the showcase are often blessed by the Goddess for doing well. You have to be careful though. Rarely, the organizer is cursed for mocking or otherwise dishonoring the Goddess if things go poorly. You are determined to do well though, and there is no way your \cKing{\parent} would have let you take on this task if \cKing{\they} thought you couldn't handle it.

You don't know exactly what will please the Moon Goddess most, but you can take a few really good guesses:
\begin{enumerate}
	\item You should represent all three dance forms (see below).
	\item You should have exactly 2 couples perform each dance.
	\item You should have as many unique dancers as possible (minimize the number of repeated performers).
	\item You should start when the moon is highest in the sky (\cTOneFifty{}).
\end {enumerate}
\vspace{5mm}
{\bf You will need to submit a roster to the royal conductor so he can prepare the music (hand the ``\gRoster{}'' sheet to a GM or NPC) at least 20 minutes before the showcase is supposed to start}\\

The three dances are:
\begin{enumerate}
\item Merengue, the national dance of \pAtlantis{}.
\item Cross-step waltz, the national dance of \pPacifica{}.
\item Swing, the national dance of \pAmerica{}.
\end{enumerate}

You will have to get people to teach you, and to teach each other, how to dance the different kinds of dances before the showcase at {\bf \cTOneFifty{}}. Appropriate music will be provided by the band (assuming you manage to submit the roster in time!).

If things don't go quite your way, and you aren't able to fulfill every requirement, you should persevere anyway. Not having a performance at all will surely upset the Goddess more than a few last minute dance substitutions.

Of course, you will also need an audience. Do encourage people to attend.

\end{document}