\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gGlowShell{}}

research notebook from locked chest

each step answers a chain of numbers.

5 locks

Return to the chest and try the combo. if it works, you may go on to the next step immediately, otherwise take a 15 minute penalty before you may go on. (scales up by 15 min every wrong answer.)

\begin{enumerate}
\item Word scrambler  (translation of inscription on chest) Answer: ``Half'' (Make a sign)
\item Number hunt  (series of runes that have appeared) Answer: <Rune>
\item Sudoku  (research in a glowing book in the library) Answer: 169
\item word search to letters  (look for clues in paintings) - own copy but must remain in line of sight. Answer (alphabetize): EGHIL
\item Logic puzzle  (on the chest, last step) Answer: North: Word Third, East: Number First, South: Letter Second, West: Rune Fourth
\end{enumerate}


Logic puzzle:

The answer begins when the sun rises. 

-----------------------------------------

One must learn the letters of their tongue before they may form the words of a great speech. Look to the four corners of the earth to hone your skill, then reveal your answer when you are ready.

Look to the natives of the West for sound council. They often warn that it is bad luck to begin with magical signs.

The warriors of the East portray themselves as justice, whose word is law. Their words are not to be trusted, however, as their every moral has a price.

Trust the priests of the North as they spread the holy word. They often advise that learning your letters is never the most important thing you can do - for to them, God comes first.

The pirates of the South are ever a pushy lot. They say that their interests come first, but you can never trust their words.

Though you have learned much of those around the world, you still do not have the key. Think on what you have seen as you lay down to rest - but keep your eyes and ears open.

-----------------------------------------

The answer ends when the sun sets.




North: Word Third
East: Number First
South: Letter Second
West: Rune Fourth



Balm
L(a)mb

Wolf
(F)low

Lump
P(l)um

Earth
(H)eart

HALF





\end{document}