\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gInduction{}}

New magicians appear with some frequency in both \pPacifica{} and \pAtlantis{}. Inducting these magicians into the guild is a high priority, both as a matter of solidarity, and as a matter of safety, as the sealing magic of the ritual stabilizes their power. While many magicians realize their power while they are young, this is not always the case. Magicians have been documented discovering their powers as late as age 52, though these occurrences are exceedingly rare.

Two current members of the Magician's Guild may induct a promising candidate through the Guild's ancient rites of induction. Eligible candidates will have an $\alpha$ score of 2. Magicians of level 2 and higher have a ``\aPerceive{}'' ability which allows them to determine the $\alpha$ score of another individual.
\begin{description}
\item[First] Find the guild crest - it has been removed from the main guild hall, but is likely still somewhere in the castle. 
\item[Second] Both inducting members must spend 1 minute together tracing over the runic circle inscribed on the ground in front of the crest with \iChalk{}. You should explain the workings of the circle to the inductee for future inductions. The magical symbol resembles a six pointed star. 
\item[Third] All three participants should observe a moment of silence for one minute as the magical energy filters through the inductee and the magical symbol. 
\item[Fourth] One of the current members should swear in the inductee with a call and response swearing them to secrecy and to uphold the ideals and traditions of the guild. You will need to read the oath out of the \iBook{} which is secretly a magical tome (though you'll actually be making up the oath). {\bf The last sentence of the call and response needs to be ``I formally accept admittance into $<$insert faction name here$>$''}
\item[Fifth] The inductee must swear allegiance to a faction within the Magician's Guild: the White Tower or the Society of Free Magicians.
\item[Sixth] Take a greensheet and an ability card from under the guild crest and give it to the new inductee - they are now an active member.
\end{description}

The new member is inducted as a Level 1 magician. They should set their $\beta$ score to 0.

\end{document}