\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gLineage{}}

For as long as you can remember, you have hungered for your birthright - the throne of \pAtlantis{}.  Your quest for the \iTrident{\MYname} ended in frustration, the \iMusicBox{\MYname} has been an unforeseen complication, and the risk of losing your claim is always looming. 
As inconvenient as the treaty talks are, they have at least afforded you one advantage: they have given you the distraction you needed to contact the Assassin's Guild, which may have finally given you access to the necessary items to prove your claim.

You will need to prove two things in order to demonstrate that you have a legitimate claim to the throne. The primary objective is to prove that you are \cKing{\King} \cKing{}'s uncle. To do this, you will need to prove both that \cMother{} was your \cMother{\parent}, and that \cExExKing{} was your \cExExKing{\parent}.

In order to prove that \cMother{} was your \cMother{\parent}, you will need to acquire your birth certificate from \cDiplomat{}. This is an item you have long sought, but have only managed to locate with the help of the Assassin's Guild. If you acquire ``\iBirthCertificate{}'', you may open it.

You will {\bf also} need to prove that \cExExKing{} is your father. This is somewhat trickier to prove, as the evidence is quite scarce. You believe that your \cMother{\parent} hid {\bf \cMother{\their} journal} someplace in \pAtlantis{} to prevent it from falling into the wrong hands. You should look for a \pPacifica{}n artifact, hidden in plain sight. If you acquire ``\iJournal{}'', you may open it.

There may be alternate proof to be found, but you don't know where to begin looking for it.

With demonstrable proof of who your mother and father were, you can summon the court genealogist (find a GM; the pages can help). You may present the necessary documents to the court genealogist who will verify your lineage. It is up to you whether you wish the presentation of documents to be a highly public ceremony or not, but if your claim is verified, pages \emph{will} spread the announcement throughout game that you are in fact of royal birth and in the line of succession.

{\bf You must confer with the court genealogist before you can summon the court justice and lay claim to the throne.}

\end{document}