\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gLove{}}

You have created a special potion that is unknown to other magicians. This potion causes the victim to become completely enamored of you (no matter who administers the potion). They are compelled to obey you in a reasonable manner and not obstruct you in any way. The potion does have some limits though. For example, you cannot compel the victim to kill anybody or help you do so, although you can order them not to stop you from doing so yourself.

In order to maintain the potion's effect in the scope of game, you must perform a ``ritual'' once in every 15 minute span of time (0 - 14 on the clock, 15 - 30 on the clock, etc. You can skip the ritual in the 15 minute period in which you administer the potion, but try not to miss the one directly after.) This ritual can be performed anywhere in the 15 minute span - so two one-minute-long rituals starting at XX:14 would take care of your needs for two ritual time periods. The ritual is mildly suggestive and may involve kissing - you do not have to roleplay this, but tell your target what you're doing and tell any observers what they see.

If you miss a 15 minute window, the spell will not break yet, but the next ritual must be {\bf 5 minutes} in length to qualify. If you miss a second window, the spell will break, so be cautious. Once the ritual is complete, tell your target ``You are mine, forever'' to seal the deal.

In order to administer the potion, the victim must either be a willing or helpless victim, or you may stick {\bf three} stickers on the target without their knowledge. The {\bf three} stickers must be applied at least 1 minute apart. It does not matter if the stickers are noticed and removed before all are applied. The only way to fail in administering a potion is to be noticed while attempting to place any of the stickers. Dots are out of game knowledge for anyone except for the player applying them.

The potion is PURPLE in color and takes 30 minutes to brew.

The required ingredients are:
\begin{enumerate}
\item A healing potion 
\item A poison (not deadly poison)
\item 2 \iPearl{}
\end{enumerate}

This potion is brewed as any other potion would be.\\

{\bf How to Brew a Potion:}\\
\begin{enumerate}
  \item Acquire the necessary ingredients.
	\item Inform a GM that you are brewing this potion.
  \item Stand in front of an unused cauldron for one minute. At the end of this time, destroy the ingredients (they have been consumed by the potion), swap the cauldron sign to ``Full of liquid'' and write down the color of the potion you are brewing.
  \item Return after the duration listed above in the spell and potion list and stir the potion for 1 minute. Put both hands on the sign for this time.
  \item Erase the color, swap the sign back to ``An Empty Cauldron'', and return to the GM to get your potion item card.
\end{enumerate}
\end{document}