\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gMonsterTransformation{}}

As an absolute last resort, when all is lost and you are under attack, you have the ability to turn into a giant monster. Though this form carries with it immense power, you have made only the most basic preparations, and as such, it quickly takes its toll and loses strength.

When you use your Monster Transformation ability, call a game halt and negate any combat attacks currently being used on you, \emph{including} waylays. You turn into a giant monster. Discard any \colorBloody{} headbands that you are currently wearing and put on a \colorKraken{} one. Your CR becomes {\bf 20}, but every time you perform any type of {\bf attack} or {\bf resist}, your CR permanently drops by {\bf 4}. When your CR becomes 4, you no longer lose CR. {\bf Read the ``Transformation speech'' to all onlookers (speech is below)}. When preparations are complete, resume game.

{\bf Advantages of Being a Monster:}
\begin{itemize}
\item You can resist waylays
\item You are immune to poisons
\item You no longer need a weapon to make wound attacks
\item You do not become bloody from wounding other players
\item You treat all bulky items, including bodies, as 1 hand bulky
\end{itemize}

{\bf Disadvantages of Being a Monster:}
\begin{itemize}
\item You can only talk semi-intelligibly - enough to yell threats, but not enough to have a conversation.
\item You are still unable to perform killing blows
\item You are immune to healing, so don't get beaten up!
\end{itemize}

{\bf Note:} Giant monsters are scarier when no one knows that they're getting weaker. Your true power is in intimidation. Consider being consistent with your attacks by attacking with less than your full CR. Don't go too low, though - performing an attack the target resists at the wrong time could be fatal to you! 

This transformation is irreversible within the scope of game, so most of your previous goals become moot. However, this form comes with a terrible price that must be repaid immediately. Your new goal becomes to perform a ritual to pay back the spirits, then to escape the palace with your life. (This is a simplified version of ``\gRitual{}.'')

\begin{description}
\item[First] Knockout or restrain a member of royalty and bring them to the \sRunicCircle{}. Once they are inside the circle, they are automatically restrained as long as you are in the room. (Tell your victim this.)
\item[Second] Perform a minute of chanting magical rituals.
\item[Third] Draw blood from your victim (use your ability).
\item[Fourth] Killing blow them with a 10 count. This is the only situation in which you may killing blow anyone.
\item[Fifth] Escape the palace (leave game).
\end{description}

{\bf Transformation Speech}\\
The water around me starts to swirl and darken. In a heartbeat, the water is so inky that it obscures me completely. From the blackness comes first one tentacle, then a second. A terrifying monster, three times the size of a mer-person, emerges as the cloud of ink dissipates. Before you floats a terror of the deep, enough to make even sharks turn tail and run.


\end{document}