\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gNPC{}}

As an NPC at the Neptune Ball, you will have to wear various hats.

{\bf Page}

Most of the time, you will be a page. This is much like being an observer, and is similar in many ways, such as immunity to combat or damage. You should find a GM if someone asks you to do so, or if you feel there is need for one. But your role also differs from traditional observers as you have several duties below.

Players may ask you to tell another player that they are looking for them. While you should accept these requests, feel free to not take this very seriously. Feel free to "`forget"' when next you see them, tell them 20 minutes later, or inform them that the person is looking for them after they have clearly already been found. 

Players may also give you items to send to someone. If their target is in game, refuse. If this an out of game person, agree, and slip the item into your pocket or drop it off at the \pGM{} area. You can then safely ignore it.

Players may ask you for specific items. If \cPriest{} asks for a \iBaby{}, or \cSpy{} asks for \iScroll{}, tell them that it just arrived, and go find it in the \pGM{} area. Any other item requests should be treated with confusion.

GMs may also ask you to spread palace announcements throughout game.

If you are asked to find the Chief Justice or the Court Genealogist, go find a GM. If they ask you to find anyone else, treat this with confusion.

Note: You differ from Observers in one other important way: players may not ask you to leave the room. This is because of your second important duty below.

{\bf Shark}

Being a shark is the fun part of being an NPC. As an NPC, if you ever see a red headband (someone who is bloody), or a yellow headband (another shark), put on a yellow headband and roll a die. On a result of 1-2, your CR is 3. On a result of 3-4, your CR is 4. On a result of 5-6, your CR is 5. Now, go on a feeding frenzy. Generally prioritize the player(s) in the red headband(s), but attack anybody who gets in your way. 

You are a proud predator of the sea. As such, you should always walk, but walk with pride and devastating purpose. Your attacks are all knockout attacks. If you knock out someone \emph{without} a red headband, show the target your \aShark{} ability. You should only stop your feeding frenzy when one of three things occurs - every player in sight is unconscious, you have knocked out 2 players not currently wearing a red headband (you can knock out as many people in red headbands as you like), or you are subject to an attack you cannot resist. Once you have stopped being a shark, do not return to being a shark for 15 minutes.

{\bf Note: If you see a black headband, you can observe, but do not turn into a shark then or for 15 minutes afterward, even if you see red headbands. The sharks are scared of the thing that the black headband represents and therefore will not appear in the area. If you see a black headband while already a shark, flee and change back.}

\end{document}