\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gPotions{}}

\emph{If you have this greensheet, your $\beta$ score should be zero. If necessary, set it to zero when you receive this sheet.}

The spells and potions a magician can use are based on their level. Spells are represented as ability cards and are used as instant abilities. All potions follow a standard brewing strategy (see below the list). Potions have distinctive colors and can be recognized by magicians by their color (Lay people don't know what color the different potions are). Potions are represented as item envelopes that {\bf must be obtained from the GM. TELL A GM WHEN YOU --START-- BREWING A POTION}. You cannot dump out or steal potions that you did not brew. (This is a kludge.)

Potions can be administered in 2 ways. A willing or helpless target can drink the potion, in which case, the person administering the potion should hand over the potion item envelope to the target. A conscious, but ignorant target can also be injected with a potion. The person administering the potion must successfully stick a certain number of stickers on the target without being caught in the act, by the target or anyone else. (Stickers can be acquired at the cauldrons. If caught in the act, tell your observer that you were clearly trying to prick your target with a small syringe.) If the potion requires multiple dots to be effective, these dots must be applied at least 1 minute apart, but do not lose effect until the potion is applied. It does not matter if the stickers are noticed and removed before all are applied. Dots are out of game knowledge for anyone except for the player applying them. The person who is attempting to administer a potion should then find a GM, explain who the potion is targeting, and hand over the potion. The GM will handle the rest.

\emph{There is no mechanic for leveling up in game.}

{\bf Each magician can only brew 2 potions at a time.} %%There will be 5 or 6 cauldrons (1 in banquet hall).

As a magician, you are aware of some of the spells and potions that magicians of different levels can make and cast. Here are the known spells and potions that may be useful this evening:
\begin{enumerate}
  \item Level 1
   \begin{enumerate}
     \item Healing Potion (RED) - 15 minutes to brew. Can cure wounds (the target will wake up, fully healed after 10 seconds) and heal most poisons.\\ 
     {\bf Ingredients required:} \iSeaSnake{}, \iSeaFan{}
		 {\bf Dots required:} 1
     \item \aLesserDispel{} - Instant spell. Can completely remove a magical effect of level-2 or lower. Can be used on magical locks to increase your ``working hand'' size by 1. Can disrupt shape shifters momentarily.
   \end{enumerate}
  \item Level 2
   \begin{enumerate}
     \item \aPerceive{} - Instant spell. Can be used to determine someone's $\alpha$ score and detect magical effects.
   \end{enumerate}
  \item Level 3
     \begin{enumerate}
     \item Poison (GREEN) - 20 minutes to brew. This poison can be only cured with a healing potion AND \aFirstAid{}/A medkit, OR an exceptionally powerful magical artifact. It will take some random amount of time (up to 30 minutes) to affect the target if injected, but will take effect immediately if drunk.\\
     {\bf Ingredients required:} \iSeaUrchins{}, \iAnglerFish{}
		 {\bf Dots required:} 3
   \end{enumerate}
   \item Level 4 - No useful spells or potions
   \item Level 5
    \begin{enumerate}
     \item Transformation Potion (ORANGE) - 30 minutes to brew. This potion will transform a merperson into a human or vice versa. This transformation reduces your CR by one until reversed (your CR cannot go below zero).\\
      {\bf Ingredients required:} \iSquid{}, \iSponge{}, \iBarnacle{}
			{\bf Dots required:} 3
   \end{enumerate}
   \item Level 6
    \begin{enumerate}
      \item \aGreaterDispel{} - Instant spell. Can break spells up to level-4. Can be used on magical locks to reduce the necessary decking hand by two (decking hand requirement cannot be reduced below 1). Can disrupt shape shifters temporarily.
    \end{enumerate}
   \item Level 7
    \begin{enumerate}
      \item Deadly Poison (BLACK) - 90 minutes to brew. This poison {\bf cannot} be cured with a healing potion or \aFirstAid{}. It will affect a target almost instantly (within approximately 5 minutes) if injected, and instantly if consumed.\\
      {\bf Ingredients required initially:} \iIceFish{}, \iElectricEel{}, \iSwordfish{}\\
      {\bf Ingredients required after brewing:} \iSnails{}, \iDeepClam{}\\
		  {\bf Dots required:} 5
    \end{enumerate}
   \item Level 8 - No useful spells or potions
   \item Level 9
   	\begin{enumerate}
   	 \item Resurrection Potion (Silver) - 30 minutes to brew. This potion can be administered to a dead character within 10 minutes of their passing. It will revive them to full health as soon as the potion is consumed.\\
   	 {\bf Ingredients required initially:} \iSnails{}, \iPearl{}\\
   	 {\bf Ingredients required after brewing:} \iDrug{}, \iAnglerFish{}, A Sand Dollar (928)
   	 {\bf Dots required:} N/A (target must be dead.)
   	\end{enumerate}
\end{enumerate}
Many magicians also develop their own private spells and potions. \\

{\bf How to Brew a Potion:}
\begin{enumerate}
  \item Acquire the necessary ingredients.
  \item Stand in front of ``\sEmptyCauldron{}'' for 1 minute. At the end of this time, destroy the ingredients (they have been consumed by the potion), swap the cauldron sign to ``\sFullCauldron{}'' and write down the color of the potion you are brewing. If you are interrupted or otherwise cease to tend the potion before the 1 minute is up, you retain the items.
  \item Return after the duration listed above. (Potions cannot over brew) If the potion is the Deadly Poison or the Resurrection Potion, spend 1 minute adding the additional ingredients at this time.
  \item Erase the color, and swap the sign back to ``\sEmptyCauldron{}''. Then go to GM HQ to obtain your potion.
\end{enumerate}

{\bf Illegal Magic:}\\
All poisons are strictly illegal in \pAtlantis{}. Additionally, for historical reasons, transformations are also illegal. Making or possesing any of these potions is a severe crime.

{\bf Dangerous Ingredients:}
Some ingredients are never meant for beneficial or benign potions. 
\begin{enumerate}
\item \iHemlock{} is a powerful hallucinogen.  %%shapeshifter
\item \iSnails{} is very poisonous, even on it's own. %%Deadly poison
\item \iPearl{} is  known to cause victims to become dangerously compliant, %%Love potion
\item \iManOfWar{} is able to alter the consumer's mind in dangerous ways. %%Buff potion
\item \iSquid{} is able to alter the consumers body in dangerous ways.  %%shapeshifter
\end{enumerate}

\end{document}