\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gChecklist{}}

{\large PRE GAME}

Pull these players aside to give them these items:
Everyone: Pack of Cards, \colorBloody{} headband
\cAriel{}, \cWillow{}, \cGeneral{}: \colorHuman{} headband
\cPrince{}: \colorShark{} headband
\cWitch{}: \colorKraken{} headband
			2	Amulets
\cQueen{}: \colorQueen{} Headband
\cQueen{}, \cDiplomat{}, \cSpy{}: Tattoo
\cKing{}: Trident
\cSlave{}: Tarot Deck
\cGeneral{}: Pen/Pencil

Make sure the music box gets placed. Draw a guide path using the music notes from the banquet hall to the pacifican suite. Attach the music note to the wall, then flip it UP and draw an arrow on the back.

Have \cPlant{} write a forged will for \cPriest{} and put it in the forgery sign.

Include announcements about masks - required, but also may need to enunciate more carefully, and repeat yourself. Player to player communication is paramount to a game like this working, so please be mindful and accommodating if you are asked to repeat yourself.

Set everyone up in the banquet hall to hear \cManta{}'s speech.

{\large DURING GAME}
Minnow NPCs may come to you about the players requesting certain specific titled NPCs be summoned temporarily. Brief them as follows and send them off into game. They should accomplish their task and sweep away imperiously. \textbf{All titled NPCs have CR = 8 FOR DEFENSE in case a PC is brash enough to attack you. You have CR = 0 for attacking anyone; that's not what you're here for.}
\begin{itemize}
	\item The Chief Justice
	\begin{enumerate}
		\item This NPC can be summoned by \cManta{} or anyone requesting clarification on the line of inheritance in \pAtlantis{}.
		\item This NPC is the ONLY ONE with the authority to NAME A NEW RULER if the previous one is killed or abdicates. At game start, \cKing{} is the ruler. If \cManta{} has successfully been confirmed by the Court Genealogist (another NPC) at some point in game, and \cKing{} and \cPrincess{} have been removed from the line (proven shapeshifter, married to an older member of the royal family of \pPacifica{}, killed, abdicated, etc.), \cManta{} is the next heir, UNLESS \cQueen{} has revealed herself. If so, \cQueen{} takes precedent over \cManta{} - but ONLY if \cQueen{\they} reveals herself BEFORE you declare \cManta{} the new ruler.
		\item This NPC can also declare someone unfit to rule if it can be demonstrated that the person is a shapeshifter (this most likely involves casting dispel magic on them to cause the person to shift in front of you.) This can disqualify the current ruler, or someone who would otherwise be in the line of succession. It doesn't matter if the person shifts between human and merperson, or between merperson and shark; any shapeshifter is dangerous and unfit to rule.
	\end{enumerate}
	\item The Court Genealogist
	\begin{enumerate}
		\item This NPC can be summoned by \cManta{} to prove \cManta{\their} lineage. - You may be re summoned if people doubt the claim.
		\item \cManta{} must present you with \textbf{both} \iBirthCertificate{} and \iJournal{}. If \cManta{\they} \cManta{\have} both, you should confirm that their lineage is confirmed, and that they are in fact \cKing{\full}'s uncle. Well, technically half uncle, but with \cExExKing{} as a parent, \cManta{} is indisputably \pAtlantis{}n royalty. 
		\item Ask all NPC minnows you can find to spread the word that ``A previously unknown \cManta{\prince} of \pAtlantis{} has been found! Long live \cManta{}!'' all across game.
		\item when you leave game, make sure to return the \iBirthCertificate{} and \iJournal{} to \cManta{}.
	\end{enumerate}
	\item The Royal Apothacary
	\begin{enumerate}
		\item This NPC can be summoned by any of \cWillow{}'s family (\cKing{}, \cAriel{}, \cPrincess{}, \cPlant{}, \cQueen{}, or \cManta{}).
		\item Task 1: Examine \cWillow{} for ~30 seconds. Declare that \cWillow{\they} \cWillow{\are} clearly addicted to something, and that you need a sample of the drug in question to make a diagnosis. Ask them to summon you again when they have one dose of \iDrug{} they can present you with. Leave game for now, unless they can produce the item immediately.
		\item Task 2: When summoned again, you will be presented with one dose of \iDrug{}. Spend 30 more seconds examining \cWillow{}, and 30 seconds examining \iDrug{} (feel free to medi-babble). Declare the solution to be for \cWillow{} to take a \iHealingPotion{} and a \iPoison{} at the same time (don't process the effects of either). \cWillow{\They} will retch violently for 30 seconds, at the end of which \cWillow{\they} will be fully free of the effects of \iDrug{}, including no longer being addicted.
		\item Take the \iDrug{} dose with you when you exit game! Don't let any of the PCs take it back.
	\end{enumerate}
\end{itemize}

\end{document}
