\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gRitual{}}

This ritual is far more potent than simply siphoning a little piece of a soul. It is also far more dangerous and time consuming. The reward is worth it though. To actually sacrifice a royal soul to the spirits will go a long way toward paying off your debts.

Since this ritual involves the spirits crossing over into this world and devouring the victim's soul from the inside out, the victim will thrash around, and needs to be restrained. Therefore, you need {\bf two} people to help you. If someone (ie: \cAriel{}) wishes to use this ritual to absolve a specific debt, he or she must be one of your helpers.

{\bf To perform the Ritual:}
\begin{description}
\item[First] Knockout or restrain a member of royalty and bring them to the \sRunicCircle{}.
\item[Second] Have your two helpers restrain your victim.
\item [Third] Outline the circle in \iChalk{\MYname}. If the circle is already chalked, you will have to remove the chalk that is present and lay down your own lines.
\item[Fourth] Perform a minute of chanting magical rituals. The person wishing to absolve their debt to you must participate as well. Feel free to use a call and repeat style. The victim will be in intense pain throughout all of this.
\item[Fifth] Killing blow them with a 10 count. This is the only situation in which you may killing blow anyone.
\end{description}

After the killing blow, the victim is dead, and the spirits leave their body. Any of your helpers with debts to you should consider them paid.

\end{document}