\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gShapeshifter{}}

You have created a special potion that is unknown to other magicians. This potion causes the victim to become a shapeshifter permanently and undetectably - even the strongest magical detection will not be able to tell the difference between a victim of this potion and a natural shapeshifter, and it would take miraculous magical power to dispel it, far beyond any magician. It also has the useful property of healing the wounds of the target, and therefore being able to masquerade as a common, benign healing potion.

This potion is particularly finicky. It requires \iHemlock{}, a very rare \pPacifica{}n herb that rapidly loses its potency. Any sample you obtain in game, or potion you brew from it will expire at \cTThree{\MYname{}}. The potion must therefore be administered before that time if it is to have any effect.

In order to administer the potion, the victim must either be a willing or helpless victim, or you may stick {\bf three} stickers on the target without their knowledge. The {\bf three} stickers must be applied at least 1 minute apart. It does not matter if the stickers are noticed and removed before all are applied. The only way to fail in administering a potion is to be noticed while attempting to place either of the stickers. Dots are out of game knowledge for anyone except for the player applying them.

The potion is GOLD in color and takes 30 minutes to brew. 

The required ingredients are:
\begin{enumerate}
\item \iHemlock{} (\cSpy{} is supposed to be providing you with this)
\item \iSquid{}
\item \iBarnacle{}
\end{enumerate}

This potion is brewed as any other potion would be.\\

{\bf How to Brew a Potion:}\\ %%MAKE SIGNS!!!
\begin{enumerate}
  \item Acquire the necessary ingredients.
  \item Stand in front of an unused cauldron for one minute. At the end of this time, destroy the ingredients (they have been consumed by the potion), swap the cauldron sign to ``Full of liquid'' and write down the color of the potion you are brewing.
  \item Return after the duration listed above and stir the potion for 1 minute. Put both hands on the sign for this time.
  \item Take the appropriate potion from the envelope below the cauldron, erase the color, and swap the sign back to ``An Empty Cauldron''.
\end{enumerate}
\end{document}