\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gSpellBreak{}}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

Many years ago, you were put under a spell by a powerful magician, \cWitch{}. You have been struggling under \cWitch{\their} control for quite some time, and have been steadily weakening the curse as time went on. Now the spell is on its last legs, and \cWitch{} is too distracted to properly strengthen it. This is your chance!

Your progress towards breaking the spell is measured in points. You can earn 1 point by meditating for 2 uninterrupted minutes out of the presence of \cWitch{}. This is repeatable, but only once every half hour. Additionally, each of the actions you perform from the list below earn you 2 points towards breaking the spell. Each action can only count once.

\begin{enumerate}
\item Touch the trident for an uninterrupted 10 seconds.
\item Have a magician cast \aLesserDispel{} on you.
\item Drink a Healing Potion (Red) when unhurt.
\item Talk to a human about the surface world for 2 minutes.
\end{enumerate}

When you reach 8 points, the spell noticeably weakens. Remove your \iEnslavementSpell{} magical effect. You are no longer compelled to do \cWitch{}'s bidding! But the spell is not fully broken. You are still bound to protect \cWitch{\their} identity by the \iIdentityProtectionSpell{} magical effect. In order to break the second layer and reveal your former captor, you must complete the steps in the research notebook entitled \nSpellBreakNotebook{}. Open it to page 2.

{\bf Note:} \cWitch{}'s death is not automatically to your benefit. Spiteful as \cWitch{\they} \cWitch{\are}, \cWitch{} set \cWitch{\their} spell to steadily drain your lifeforce in the event of \cWitch{\their} demise to pay \cWitch{\their} debt to the spirits as fully as possible. If \cWitch{} dies in game, you must finish breaking the first layer of the spell before the end of the Ball, or wither away shortly thereafter. The second layer is not quite as deadly to leave in place, but you would dearly like to be able to fully explain your ordeal, and this Ball represents your best opportunity to complete that task.

\end{document}