\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gWS{}}

You have chosen to embark on a quest for the fabled wishing stone. This magical artifact is one of the most powerful artifacts known under the sea, and can grant many wishes to the one who controls it. The stone does not appear to just anyone however, and you must prove your worthiness.

Answer the questions below, writing down the answer in the space provided. Take the letter indicated in parenthesis after the question, and put it in the appropriate space at the bottom of this sheet. Once you think you know the final answer, find a GM and tell them. You {\bf may} guess, even if you don't have all of the letters yet. If you are correct, you will be provided with your prize. However, if you are incorrect, you must wait {\bf 5} minutes before submitting another answer. The GM will tell you which letter(s) are wrong. {\bf You only get two wrong guesses before losing your chance forever. You may begin submitting answers after the banquet.}

EXAMPLE:
Where are you? (1 word, take the 2nd letter of 1st word)\\
Answer: Atlantica  -- Take ``t''.
		

{\bf Questions:}
\begin{enumerate}
 \item Who gave Poseidon the trident? (1 word, take 1st letter of 1st word) \vspace{3 mm}\\  \underline{\hspace{15cm}}
 \item What is the patron animal of the \pAtlantis{}n religion? (2 words, take 2nd letter of 2nd word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item Among the Explorer's Guild, the Guardian's Guild, and the Merchant's Guild, which guild has the oldest current or most recent leader? (3 words, take 3rd letter of 2nd word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item Who created the \sArtifactTwo{}? (1 word, take 1st letter of 1st word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item Who was the King of Atlantica when the war with Pacifica started? (1 word, take 1st letter of 1st word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item How many factions are there in the Magician's Guild? (1 word, take 4th letter of 1st word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item Where is the Assassin's Guild? (3 words, take 1st letter of 3rd word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item What magical item is purported to bring marital happiness? (3 words, take 4th letter of 2rd word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item Who is the current queen of Atlantica? (1 word, take 1st letter of 1st word) \vspace{3 mm}\\ \underline{\hspace{15cm}} % TODO: correct this gender-wise
	\item Who is the current ruler of Pacifica? (2 words, take 5th letter of 2nd word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item How many major powers under the sea? (1 word, take 1st letter of 1st word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item What is the national form of dance in \pAtlantis{}? (1 word, take 3rd letter of 1st word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item Where is the Magician's Guild Crest now? (2 words, take 4th letter of 2nd word) \vspace{3 mm}\\ \underline{\hspace{15cm}}
	\item What is the name of the Province in which the polio vaccine was developed? (1 word, take 3rd letter of 1st word) \vspace{3 mm}\\ \underline{\hspace{15cm}} \vspace{10 mm}
\end{enumerate}

{\Large Final Answer:}\\
Assemble the letters taken from the answers to the questions above here (in numerical order by question): \vspace{5 mm}

\underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}}

\end{document}